---
title: "Aggregate"
format: html
editor: visual
---

```{r}
library(werptoolkitr)
library(dplyr)
library(sf)
```

## Paths

I'm going to set this up to dump data to the QAEL WERP share for now. Unfortunately, that calls itself something different for each of us.

```{r}
if (Sys.info()['user'] == 'galen') {
  qaelpath <- '~/../Deakin University/QAEL - WERP in house - WERP'
} else if (Sys.info()['user'] == 'Georgiad') {
  qaelpath <- '~/Deakin University/QAEL - WERP - WERP'
} else if (Sys.info()['user'] == 'georgiad') {
  #qaelpath <- '~/Deakin University/QAEL - WERP - WERP'
  qaelpath <- 'C:/Users/georgiad/Deakin University/QAEL - WERP - WERP'
} else if (Sys.info()['user'] == 'Admin') {
  qaelpath <- 'C:/Users/Admin/Deakin University/QAEL - WERP in house - WERP'
} else {
  rlang::abort("YOU'RE NOT GALEN. PUT IN YOUR PATH TO QAEL-WERP")
}
```

ewr_results \<- file.path(project_dir, 'module_output', 'EWR')

```{r}
# python can't use the tildes, so have to expand
qaelpath <- path.expand(qaelpath)

# Outer directory for project data
project_dir = file.path(qaelpath, 'Toolkit', 'macq-data')

# Hydrographs (expected to exist already; created here with Ash_data_sorting.qmd)
hydro_dir = file.path(project_dir, 'hydrographs')

# Generated data
# EWR outputs (will be created here in controller, read from here in aggregator)
# 4 specific sets 

# outputs of aggregator. There may be multiple modules
# agg_results <- file.path(project_dir, 'aggregator_output')
# 
# 
# sdl_objective_simple_agg_dir <- file.path(agg_results, 'sdl_objective_simple')
# sdl_objective_agg_dir <- file.path(agg_results, 'sdl_objective')
# sdl_target_agg_dir <- file.path(agg_results, 'sdl_target')
# sdl_EWRs_agg_dir <- file.path(agg_results, 'sdl_EWRs')
# sdl_theme_agg_dir <- file.path(agg_results, 'sdl_theme')
```

We now need to clip to the Macquarie, or it will return a bunch of other units due to overlaps

```{r}
sdl_clip <- sdl_units |> 
  dplyr::filter(SWSDLName == 'Macquarie–Castlereagh')
```

## Aggregation sequencing

-   Sequence of steps

-   Sequence of functions

We'll likely want something different here (or multiple)

I took the basin off of here, since this is just the Mac-Castle

```{r}
aggseq_simple <- list(ewr_code = c('ewr_code_timing', 'ewr_code'),
               planning_unit = planning_units)
funseq_simple <- list("ArithmeticMean",
                      'ArithmeticMean') 




aggseq <- list(ewr_code = c('ewr_code_timing', 'ewr_code'),
               planning_unit = planning_units,
               env_obj =  c('ewr_code', "env_obj"),
               sdl_units = sdl_clip,
               Specific_goal = c('env_obj', "Specific_goal"),
               Objective = c('Specific_goal', 'Objective'),
               target_5_year_2024 = c('Objective', 'target_5_year_2024'))


funseq <- list("ArithmeticMean", # changed from 'CompensatingFactor',
               'ArithmeticMean',
               'ArithmeticMean',
               'SpatialWeightedMean',
               'ArithmeticMean',
               'ArithmeticMean',
               'ArithmeticMean')

# NOTE: I've been moving to Target as an outcome, since there seems to be appetite to aggregate to the broad ecological groupings. It means we lose some granularity and can't get to the 5,10,20 year targets. I'll do that too and put it in an internal directory.

target_aggseq <- list(ewr_code = c('ewr_code_timing', 'ewr_code'),
               planning_unit = planning_units,
               env_obj =  c('ewr_code', "env_obj"),
               sdl_units = sdl_clip,
               Specific_goal = c('env_obj', "Specific_goal"),
               Target = c('Specific_goal', 'Target'))

target_funseq <- list("ArithmeticMean", # changed from 'CompensatingFactor',
               'ArithmeticMean',
               'ArithmeticMean',
               'SpatialWeightedMean',
               'ArithmeticMean',
               'ArithmeticMean')

#Georgias version:
EWRs_aggseq <- list(
               ewr_code = c('ewr_code_timing', 'ewr_code'),
               planning_unit = planning_units,
               sdl_units = sdl_clip)

EWRs_funseq <- list(
              c('ArithmeticMean', "NumberOfValues", "Variance"), #aggregates ewr_code_timing to ewr_code
              c('ArithmeticMean', "NumberOfValues", "Sum"), #aggregate gauges to planning_unit
              c('ArithmeticMean', "NumberOfValues", "Sum")) #planning_unit gauges to sdl_units
              
Theme_aggseq <- list(
               ewr_code = c('ewr_code_timing', 'ewr_code'),
               planning_units = planning_units,
               env_obj =  c('ewr_code', "env_obj"),
               sdl_units = sdl_clip,
               Target = c('env_obj', 'Target'))

Theme_funseq <- list(
              c('ArithmeticMean', "NumberOfValues", "Variance"), #aggregates ewr_code_timing to ewr_code
              c('ArithmeticMean', "NumberOfValues", "Sum"), #aggregate gauges to planning_unit
              c('ArithmeticMean', "NumberOfValues", "Sum"), #ewr_code to env_obj              
              c('ArithmeticMean', "NumberOfValues", "Sum"), #planning_unit to sdl_units              
              c('ArithmeticMean', "NumberOfValues", "Sum")) #env_obj  to Target

```

## Aggregate

-   Sequence (levels of each theme, space, time axis)

-   Aggregation functions at each step

-   Produces a list, with each sheet a step in the aggregation

```{r}
#SIMPLE

# system.time(agged_data_simple <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk5a', 'module_output', 'EWR'), 
#            type = 'achievement',
#            geopath = bom_basin_gauges,
#            causalpath = causal_ewr,
#            groupers = 'scenario',
#            aggCols = 'ewr_achieved',
#            group_until = list(planning_unit_name = is_notpoint,
#                                 gauge = is_notpoint),
#            pseudo_spatial = 'planning_unit',
#            aggsequence = aggseq_simple,
#            funsequence = funseq_simple,
#            saveintermediate = TRUE,
#            namehistory = FALSE,
#            keepAllPolys = FALSE,
#            returnList = TRUE,
#            savepath = file.path(project_dir, 'historic', 'Mk5a', 'aggregator_output', 'sdl_objective_simple')))

system.time(agged_data_simple <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk5', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint,
                                gauge = is_notpoint),
           pseudo_spatial = 'planning_unit',
           aggsequence = aggseq_simple,
           funsequence = funseq_simple,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk5', 'aggregator_output', 'sdl_objective_simple')))

system.time(agged_data_simple <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk4a', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint,
                                gauge = is_notpoint),
           pseudo_spatial = 'planning_unit',
           aggsequence = aggseq_simple,
           funsequence = funseq_simple,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk4a', 'aggregator_output', 'sdl_objective_simple')))

system.time(agged_data_simple <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk4', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint,
                                gauge = is_notpoint),
           pseudo_spatial = 'planning_unit',
           aggsequence = aggseq_simple,
           funsequence = funseq_simple,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk4', 'aggregator_output', 'sdl_objective_simple')))
# ewr_code_timing <- agged_data_simple$ewr_code_timing
# ewr_code <- agged_data_simple$ewr_code
```

THIS ERROR MEANS the path is wrong:

```         
Error in UseMethod("mutate") :    no applicable method for 'mutate' applied to an object of class "NULL" Timing stopped at: 0.02 0 0.01
```

```{r}
# system.time(agged_data <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk5a', 'module_output', 'EWR'), 
#            type = 'achievement',
#            geopath = bom_basin_gauges,
#            causalpath = causal_ewr,
#            groupers = 'scenario',
#            aggCols = 'ewr_achieved',
#            group_until = list(planning_unit_name = is_notpoint, 
#                                 gauge = is_notpoint),
#            pseudo_spatial = 'planning_unit',
#            aggsequence = aggseq,
#            funsequence = funseq,
#            saveintermediate = TRUE,
#            namehistory = FALSE,
#            keepAllPolys = FALSE,
#            returnList = TRUE,
#            savepath = file.path(project_dir, 'historic', 'Mk5a', 'aggregator_output', 'sdl_objective'))) 

system.time(agged_data <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk5', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
           pseudo_spatial = 'planning_unit',
           aggsequence = aggseq,
           funsequence = funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk5', 'aggregator_output', 'sdl_objective'))) 

system.time(agged_data <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk4a', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
           pseudo_spatial = 'planning_unit',
           aggsequence = aggseq,
           funsequence = funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk4a', 'aggregator_output', 'sdl_objective'))) 

system.time(agged_data <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk4', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
           pseudo_spatial = 'planning_unit',
           aggsequence = aggseq,
           funsequence = funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk4', 'aggregator_output', 'sdl_objective'))) 
```

```{r}
# system.time(agged_data_tar <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk5a', 'module_output', 'EWR'), 
#            type = 'achievement',
#            geopath = bom_basin_gauges,
#            causalpath = causal_ewr,
#            groupers = 'scenario',
#            aggCols = 'ewr_achieved',
#            group_until = list(planning_unit_name = is_notpoint, 
#                                 gauge = is_notpoint),
#                         pseudo_spatial = 'planning_unit',
# 
#            aggsequence = target_aggseq,
#            funsequence = target_funseq,
#            saveintermediate = TRUE,
#            namehistory = FALSE,
#            keepAllPolys = FALSE,
#            returnList = TRUE,
#            savepath = file.path(project_dir, 'historic', 'Mk5a', 'aggregator_output', 'sdl_target'))) 

system.time(agged_data_tar <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk5', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
                        pseudo_spatial = 'planning_unit',

           aggsequence = target_aggseq,
           funsequence = target_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk5', 'aggregator_output', 'sdl_target'))) 

system.time(agged_data_tar <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk4a', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
                        pseudo_spatial = 'planning_unit',

           aggsequence = target_aggseq,
           funsequence = target_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk4a', 'aggregator_output', 'sdl_target'))) 


system.time(agged_data_tar <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk4', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
                        pseudo_spatial = 'planning_unit',

           aggsequence = target_aggseq,
           funsequence = target_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk4', 'aggregator_output', 'sdl_target'))) 
```

```{r}
# system.time(agged_data_EWRs <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk5a', 'module_output', 'EWR'), 
#            type = 'achievement',
#            geopath = bom_basin_gauges,
#            causalpath = causal_ewr,
#            groupers = 'scenario',
#            aggCols = 'ewr_achieved',
#            group_until = list(planning_unit_name = is_notpoint, 
#                                 gauge = is_notpoint),
#                         pseudo_spatial = 'planning_unit',
# 
#            aggsequence = EWRs_aggseq,
#            funsequence = EWRs_funseq,
#            saveintermediate = TRUE,
#            namehistory = FALSE,
#            keepAllPolys = FALSE,
#            returnList = TRUE,
#            savepath = file.path(project_dir, 'historic', 'Mk5a', 'aggregator_output', 'sdl_EWRs')))

system.time(agged_data_EWRs <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk5', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
                        pseudo_spatial = 'planning_unit',

           aggsequence = EWRs_aggseq,
           funsequence = EWRs_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk5', 'aggregator_output', 'sdl_EWRs')))

system.time(agged_data_EWRs <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk4a', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
                        pseudo_spatial = 'planning_unit',

           aggsequence = EWRs_aggseq,
           funsequence = EWRs_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk4a', 'aggregator_output', 'sdl_EWRs')))

system.time(agged_data_EWRs <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk4', 'module_output', 'EWR'), 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           group_until = list(planning_unit_name = is_notpoint, 
                                gauge = is_notpoint),
                        pseudo_spatial = 'planning_unit',

           aggsequence = EWRs_aggseq,
           funsequence = EWRs_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk4', 'aggregator_output', 'sdl_EWRs')))
```

```{r}

# system.time(agged_data_Theme <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk5a', 'module_output', 'EWR'),  
#            type = 'achievement',
#            geopath = bom_basin_gauges,
#            causalpath = causal_ewr,
#            groupers = 'scenario',
#            aggCols = 'ewr_achieved',
#            # group_until = list(planning_unit_name = 'sdl_units', 
#            #                      gauge = is_notpoint),
#            #              pseudo_spatial = 'planning_units',
#            auto_ewr_PU = TRUE,
#            aggsequence = Theme_aggseq,
#            funsequence = Theme_funseq,
#            saveintermediate = TRUE,
#            namehistory = FALSE,
#            keepAllPolys = FALSE,
#            returnList = TRUE,
#            savepath = file.path(project_dir, 'historic', 'Mk5a', 'aggregator_output', 'sdl_theme')))

system.time(agged_data_Theme <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk5', 'module_output', 'EWR'),  
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           # group_until = list(planning_unit_name = 'sdl_units', 
           #                      gauge = is_notpoint),
           #              pseudo_spatial = 'planning_units',
           auto_ewr_PU = TRUE,
           aggsequence = Theme_aggseq,
           funsequence = Theme_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk5', 'aggregator_output', 'sdl_theme')))

system.time(agged_data_Theme <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk4a', 'module_output', 'EWR'),  
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           # group_until = list(planning_unit_name = 'sdl_units', 
           #                      gauge = is_notpoint),
           #              pseudo_spatial = 'planning_units',
           auto_ewr_PU = TRUE,
           aggsequence = Theme_aggseq,
           funsequence = Theme_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk4a', 'aggregator_output', 'sdl_theme')))

system.time(agged_data_Theme <- read_and_agg(datpath = file.path(project_dir, 'historic', 'Mk4', 'module_output', 'EWR'),  
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           # group_until = list(planning_unit_name = 'sdl_units', 
           #                      gauge = is_notpoint),
           #              pseudo_spatial = 'planning_units',
           auto_ewr_PU = TRUE,
           aggsequence = Theme_aggseq,
           funsequence = Theme_funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = file.path(project_dir, 'historic', 'Mk4', 'aggregator_output', 'sdl_theme')))
```

40 seconds

```         
#GD: user  system elapsed   128.84   12.03  264.08 
```
