---
title: "Aggregate"
format: html
editor: visual
---

```{r}
library(werptoolkitr)
library(dplyr)
library(sf)
```

## Paths

I'm going to set this up to dump data to the QAEL WERP share for now. Unfortunately, that calls itself something different for each of us.

```{r}
if (Sys.info()['user'] == 'galen') {
  qaelpath <- '~/../Deakin University/QAEL - WERP in house - WERP'
} else {
  rlang::abort("YOU'RE NOT GALEN. PUT IN YOUR PATH TO QAEL-WERP")
}
```

```{r}
# python can't use the tildes, so have to expand
qaelpath <- path.expand(qaelpath)

# Outer directory for project data
project_dir = file.path(qaelpath, 'Toolkit', 'macq-data')

# Hydrographs (expected to exist already; created here with Ash_data_sorting.qmd)
hydro_dir = file.path(project_dir, 'river_system_simulation_data')

# Generated data
# EWR outputs (will be created here in controller, read from here in aggregator)
ewr_results <- file.path(project_dir, 'module_output', 'EWR')

# outputs of aggregator. There may be multiple modules
agg_results <- file.path(project_dir, 'aggregator_output')
```

## Aggregation sequencing

-   Sequence of steps

-   Sequence of functions

We'll likely want something different here (or multiple)

```{r}
aggseq <- list(ewr_code = c('ewr_code_timing', 'ewr_code'),
               env_obj =  c('ewr_code', "env_obj"),
               sdl_units = sdl_units,
               Specific_goal = c('env_obj', "Specific_goal"),
               Objective = c('Specific_goal', 'Objective'),
               mdb = basin,
               target_5_year_2024 = c('Objective', 'target_5_year_2024'))


funseq <- list(c('CompensatingFactor'),
               c('ArithmeticMean'),
               c('ArithmeticMean'),
               c('ArithmeticMean'),
               c('ArithmeticMean'),
               c('SpatialWeightedMean'),
               c('ArithmeticMean'))
```

## Aggregate

-   Sequence (levels of each theme, space, time axis)

-   Aggregation functions at each step

-   Produces a list, with each sheet a step in the aggregation

```{r}
system.time(agged_data <- read_and_agg(datpath = ewr_results, 
           type = 'achievement',
           geopath = bom_basin_gauges,
           causalpath = causal_ewr,
           groupers = 'scenario',
           aggCols = 'ewr_achieved',
           aggsequence = aggseq,
           funsequence = funseq,
           saveintermediate = TRUE,
           namehistory = FALSE,
           keepAllPolys = FALSE,
           returnList = TRUE,
           savepath = agg_results))
```

130 seconds.

On to comparing
