---
title: "Aggregation on HPC"
format: html
editor: visual
---

```{r}
library(werptoolkitr)
library(sf)
library(future.batchtools)
library(furrr)
```

Set up parallel structure

```{r}
if (Sys.info()['user'] == 'hol436') {
  plan(list(tweak(batchtools_slurm,
                  # workers = 4, # I assume it'll grab 4, since that's the length of the futurelist vectors
                  template = "HPC/batchtools.slurm.tmpl",
                  resources = list(time = 15, # Can cut way down probably. 
                                   ntasks.per.node = 30, # If it's 2mins per job, and we want it to take ~ 10 mins, and there are 120 inner_subdirs, that's 24. 30 is 4 iterations. Should we ask for more? traeoff in queue time vs proc time, and not sure how it'll play out. 
                                   mem.per.cpu = '4GB', # I think 'mem' alone is for the whole node, so this is safer
                                   job.name = 'macagg')),
            multicore))
} else {
  plan(multisession)
}
```

To run this on the hpc, purl it with

```{r}
#| eval: false

infile <- 'HPC/2_aggregate_HPC.qmd'

rfile <- stringr::str_replace(infile, '.qmd', '.R')

knitr::purl(input = infile, output = rfile)

```

## Paths

```{r}
# tired of writing the whole thing out
source('R/paths.R')
source('R/agg_variables.R')
```

I keep doing things very similar to this to deal with the nested dirs. Should make it a function, but it's not quite stable yet.

```{r}
# Get all the EWR dir paths should I save this like i did with the gauges? 
# Wouldn't locally, but it's really slow on petrichor.

if (!file.exists('HPC/inner_dirs.rds')) {
    inner_dirs <- list.dirs(
  ewr_results, recursive = TRUE
  )
    saveRDS(object = inner_dirs, file = 'HPC/inner_dirs.rds')
} else {
    inner_dirs = readRDS('HPC/inner_dirs.rds')
}


inner_climdirs <- grepl('r[0-9]_[0-9]_e1_[0-9]{1,2}$', inner_dirs)
inner_parents <- inner_dirs[inner_climdirs]
# Those will be the hydro_dirs, each with 76 scenarios inside
# Then we want to make the outputs work, so put them in subdirs with the same structure
inner_subdirs <- gsub(ewr_results, '', inner_parents)
inner_subdirs <- gsub('^/', '', inner_subdirs)
```

Prevent issues with PU overlaps

```{r}
sdl_clip <- sdl_units |> 
  dplyr::filter(SWSDLName == 'Macquarie–Castlereagh')
```

Set up the new causal links

```{r}
objective_mapping <- readr::read_csv(file.path(project_dir, 'EWR_to_Target_mapping.csv')) |> 
  # dplyr::filter(state == 'NSW') |> 
  dplyr::filter(grepl('Macq', l_t_w_p_short_name)) |> 
  dplyr::select(planning_unit_name, gauge, ewr_code, ewr_code_timing, 
                eco_objective_code, env_group = target)

# This is what we used originally
ewr2target <- objective_mapping |> 
  dplyr::select(-eco_objective_code) |> 
  dplyr::distinct() |> 
  dplyr::mutate(ewr_code_timing = ifelse(is.na(ewr_code_timing), '', ewr_code_timing)) |> 
  dplyr::mutate(ewr_code_timing = paste0(ewr_code, '_', ewr_code_timing)|>
                  gsub('_$', '', x = _)) |> 
  dplyr::mutate(target = dplyr::case_when(      
    env_group == "NF" ~ "Native fish",
    env_group == "NV" ~ "Native vegetation" ,
    env_group == "OS" ~ "Other species",   
    env_group == "EF" ~ "Priority ecosystem function", 
    env_group == "WB" ~ "Waterbird",
    is.na(env_group) ~ NA
  )
  )

# go to env_obj
ewr2obj <- objective_mapping |> 
  dplyr::select(-env_group) |> 
  dplyr::distinct() |> 
  dplyr::mutate(ewr_code_timing = ifelse(is.na(ewr_code_timing), '', ewr_code_timing)) |> 
  dplyr::mutate(ewr_code_timing = paste0(ewr_code, '_', ewr_code_timing)|>
                  gsub('_$', '', x = _)) |>
  dplyr::mutate(eco_objective_code = stringr::str_remove_all(eco_objective_code, "/xa0"),
                eco_objective_code = stringr::str_replace_all(eco_objective_code, "-", "_")) |> 
  dplyr::mutate(env_obj = strsplit(eco_objective_code, split = '_')) |>
  tidyr::unnest_longer(col = env_obj) |>
  dplyr::select(-eco_objective_code)

# then to Target
obj2target <- ewr2obj |> 
  dplyr::select(-ewr_code, -ewr_code_timing) |> 
  dplyr::mutate(target = dplyr::case_when(grepl('^NF', env_obj) ~ "Native fish",
                                   grepl('^NV', env_obj) ~ "Native vegetation",
                                   grepl('^OS', env_obj) ~ "Other species",
                                   grepl('^EF', env_obj) ~ "Priority ecosystem function",
                                   grepl('^WB', env_obj) ~ "Waterbird",
                                   .default = NA)) |> 
  dplyr::distinct()


# A very Macquarie-particular change
ewr2target <- ewr2target |> 
  dplyr::mutate(target = stringr::str_replace(target, 'Other species', 'Flow-dependent frogs'))
obj2target <- obj2target |> 
  dplyr::mutate(target = stringr::str_replace(target, 'Other species', 'Flow-dependent frogs'))


# a few functions work better with a list of dfs than a bare df.
objective_list <- list(ewr2target)
objective_steps <- list(ewr2obj = ewr2obj, obj2target = obj2target)
```

# Set up sequencing etc

furrr isn't playing nicely with passing in sf by name, so eating a bit of overhead and passing the objects themselves. Doesn't seem to hurt too much.

## Timeseries

The 'timeseries' runs are simpler.

### EWRs-PU-SDL

```{r}
agg_sEt <- list(ewr_code = c("ewr_code_timing", "ewr_code"),
                planning_units = planning_units, 
                sdl_units = sdl_clip)

fun_sEt <- list(c('ArithmeticMean'),
                c('ArithmeticMean'),
                c('ArithmeticMean'))

retained_sEt <- c('sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_ewr_achieved')

cols_sEt <- 'ewr_achieved'

name_sEt <- 'sdl_ewr_timeseries'
```

### target timeseries

```{r}
agg_sTt <- list(ewr_code = c("ewr_code_timing", "ewr_code"),
                env_obj = c('ewr_code', 'env_obj'),
                target = c('env_obj', 'target'),
                planning_units = planning_units, 
                sdl_units = sdl_clip)

fun_sTt <- list(c('ArithmeticMean'),
                c('ArithmeticMean'),
                c('ArithmeticMean'),
                c('ArithmeticMean'),
                c('ArithmeticMean'))

retained_sTt <- c('sdl_units_ArithmeticMean_planning_units_ArithmeticMean_target_ArithmeticMean_env_obj_ArithmeticMean_ewr_code_ArithmeticMean_ewr_achieved')

cols_sTt <- 'ewr_achieved'

name_sTt <- 'sdl_target_timeseries'
```

## 'Spells'?

I think these are the same as above, but we don't retain time and we calculate some other summary variables?

### sdl-ewr-spells

There's some annoying factorial aggregation here, but it's actually reasonably short to write, so I'll just do it.

```{r}
agg_sEs <- list(all_time = 'all_time',
                ewr_code = c("ewr_code_timing", "ewr_code"),
                planning_units = planning_units, 
                sdl_units = sdl_clip)

fun_sEs <- list(c('ArithmeticMean', 'maxInterevent'),
                c('ArithmeticMean', 'Max'),
                c('ArithmeticMean', 'Max'),
                c('ArithmeticMean', 'Max'))

retained_sEs <- c('sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_all_time_ArithmeticMean_ewr_achieved',
                  'sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_all_time_maxInterevent_event_years',
                  'sdl_units_Max_planning_units_Max_ewr_code_Max_all_time_maxInterevent_event_years')

cols_sEs <- c('ewr_achieved', 'event_years')

name_sEs <- 'sdl_ewr_spells'
```

### sdl-target-spells

There's some annoying factorial aggregation here, but it's actually reasonably short to write, so I'll just do it.

```{r}
agg_sTs <- list(all_time = 'all_time',
                ewr_code = c("ewr_code_timing", "ewr_code"),
                env_obj = c('ewr_code', 'env_obj'),
                target = c('env_obj', 'target'),
                planning_units = planning_units, 
                sdl_units = sdl_clip)

fun_sTs <- list(c('ArithmeticMean', 'maxInterevent'),
                c('ArithmeticMean', 'Max'),
                c('ArithmeticMean', 'Max'),
                c('ArithmeticMean', 'Max'),
                c('ArithmeticMean', 'Max'),
                c('ArithmeticMean', 'Max'))

retained_sTs <- c('sdl_units_ArithmeticMean_planning_units_ArithmeticMean_target_ArithmeticMean_env_obj_ArithmeticMean_ewr_code_ArithmeticMean_all_time_ArithmeticMean_ewr_achieved',
                  'sdl_units_ArithmeticMean_planning_units_ArithmeticMean_target_ArithmeticMean_env_obj_ArithmeticMean_ewr_code_ArithmeticMean_all_time_maxInterevent_event_years',
                  'sdl_units_Max_planning_units_Max_target_Max_env_obj_Max_ewr_code_Max_all_time_maxInterevent_event_years')

cols_sTs <- c('ewr_achieved', 'event_years')

name_sTs <- 'sdl_target_spells'
```

## Set up the outer loop lists

```{r}
agg_seqs <- list(agg_sEt, agg_sTt, agg_sEs, agg_sTs)
fun_seqs <- list(fun_sEt, fun_sTt, fun_sEs, fun_sTs)
cols_seqs <- list(cols_sEt, cols_sTt, cols_sEs, cols_sTs)
names_seqs <- list(name_sEt, name_sTt, name_sEs, name_sTs)

futurelist <- list(aggsequence = agg_seqs,
                   funsequence = fun_seqs,
                   aggCols = cols_seqs,
                   aggname = names_seqs,
                   # kind of goofy, but makes the pmap smoother.
                   inner_subdirs = list(inner_subdirs, inner_subdirs, inner_subdirs, inner_subdirs))
```

Nesting furrrs is always tricky, so I'll make a couple helper wrappers.

```{r}
# we need to set up an inner function that loops over the inner_subdirs

# I'll set up a single dir function too.
onedir <- function(subdir, aggsequence, funsequence, aggCols, aggname) {
  oneagg <- read_and_agg(
    datpath = file.path(ewr_results, subdir),
    type = "achievement",
    geopath = bom_basin_gauges,
    causalpath = objective_steps,
    groupers = "scenario",
    aggCols = aggCols,
    aggsequence = aggsequence, # generalise to furr over all agg paths
    funsequence = funsequence, # generalise to furr of all agg paths
    keepAllPolys = FALSE,
    auto_ewr_PU = TRUE,
    saveintermediate = FALSE,
    returnList = FALSE,
    savepath = file.path(project_dir,
                        'aggregated',
                        subdir,
                        aggname) # generalise
  )
}

dirloop <- function(aggsequence, funsequence, aggCols, aggname, inner_subdirs) {
  furrr::future_map(inner_subdirs, /(x) onedir(x, aggsequence, funsequence, 
                                               aggCols, aggname))
  
}

```

```{r}
system.time(aggloop <- furrr::future_pmap(futurelist, dirloop))

```

9600 seconds locally, 600 on Petrichor (with 30 cores x 4 workers)

And a test

```{r}
test_sdl_ewr_ts <- readRDS(file.path(project_dir, 'aggregated', inner_subdirs[100], name_sEt, 'achievement_aggregated.rds'))
test_sdl_target_ts <- readRDS(file.path(project_dir, 'aggregated', inner_subdirs[100], name_sTt, 'achievement_aggregated.rds'))
test_sdl_ewr_spells <- readRDS(file.path(project_dir, 'aggregated', inner_subdirs[100], name_sEs, 'achievement_aggregated.rds'))
test_sdl_target_spells <- readRDS(file.path(project_dir, 'aggregated', inner_subdirs[100], name_sTs, 'achievement_aggregated.rds'))

all(retained_sEt %in% names(test_sdl_ewr_ts))
all(retained_sTt %in% names(test_sdl_target_ts))

all(retained_sTs %in% names(test_sdl_target_spells))
all(retained_sEs %in% names(test_sdl_ewr_spells))
```

Some tests that all files are there.

```{r}

expected_files <- purrr::map(inner_subdirs, /(x) file.path(x, file.path(names_seqs, 'achievement_aggregated.rds'))) |> 
  unlist()

found_files <- list.files(file.path(project_dir, 'aggregated'), 
                          recursive = TRUE, 
                          pattern = 'achievement_aggregated.rds')

all_found <- all(expected_files %in% found_files)
```

```{r}
if (all_found) {
  rlang::inform("All files created")
} else {
  rlang::inform(c("Expected files missing",
                  glue::glue("{expected_files[which(!expected_files %in% found_files)]}")))
}
```

# Testing

```{r}
# readRDS('C:/Users/galen/Deakin University/QAEL - WERP in house - WERP/Toolkit/macquarie/aggregated/historical/MACQ_CC_EFR/licvolfactor_1_0/r0_8_e1_0/sdl_ewr_spells/achievement_aggregated.rds')
```

```{r}
# readRDS('C:/Users/galen/Deakin University/QAEL - WERP in house - WERP/Toolkit/macquarie/aggregated_NOENVOBJ/historical/MACQ_CC_EFR/licvolfactor_1_0/r0_8_e1_0/sdl_ewr_spells/achievement_aggregated.rds')
```

```{r}
# oneagg <- read_and_agg(
#     datpath = file.path(ewr_results, inner_subdirs[1]),
#     type = "achievement",
#     geopath = bom_basin_gauges,
#     causalpath = objective_steps,
#     groupers = "scenario",
#     aggCols = cols_sEs,
#     aggsequence = agg_sEs, # generalise to furr over all agg paths
#     funsequence = fun_sEs, # generalise to furr of all agg paths
#     keepAllPolys = FALSE,
#     auto_ewr_PU = TRUE,
#     saveintermediate = FALSE,
#     returnList = TRUE,
#     savepath = NULL) # generalise
```

```{r}
# oneaggT <- read_and_agg(
#     datpath = file.path(ewr_results, inner_subdirs[1]),
#     type = "achievement",
#     geopath = bom_basin_gauges,
#     causalpath = objective_steps,
#     groupers = "scenario",
#     aggCols = cols_sTs,
#     aggsequence = agg_sTs, # generalise to furr over all agg paths
#     funsequence = fun_sTs, # generalise to furr of all agg paths
#     keepAllPolys = FALSE,
#     auto_ewr_PU = TRUE,
#     saveintermediate = FALSE,
#     returnList = TRUE,
#     savepath = NULL) # generalise
```

```{r}
  # onespells <- read_in_aggs(project_dir = project_dir,
  #                           data_path = file.path(inner_subdirs[1], 'sdl_ewr_spells'),
  #                           lastagg = 'sdl_units',
  #                           retain_cols = retained_sEs,
  #                           max_handling = 'remove',
  #                           factorise = FALSE)
```
