---
title: "Organise data"
format: html
editor: visual
---

```{r setup}
#| include: false
#| warning: false
#| message: false

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file(),
                     cache.lazy = FALSE,
                     warning = FALSE, 
                     message = FALSE)

```

## Data

Data from Ash on his blob. https://sho108storage.blob.core.windows.net/werp-deliverables/

Galen can access via CSIRO Azure account with Azure Storage Explorer. In process of sorting out programmatic access, for now it's just copied down.

This file is just going to extract the zips. The toolkit actually *can* read them straight out of the zip now, but unzipping seems better for clarity.

They're on the QAEL werp drive so we don't all have to have them locally. Very annoyingly, the WERP dir has different names for all of us. So it would be really nice to actually access a blob.

```{r}
#| include: false

source('R/paths.R')

```

```{r}


# 1. allocation_reliability.csv
# 2. allocation_resilience.csv
# 3. hs_delivered_to_ordered_ratio_reliability.csv
# 4. hs_delivered_to_ordered_ratio_resilience.csv
# 5. days_burrendong_lt_dead_storage.csv


```

## allocation_reliability.csv

```{r}
#1.
Files_balance <- list.files(path = list.dirs(path = data_path), pattern = "allocation_reliability.csv", full.names=TRUE)
Files_balance <- Files_balance[!grepl('exp11', Files_balance)] 

read_plus <- function(flnm) {
    readr::read_csv(flnm) |>
    dplyr::mutate(filename = flnm)
}

Merged_balance_init <- do.call(rbind,
          lapply(Files_balance[1], read_plus))

#balance data
for (i in 2:length(Files_balance)) {
  Merged_balance_temp <- do.call(rbind,
          lapply(Files_balance[i], read_plus))
  
Merged_balance_init <- dplyr::bind_rows(Merged_balance_init, Merged_balance_temp)
  
}

#"C:/Users/Admin/Deakin University/QAEL - WERP in house - WERP/Toolkit/macquarie/macq_cut/historical/MACQ_CC_EFR/licvolfactor_1_0/r0_8_e1_0/0/allocation_reliability.csv"

# # get the right scenario name 
Merged_balance <- Merged_balance_init |>
  tidyr::separate(filename, sep = "/", remove = FALSE, 
                  into = c(NA, NA, NA, NA, NA, NA, NA, NA, "Data", "Mk", "licvolfactor", "climate","replicate", "measure"))


write.csv(Merged_balance, file.path(hydro_results, "allocation_reliability_merged.csv")) #453mB

Merged_balance <- NULL
Merged_balance_init <- NULL
Merged_balance_temp <- NULL
```

## allocation_resilience.csv

```{r}
#2.
Files_balance <- list.files(path = list.dirs(path = data_path), pattern = "allocation_resilience.csv", full.names=TRUE)
Files_balance <- Files_balance[!grepl('exp11', Files_balance)] 

read_plus <- function(flnm) {
    readr::read_csv(flnm) |>
    dplyr::mutate(filename = flnm)
}

Merged_balance_init <- do.call(rbind,
          lapply(Files_balance[1], read_plus))

#balance data
for (i in 2:length(Files_balance)) {
  Merged_balance_temp <- do.call(rbind,
          lapply(Files_balance[i], read_plus))
  
Merged_balance_init <- bind_rows(Merged_balance_init, Merged_balance_temp)
  
}

# # get the right scenario name 
Merged_balance <- Merged_balance_init |>
  tidyr::separate(filename, sep = "/", remove = FALSE, 
                  into = c(NA, NA, NA, NA, NA, NA, NA, NA, "Data", "Mk", "licvolfactor", "climate","replicate", "measure"))

write.csv(Merged_balance, file.path(hydro_results, "allocation_resilience_merged.csv"))

Merged_balance <- NULL
Merged_balance_init <- NULL
Merged_balance_temp <- NULL
```

## hs_delivered_to_ordered_ratio_reliability.csv

```{r}
#3.
Files_balance <- list.files(path = list.dirs(path = data_path), pattern = "hs_delivered_to_ordered_ratio_reliability.csv", full.names=TRUE)
Files_balance <- Files_balance[!grepl('exp11', Files_balance)] 

read_plus <- function(flnm) {
    readr::read_csv(flnm) |>
    dplyr::mutate(filename = flnm)
}

Merged_balance_init <- do.call(rbind,
          lapply(Files_balance[1], read_plus))

#balance data
for (i in 2:length(Files_balance)) {
  Merged_balance_temp <- do.call(rbind,
          lapply(Files_balance[i], read_plus))
  
Merged_balance_init <- rbind(Merged_balance_init, Merged_balance_temp)
  
}

# # get the right scenario name 
Merged_balance <- Merged_balance_init |>
  tidyr::separate(filename, sep = "/", remove = FALSE, 
                  into = c(NA, NA, NA, NA, NA, NA, NA, NA, "Data", "Mk", "licvolfactor", "climate","replicate", "measure"))

write.csv(Merged_balance, file.path(hydro_results, "hs_delivered_to_ordered_ratio_reliability_merged.csv"))

Merged_balance <- NULL
Merged_balance_init <- NULL
Merged_balance_temp <- NULL

```

## hs_delivered_to_ordered_ratio_resilience.csv

```{r}
#4.
Files_balance <- list.files(path = list.dirs(path = data_path), pattern = "hs_delivered_to_ordered_ratio_resilience.csv", full.names=TRUE)
Files_balance <- Files_balance[!grepl('exp11', Files_balance)] 

read_plus <- function(flnm) {
    readr::read_csv(flnm) |>
    dplyr::mutate(filename = flnm)
}

Merged_balance_init <- do.call(rbind,
          lapply(Files_balance[1], read_plus))

#balance data
for (i in 2:length(Files_balance)) {
  Merged_balance_temp <- do.call(rbind,
          lapply(Files_balance[i], read_plus))
  
Merged_balance_init <- rbind(Merged_balance_init, Merged_balance_temp)
  
}

# # get the right scenario name 
Merged_balance <- Merged_balance_init |>
  tidyr::separate(filename, sep = "/", remove = FALSE, 
                  into = c(NA, NA, NA, NA, NA, NA, NA, NA, "Data", "Mk", "licvolfactor", "climate","replicate", "measure"))

write.csv(Merged_balance, file.path(hydro_results, "hs_delivered_to_ordered_ratio_resilience_merged.csv"))

Merged_balance <- NULL
Merged_balance_init <- NULL
Merged_balance_temp <- NULL
```

## days_burrendong_lt_dead_storage.csv

```{r}
#1.
Files_balance <- list.files(path = list.dirs(path = data_path), pattern = "days_burrendong_lt_dead_storage.csv", full.names=TRUE)
Files_balance <- Files_balance[!grepl('exp11', Files_balance)] 

read_plus <- function(flnm) {
    readr::read_csv(flnm) |>
    dplyr::mutate(filename = flnm)
}

Merged_balance_init <- do.call(rbind,
          lapply(Files_balance[1], read_plus))
Merged_balance_init <- Merged_balance_init[-1:-2,]


#balance data
for (i in 2:length(Files_balance)) {
  Merged_balance_temp <- do.call(rbind,
          lapply(Files_balance[i], read_plus))
  Merged_balance_temp <- Merged_balance_temp[-1:-2,]
  
Merged_balance_init <- dplyr::bind_rows(Merged_balance_init, Merged_balance_temp)
  
}

#"C:/Users/Admin/Deakin University/QAEL - WERP in house - WERP/Toolkit/macquarie/macq_cut/historical/MACQ_CC_EFR/licvolfactor_1_0/r0_8_e1_0/0/allocation_reliability.csv"

# # get the right scenario name 
Merged_balance <- Merged_balance_init |>
  tidyr::separate(filename, sep = "/", remove = FALSE, 
                  into = c(NA, NA, NA, NA, NA, NA, NA, NA, "Data", "Mk", "licvolfactor", "climate","replicate", "measure"))


write.csv(Merged_balance, file.path(hydro_results, "days_burrendong_lt_dead_storage_merged.csv")) #453mB

Merged_balance <- NULL
Merged_balance_init <- NULL
Merged_balance_temp <- NULL
```

## Temporary aggregator

```{r}

GS_reliability <- read.csv(file.path(hydro_results, "allocation_reliability_merged.csv"))|> #453mB
  dplyr::mutate(measure = "GS_reliability",
                measure_achieved = X02.aal)|>
  dplyr::filter(threshold == 80)|>
  dplyr::select(filename, Data, Mk, licvolfactor, climate, replicate, measure, measure_achieved)

GS_resilience <- read.csv(file.path(hydro_results, "allocation_resilience_merged.csv"))|>
  dplyr::mutate(measure = "GS_resilience",
                measure_achieved = X02.aal)|>
  dplyr::filter(threshold == 80)|>
  dplyr::select(filename, Data, Mk, licvolfactor, climate, replicate, measure, measure_achieved)

# Going to use number of days in dead storage as another metric that will be less ambiguous
# HS_reliability <- read.csv(file.path(hydro_results, "hs_delivered_to_ordered_ratio_reliability_merged.csv"))|>
#   dplyr::mutate(measure = "HS_reliability",
#                 measure_achieved = hs_delivered_to_ordered_ratio,
#                 threshold = threshold*100)|>
#   dplyr::filter(threshold == 80)|>
#   dplyr::select(filename, Data, Mk, licvolfactor, climate, replicate, measure, measure_achieved)

HS_resilience <- read.csv(file.path(hydro_results, "hs_delivered_to_ordered_ratio_resilience_merged.csv"))|>
  dplyr::mutate(measure = "HS_resilience",
                measure_achieved = hs_delivered_to_ordered_ratio,
                threshold = threshold*100)|>
  dplyr::filter(threshold == 80)|>
  dplyr::select(filename, Data, Mk, licvolfactor, climate, replicate, measure, measure_achieved)

days_burrendong_lt_dead_storage <- read.csv(file.path(hydro_results, "days_burrendong_lt_dead_storage_merged.csv"))|>
  dplyr::mutate(measure = "days_burrendong_lt_dead_storage") |>
  dplyr::group_by(filename, Data, Mk, licvolfactor, climate, replicate, measure) |>
  dplyr::summarise(measure_achieved = mean(Current.volume))|>
  dplyr::select(filename, Data, Mk, licvolfactor, climate, replicate, measure, measure_achieved)

Merged_hydrology_summary <- dplyr::bind_rows(GS_reliability, GS_resilience, #HS_reliability, 
                                             HS_resilience, days_burrendong_lt_dead_storage)

write.csv(Merged_hydrology_summary, file = file.path(hydro_results, "Hydrology_summary.csv"))

```

## scenario aggregation

```{r}

Merged_hydrology_summary <- read.csv(file.path(hydro_results, "Hydrology_summary.csv"))

Merged_hydrology_vulnerability <- Merged_hydrology_summary |>
  dplyr::group_by(Data, Mk, licvolfactor, climate, measure)|>
  dplyr::summarise(
    variance_measure_achieved = werptoolkitr::Variance(measure_achieved),
    measure_achieved = mean(measure_achieved))

write.csv(Merged_hydrology_vulnerability, file.path(hydro_results, "sdl_hydrology_vulnerability.csv"))
```
