---
title: "EWR parallel testing"
format: html
editor: visual
---

```{r}
library(werptoolkitr)
library(dplyr)
library(sf) # Needed? I think not here, but just in case
library(future)

# set the future plan for parallelising.
plan(multisession)
```

## Paths

I'm going to set this up to dump data to the QAEL WERP share for now. Unfortunately, that calls itself something different for each of us.

```{r}
if (Sys.info()['user'] == 'galen') {
  qaelpath <- '~/../Deakin University/QAEL - WERP in house - WERP'
} else if (Sys.info()['user'] == 'Georgiad') {
  qaelpath <- '~/Deakin University/QAEL - WERP - WERP'
} else if (Sys.info()['user'] == 'georgiad') {
  #qaelpath <- '~/Deakin University/QAEL - WERP - WERP'
  qaelpath <- 'C:/Users/georgiad/Deakin University/QAEL - WERP - WERP'
} else if (Sys.info()['user'] == 'Admin') {
  qaelpath <- 'C:/Users/Admin/Deakin University/QAEL - WERP in house - WERP'
} else {
  rlang::abort("YOU'RE NOT GALEN. PUT IN YOUR PATH TO QAEL-WERP")
}
```

```{r}
# python can't use the tildes, so have to expand
qaelpath <- path.expand(qaelpath)

# Test on a single directory
project_dir = file.path(qaelpath, 'Toolkit', 'macq-ewr-test')

# Hydrographs
# very short and only one for testing
hydro_dir = file.path(qaelpath, 'Toolkit/AshData/cutout')

# a single set of 76 * 6 runs
hydro_dir = file.path(qaelpath, 'Toolkit/macquarie_cut/stochastic/MACQ_CC_EFR')

# The whole thing- almost certainly a bad idea
# hydro_dir = file.path(qaelpath, 'Toolkit/macquarie_cut')

# The catch here is I need to move them around if I don't do the whole thing. I need a subsetter on prep_run_save_ewrs


# Generated data
# EWR outputs (will be created here in controller, read from here in aggregator)
#ewr_results <- file.path(project_dir, 'module_output', 'EWR_nonrounding')
ewr_results <- file.path(project_dir, 'module_output', 'EWR')

# outputs of aggregator. There may be multiple modules
agg_results <- file.path(project_dir, 'aggregator_output')
```

## Module controls

We need 'summary' and 'yearly' to assess EWR achievement. No reason to return them to the session.

```{r}
outputType <- list('summary', 'yearly')
returnType <- list('none') # list('summary', 'yearly')
```

# Run EWR tool

Run it in parallel, and use the 'IQQM - netcdf\` format. (and note timing)

```{r}

ewr_time <- system.time(ewr_out <- prep_run_save_ewrs(hydro_dir = hydro_dir, 
                                  output_parent_dir = project_dir,
                                  output_subdir = 'stochastic/MACQ_CC_EFR',
                              model_format = 'IQQM - netcdf',
                                  outputType = outputType,
                                  returnType = returnType,
                              rparallel = TRUE))
```

The timing

```{r}
glue::glue("The run of all files through the EWR took {ewr_time['elapsed']} seconds, which is
           {ewr_time['elapsed']/60} minutes, which is
           {ewr_time['elapsed']/60/60} hours")
```

Under a minute for the test. 7.8 hours for the mk4

```{r}
ewr_time5 <- system.time(ewr_out <- prep_run_save_ewrs(hydro_dir = file.path(qaelpath, 'Toolkit/macquarie_cut/stochastic/MACQ_CC_EFR_mkv'), 
                                  output_parent_dir = project_dir,
                                  output_subdir = 'stochastic/MACQ_CC_EFR_mkv',
                              model_format = 'IQQM - netcdf',
                                  outputType = outputType,
                                  returnType = returnType,
                              rparallel = TRUE))
```

```{r}
glue::glue("The run of all files through the EWR took {ewr_time5['elapsed']} seconds, which is
           {ewr_time5['elapsed']/60} minutes, which is
           {ewr_time5['elapsed']/60/60} hours")
```

```{r}
ewr_time5a <- system.time(ewr_out <- prep_run_save_ewrs(hydro_dir = file.path(qaelpath, 'Toolkit/macquarie_cut/stochastic/MACQ_CC_EFR_mkva'), 
                                  output_parent_dir = project_dir,
                                  output_subdir = 'stochastic/MACQ_CC_EFR_mkva',
                              model_format = 'IQQM - netcdf',
                                  outputType = outputType,
                                  returnType = returnType,
                              rparallel = TRUE))
```

```{r}
glue::glue("The run of all files through the EWR took {ewr_time5a['elapsed']} seconds, which is
           {ewr_time5a['elapsed']/60} minutes, which is
           {ewr_time5a['elapsed']/60/60} hours")
```

```{r}
# testing the missings needs the same settings, which aren't necessarily optimized
ewr_time4a <- system.time(ewr_out <- prep_run_save_ewrs(hydro_dir = file.path(qaelpath, 'Toolkit/macquarie_cut/stochastic/MACQ_CC_EFR_mkiv'), 
                                  output_parent_dir = project_dir,
                                  output_subdir = 'stochastic/MACQ_CC_EFR_mkiv',                                  fill_missing = TRUE,
                              model_format = 'IQQM - netcdf',
                                  outputType = outputType,
                                  returnType = returnType,
                              rparallel = TRUE,
                              print_runs = TRUE))
```

Making some changes here to try to get to work with a big set of runs

```{r}
ewr_time4a <- system.time(ewr_out <- prep_run_save_ewrs(hydro_dir = file.path(qaelpath, 'Toolkit/macquarie_cut/stochastic'), 
                                  output_parent_dir = project_dir,
                                  output_subdir = 'stochastic',
                                  file_search = "MACQ_CC_EFR_mkiv",
                                  fill_missing = TRUE,
                              model_format = 'IQQM - netcdf',
                                  outputType = outputType,
                                  returnType = returnType,
                              rparallel = TRUE,
                              print_runs = TRUE))
```

```{r}
glue::glue("The run of all files through the EWR took {ewr_time4a['elapsed']} seconds, which is
           {ewr_time4a['elapsed']/60} minutes, which is
           {ewr_time4a['elapsed']/60/60} hours")
```
