---
title: "Comparer"
format: html
editor: visual
execute: 
  cache: true
---

```{r setup}

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```

## Librarys

```{r}
#| include: false

library(werptoolkitr)
library(dplyr)
library(sf)
library(ggplot2)
library(patchwork)
library(tidyr)
library(ggridges)
#library(future.batchtools)
library(furrr)
```

## Functions

```{r}
source('R/paths.R')
source('R/read_in_aggs.R')
source('R/agg_variables.R')

```

## Data

```{r}
#EWR tool
#Only read in what is necessary

#Economic
sdl_Economic_timeseries <- clean_factors(read.csv(file.path(Economic_results, "Economic_yearly.csv")))
sdl_Economic_timeseries$measure <- "economic_benefit"

sdl_Economic_spells <- clean_factors(read.csv(file.path(Economic_results, "Economic_summary.csv")))
sdl_Economic_spells$measure <- "economic_benefit"
sdl_Economic_spells <- sdl_Economic_spells|>
  dplyr::mutate(scenario = paste(licvolfactor, Evapotranspiration, Rainfall, Mark, Data, replicate, sep = "_"))
dimgroups <- c('measure', 'SWSDLName', "names_CSIRO_climate_scenario")

sdl_Economic_baseline <- werptoolkitr::baseline_compare(val_df = sdl_Economic_spells,
                            compare_col = 'scenario',
                            base_lev = "1_1_1_Mk4a_Historic_0",
                            group_cols = dimgroups,
                            comp_fun = relative,
                            values_col = 'economic_benefit',
                            failmissing = FALSE)

sdl_economic_vulnerability <- clean_factors(read.csv(file.path(Economic_results, "sdl_economic_vulnerability.csv")))
sdl_economic_vulnerability$measure <- "economic_benefit"

#Hydrology
#there are no timeseries
sdl_hydrology_spells <- clean_factors(read.csv(file.path(hydro_results, "Hydrology_summary.csv")))
sdl_hydrology_spells <- sdl_hydrology_spells|>
  dplyr::mutate(scenario = paste(licvolfactor, Evapotranspiration, Rainfall, Mark, Data, replicate, sep = "_"))
dimgroups <- c('measure', 'SWSDLName', "names_CSIRO_climate_scenario")

sdl_hydrology_baseline <- werptoolkitr::baseline_compare(val_df = sdl_hydrology_spells,
                            compare_col = 'scenario',
                            base_lev = "1_1_1_Mk4a_Historic_0",
                            group_cols = dimgroups,
                            comp_fun = relative,
                            values_col = 'measure_achieved',
                            failmissing = FALSE)


sdl_hydrology_vulnerability <- clean_factors(read.csv(file.path(hydro_results, "sdl_hydrology_vulnerability.csv")))

rm(sdl_Economic_spells)
rm(sdl_hydrology_spells)

```

## Palettes

```{r}
#| label: palettes
#| include: false



sdl_ewr_vulnerability <- read_in_aggs(project_dir = project_dir,
                          data_type = 'historical',
                          info_list = aggregation_info,
                          aggname = 'sdl_ewr_vulnerability',
                            mark = 'all',
                            licvol = 'all',
                            climate = 'all',
                          max_handling = "remove")

scenarios <- sdl_ewr_vulnerability |>
  distinct(Rainfall, Evapotranspiration, licvolfactor, Mark)
rm(sdl_ewr_vulnerability)

# Qualitative
# pal_SDL <- make_pal(unique(sdl_objective_nonrounding_agg$sdl_units$SWSDLName), 
#                     palette = "impressionist.colors::la_recolte_des_foins_eragny")

# pal_gauge <- make_pal(unique(gauges_to_plot),                       
#                       palette = 'ggsci::nrc_npg')

scale_evap_pal <- make_pal(as.character(unique(scenarios$Evapotranspiration)),
                      palette = 'nationalparkcolors::Redwoods')

scale_rain_pal <- make_pal(as.character(unique(scenarios$Rainfall)),
                      palette = 'nationalparkcolors::Redwoods')

# pal_scale_evap_historical_comp <- make_pal(as.character(unique(scenarios$names_scale_evap_historical_comp)),
#                       palette = 'nationalparkcolors::Redwoods')

# pal_scenario <- make_pal(rev(as.character(unique(scenarios$scenario))),
#                       palette = 'scico::roma')

pal_climate_scenario <- make_pal(
  rev(c("SR0.8_SE1.07", "SR0.8_SE1.00", "SR1.0_SE1.07",
         "SR1.0_SE1.00", "SR1.2_SE1.07", "SR1.2_SE1.00", NA)),
                      palette = 'scico::imola')

# pal_MDBA_climate_scenario <- make_pal(rev(as.character(unique(scenarios$names_MDBA_climate_scenario))),
#                       palette = 'scico::roma')

pal_licvolfactor <- make_pal(as.character(unique(scenarios$licvolfactor)),
                      palette = 'scico::cork')

# these have to use quantitative even though they're not, or we run out of colors.
pal_env = list(EB = 'grDevices::Grays',
                EF = 'grDevices::Purp',
                NF = 'grDevices::Mint',
                NV = 'grDevices::Burg',
                OS = 'grDevices::Blues 2',
                WB = 'grDevices::Peach')

# use the first level of each of those to make a named pal. I wish there were an easier way
pal_envgroup <- purrr::imap_chr(pal_env,
                                \(x,y) make_pal(levels = y, palette = x)) |> 
  werptoolkitr:::as_colors()

pal_Target <-  stats::setNames(c("#1B1B1BFF", "#A1D8B6FF", "#005D67FF", "#67223FFF", "#023FA5FF", "#EA4C3BFF", 
                                 "#4873B8", "#B7A447", "#FDC010"), 
            c('Priority ecosystem function', 'Native fish', 'Native vegetation', 'Other species', 'Waterbirds', 
               "End of system flows", "Water allocation", "Agricultural benefits"))
class(pal_Target) <- 'colors'

pal_EWR <- stats::setNames(c("#555555FF", '#7B3014FF', "#9E3D22FF", '#C35322FF', '#E77129FF', '#F59843FF',
                                            '#FCAD52FF', '#FFC07CFF', '#FFEDDAFF', '#D6E8F3FF', '#A3CCE5FF', '#7DAED1FF',
                                            '#6094BFFF', '#4677A5FF', '#2B5C8AFF'), 
                                          c("CF", "VF", "BF1", "BF2", "SF1", "SF2",
                                            "SF3", "LF1", "LF2", "OB-WL", "OB-WM", "OB-WS1",
                                            "OB-WS2", "OB-WS3", "OB-WS4"))
class(pal_EWR) <- 'colors'

pal_hydro <- stats::setNames(c("#7F0038FF", '#C31E6EFF', "#326812FF", '#033800FF', "#7640A9FF"),
                             c("GS_reliability", "GS_resilience", "HS_reliability", "HS_resilience", "economic_benefit"))
class(pal_hydro) <- 'colors'

pal_theme <- stats::setNames(c("#1B1B1BFF", "#A1D8B6FF", "#005D67FF", "#67223FFF", "#023FA5FF", "#EA4C3BFF", 
                                 "#4873B8", "#B7A447", "#FDC010", "#7F0038FF", '#C31E6EFF', "#326812FF", '#033800FF', "#7640A9FF"),
                             c('Priority ecosystem function', 'Native fish', 'Native vegetation', 'Other species', 'Waterbirds', 
               "End of system flows", "Water allocation", "Agricultural benefits", "GS_reliability", "GS_resilience", "HS_reliability", "HS_resilience", "economic_benefit"))
class(pal_theme) <- 'colors'


# Quantitative- sequential achievement
pal_achieve <- 'grDevices::Blue-Yellow'

# quantitative- diverging achievement (e.g. relative to baseline)
pal_compare <- 'scico::bam'

pal_scene <- make_pal(unique(scenarios$scenario),                       
                      palette = "viridis::mako", #'ggsci::nrc_npg', 
                      refvals = 'base', refcols = 'black')

# Data sets
shapes_data <- c(21,24)
names(shapes_data) <- c("Historic", "Stochastic")

shapes_data2 <- c(24,21)
names(shapes_data2) <- c("Stochastic", "Historic")

linetype_data <- c("dotted", "solid")
names(linetype_data) <- c("Historic", "Stochastic")

linetype_data2 <- c("solid", "dotted")
names(linetype_data2) <- c("Stochastic", "Historic")


pal_CSIRO_climate_scenario <- stats::setNames(
  c('#2166ACFF', '#92C5DEFF', '#F7F7F7FF',  '#F4A582FF', '#D6604DFF', '#B2182BFF', '#1A1A1AFF'),
  c("Just Wet", "Hot and Wet", "Historical climate",  "Just Hot", "Just Dry", "Hot and Dry", NA))
class(pal_CSIRO_climate_scenario) <- 'colors'

SWSDLName_subset <-  "Macquarie–Castlereagh"

#maybe make palette based on end of sys flow???


```

## MAP

```{r}
gauges_df <- get_ewr_gauges()|>
  #st_drop_geometry() |>
  mutate(OWNER = case_when(owner == "NSW - NSW Department of Industry – Lands and Water" ~ "NSW",
                           owner == "VIC - Department of Environment, Land, Water and Planning"~ "VIC",
                           owner == "SA - Department of Environment, Water and Natural Resources"~ "SA",
                           owner == "QLD - Department of Natural Resources, Mines and Energy"~ "QLD",
                           owner == NA ~ NA))

Map_Macquarie <- ggplot(data = sdl_units,  aes(geometry = geometry)) +
  geom_sf(fill = "white")+
  geom_sf(data = filter(gauges_df, gauge %in% gauges_to_plot),  aes(geometry = geometry), colour = "#fcaa20")+
  geom_sf(data = filter(sdl_units, SWSDLName == SWSDLName_subset),  aes(geometry = geometry), fill = "#fcaa20", colour = "#fcaa20", alpha = 0.1)+ 
  geom_sf_text(data = filter(sdl_units, SWSDLName == SWSDLName_subset), aes(label = SWSDLName), colour = "#fcaa20") +
  theme(legend.position = "none")+
  theme_werp_toolkit(legend.position = "none")

Map_Macquarie

ggsave(plot = Map_Macquarie, filename = file.path(comp_results, paste0("Map_Macquarie", Sys.Date(), ".tiff")), device = "tiff",
       width = 8, height = 5)
```

## 1A) Vulnerability - no climate change

```{r}
sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = c('licvolfactor_1_0',"licvolfactor_1_0"),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

mean_EWR_Stoch_var <- mean(filter(sdl_EWR_vulnerability, Data == "Stochastic")$variance_ewr_achieved) #0.01 
mean_target_Stoch_var <- mean(filter(sdl_target_vulnerability, Data == "Stochastic")$variance_ewr_achieved)
mean_hydro_Stoch_var <- mean(filter(sdl_hydrology_vulnerability, Data == "Stochastic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a")$variance_measure_achieved)
mean_hydro_Stoch_ach <- mean(filter(sdl_hydrology_vulnerability, Data == "Stochastic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a")$measure_achieved)
mean_economic_Stoch_var <- mean(filter(sdl_economic_vulnerability, Data == "Stochastic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a")$variance_economic_benefit)
mean_economic_Stoch_ach <- mean(filter(sdl_economic_vulnerability, Data == "Stochastic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a")$economic_benefit)


#EWR
plot_sdl_EWR_vulnerability_S_noclimate <- ggplot(data = filter(sdl_EWR_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none")+
  geom_vline(xintercept = 0.5) +
    geom_hline(yintercept = mean_EWR_Stoch_var) +
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_EWR_vulnerability_H_noclimate <- ggplot(data = filter(sdl_EWR_vulnerability, Data == "Historic"), 
                                                 #V1#aes(y = factor(variance_ewr_achieved), 
                                                 aes(y = factor(ewr_code),
                                                 x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))

#TARGET
plot_sdl_target_vulnerability_S_noclimate <- ggplot(data = filter(sdl_target_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none")+
  geom_vline(xintercept = 0.5) +
    geom_hline(yintercept = mean_target_Stoch_var) +
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_target_vulnerability_H_noclimate <- ggplot(data = filter(sdl_target_vulnerability, Data == "Historic"), 
                                                    #V1#aes(y = factor(variance_ewr_achieved), 
                                                    aes(y = target, 
                                                    x = ewr_achieved, colour = target, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))

#Hydrology:
plot_sdl_hydro_vulnerability_S_noclimate <- ggplot(data = filter(sdl_hydrology_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none")+
  geom_vline(xintercept = mean_hydro_Stoch_ach) +
    geom_hline(yintercept = mean_hydro_Stoch_var) +
  scale_colour_manual(values = pal_hydro) +
  scale_shape_manual(values = shapes_data2)# +
  #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_hydro_vulnerability_H_noclimate <- ggplot(data = filter(sdl_hydrology_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a"), 
                                                   #V1#aes(y = factor(variance_measure_achieved), 
                                                   aes(y = factor(measure), 
                                                   x = measure_achieved, colour = measure, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_hydro_Stoch_ach) +
  scale_colour_manual(values = pal_hydro)+
  scale_shape_manual(values = shapes_data2)#+
  #coord_cartesian(xlim = c(0,1))

#Economic:
plot_sdl_economic_vulnerability_S_noclimate <- ggplot(data = filter(sdl_economic_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a"), aes(y = variance_economic_benefit, x = economic_benefit, colour = measure, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none")+
  geom_vline(xintercept = mean_economic_Stoch_ach) +
  geom_hline(yintercept = mean_economic_Stoch_var) +
  scale_colour_manual(values = pal_hydro) +
  scale_shape_manual(values = shapes_data2)# +
  #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_economic_vulnerability_H_noclimate <- ggplot(data = filter(sdl_economic_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a"), 
                                                      #V1#aes(y = factor(variance_economic_benefit), 
                                                      aes(y = factor(measure), 
                                                          x = economic_benefit, colour = measure, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_economic_Stoch_ach) +
  scale_colour_manual(values = pal_hydro)+
  scale_shape_manual(values = shapes_data2)#+
  #coord_cartesian(xlim = c(0,1))


```

## 1B) Vulnerability - no climate change - with licvol

There are no economic data for licvol (other than historic/no change licvol)

```{r}
sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = "all",#c('licvolfactor_1_0', 'licvolfactor_1_5', 'licvolfactor_0_5'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = "all",#c('licvolfactor_1_0', 'licvolfactor_1_5', 'licvolfactor_0_5'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

#EWR
plot_sdl_EWR_vulnerability_S_licvol <- ggplot(data = filter(sdl_EWR_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = 0.5) +
    geom_hline(yintercept = mean_EWR_Stoch_var) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_EWR_vulnerability_H_licvol <- ggplot(data = filter(sdl_EWR_vulnerability, Data == "Historic"), 
                                              #V1#aes(y = factor(variance_ewr_achieved),
                                              aes(y = ewr_code,
                                                  x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))

#Target
plot_sdl_target_vulnerability_S_licvol <- ggplot(data = filter(sdl_target_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = target, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = 0.5) +
    geom_hline(yintercept = mean_target_Stoch_var) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_target_vulnerability_H_licvol <- ggplot(data = filter(sdl_target_vulnerability, Data == "Historic"), 
                                                 #V1#aes(y = factor(variance_ewr_achieved), 
                                                 aes(y = target, 
                                                     x = ewr_achieved, colour = target, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = target, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))

#Hydrology:
plot_sdl_hydro_vulnerability_S_licvol <- ggplot(data = filter(sdl_hydrology_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = measure, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = mean_hydro_Stoch_ach) +
    geom_hline(yintercept = mean_hydro_Stoch_var) +
  scale_fill_manual(values = pal_hydro)+
  scale_colour_manual(values = pal_hydro) +
  scale_shape_manual(values = shapes_data2)# +
  #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_hydro_vulnerability_H_licvol <- ggplot(data = filter(sdl_hydrology_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), 
                                                #V1#aes(y = factor(variance_measure_achieved), 
                                                aes(y = measure, 
                                                    x = measure_achieved, colour = measure, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = measure, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_hydro_Stoch_ach) +
  scale_fill_manual(values = pal_hydro)+
  scale_colour_manual(values = pal_hydro)+
  scale_shape_manual(values = shapes_data2)#+
  #coord_cartesian(xlim = c(0,1))

#Economic:
# plot_sdl_economic_vulnerability_S_licvol <- ggplot(data = filter(sdl_economic_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), aes(y = variance_economic_benefit, x = economic_benefit, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = licvolfactor)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal")+
#   geom_vline(xintercept = mean_economic_Stoch_ach) +
#   geom_hline(yintercept = mean_economic_Stoch_var) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro) +
#   scale_shape_manual(values = shapes_data2)# +
#   #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_economic_vulnerability_H_licvol <- ggplot(data = filter(sdl_economic_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), 
                                                   #V1#aes(y = factor(variance_economic_benefit),
                                                   aes(y = measure, 
                                                       x = economic_benefit, colour = measure, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = measure, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_economic_Stoch_ach) +
  scale_fill_manual(values = pal_hydro)+
  scale_colour_manual(values = pal_hydro)+
  scale_shape_manual(values = shapes_data2)#+
  #coord_cartesian(xlim = c(0,1))

```

## 1C) Vulnerability - no climate change - with diff marks
Marks are irrelevant for Economic results

```{r}
sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = "all",#c("MACQ_CC_EFR", 'MACQ_CC_EFR_mkiv', "MACQ_CC_EFR_mkv"), 
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = "all",#c("MACQ_CC_EFR", 'MACQ_CC_EFR_mkiv', "MACQ_CC_EFR_mkv"), 
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

#EWR
plot_sdl_EWR_vulnerability_S_mks <- ggplot(data = filter(sdl_EWR_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = 0.5) +
    geom_hline(yintercept = mean_EWR_Stoch_var) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_EWR_vulnerability_H_mks <- ggplot(data = filter(sdl_EWR_vulnerability, Data == "Historic"), 
                                           #V1#aes(y = factor(variance_ewr_achieved), 
                                           aes(y = ewr_code, 
                                               x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))

#TARGET
plot_sdl_target_vulnerability_S_mks <- ggplot(data = filter(sdl_target_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = target, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = 0.5) +
  geom_hline(yintercept = mean_target_Stoch_var) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_target_vulnerability_H_mks <- ggplot(data = filter(sdl_target_vulnerability, Data == "Historic"), 
                                              #V1#aes(y = factor(variance_ewr_achieved),
                                              aes(y = target, 
                                                  x = ewr_achieved, colour = target, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = target, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))

#Hydrology:
plot_sdl_hydro_vulnerability_S_mks <- ggplot(data = filter(sdl_hydrology_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = measure, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = mean_hydro_Stoch_ach) +
    geom_hline(yintercept = mean_hydro_Stoch_var) +
  scale_fill_manual(values = pal_hydro)+
  scale_colour_manual(values = pal_hydro) +
  scale_shape_manual(values = shapes_data2)# +
  #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_hydro_vulnerability_H_mks <- ggplot(data = filter(sdl_hydrology_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0), 
                                             #V1#aes(y = factor(variance_measure_achieved), 
                                             aes(y = measure, 
                                                 x = measure_achieved, colour = measure, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = measure, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_hydro_Stoch_ach) +
  scale_fill_manual(values = pal_hydro)+
  scale_colour_manual(values = pal_hydro)+
  scale_shape_manual(values = shapes_data2)#+
  #coord_cartesian(xlim = c(0,1))

#Economic:
# plot_sdl_economic_vulnerability_S_mks <- ggplot(data = filter(sdl_economic_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), aes(y = variance_economic_benefit, x = economic_benefit, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = licvolfactor)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal")+
#   geom_vline(xintercept = mean_economic_Stoch_ach) +
#   geom_hline(yintercept = mean_economic_Stoch_var) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro) +
#   scale_shape_manual(values = shapes_data2)# +
#   #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

# plot_sdl_economic_vulnerability_H_mks <- ggplot(data = filter(sdl_economic_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), aes(y = factor(variance_economic_benefit), x = economic_benefit, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = licvolfactor)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal",
#         axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
#   geom_vline(xintercept = mean_economic_Stoch_ach) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro)+
#   scale_shape_manual(values = shapes_data2)#+
#   #coord_cartesian(xlim = c(0,1))

```

## 1D) Vulnerability - With climate change
```{r}
sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR_mkiv'), 
                                    licvol = c('licvolfactor_1_0'),
                                    climate = "all",#c('r0_8_e1_07', 'r1_0_e1_0', 'r1_2_e1_0'),
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR_mkiv'), 
                                    licvol = c('licvolfactor_1_0'),
                                    climate = "all",#c('r0_8_e1_07', 'r1_0_e1_0', 'r1_2_e1_0'),
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

#EWR
plot_sdl_EWR_vulnerability_S_climate <- ggplot(data = filter(sdl_EWR_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = 0.5) +
    geom_hline(yintercept = mean_EWR_Stoch_var) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.02))#, ylim = c(0 , 0.003))

plot_sdl_EWR_vulnerability_H_climate <- ggplot(data = filter(sdl_EWR_vulnerability, Data == "Historic"), 
                                               #V1#aes(y = factor(variance_ewr_achieved), 
                                                   aes(y = ewr_code,
                                                   x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1), ylim = c(0, 0.02))

#TARGET
plot_sdl_target_vulnerability_S_climate <- ggplot(data = filter(sdl_target_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = target, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = 0.5) +
  geom_hline(yintercept = mean_target_Stoch_var) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
  coord_cartesian(xlim = c(0,1), ylim = c(0, 0.02))

plot_sdl_target_vulnerability_H_climate <- ggplot(data = filter(sdl_target_vulnerability, Data == "Historic"), 
                                                  #V1#aes(y = factor(variance_ewr_achieved), 
                                                      aes(y = target, 
                                                      x = ewr_achieved, colour = target, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = target, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1), ylim = c(0, 0.02))

#Hydrology:
plot_sdl_hydro_vulnerability_S_climate <- ggplot(data = filter(sdl_hydrology_vulnerability, licvolfactor == 1.0 & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = measure, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = mean_hydro_Stoch_ach) +
    geom_hline(yintercept = mean_hydro_Stoch_var) +
  scale_fill_manual(values = pal_hydro)+
  scale_colour_manual(values = pal_hydro) +
  scale_shape_manual(values = shapes_data2)# +
  #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_hydro_vulnerability_H_climate <- ggplot(data = filter(sdl_hydrology_vulnerability, Data == "Historic" & licvolfactor == 1.0 & Mark == "Mk4a"), 
                                                 #V1#aes(y = factor(variance_measure_achieved), 
                                                     aes(y = measure,
                                                     x = measure_achieved, colour = measure, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = measure, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_hydro_Stoch_ach) +
  scale_fill_manual(values = pal_hydro)+
  scale_colour_manual(values = pal_hydro)+
  scale_shape_manual(values = shapes_data2)#+
  #coord_cartesian(xlim = c(0,1))

#Economic:
plot_sdl_economic_vulnerability_S_climate <- ggplot(data = filter(sdl_economic_vulnerability, licvolfactor == 1.0 & Mark == "Mk4a"), aes(y = variance_economic_benefit, x = economic_benefit, colour = measure, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = measure, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = mean_economic_Stoch_ach) +
  geom_hline(yintercept = mean_economic_Stoch_var) +
  scale_fill_manual(values = pal_hydro)+
  scale_colour_manual(values = pal_hydro) +
  scale_shape_manual(values = shapes_data2)# +
  #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_economic_vulnerability_H_climate <- ggplot(data = filter(sdl_economic_vulnerability, Data == "Historic" & licvolfactor == 1.0 & Mark == "Mk4a"), 
                                                    #V1#aes(y = factor(variance_measure_achieved), 
                                                    aes(y = measure,
                                                    x = economic_benefit, colour = measure, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = measure, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_economic_Stoch_ach) +
  scale_fill_manual(values = pal_hydro)+
  scale_colour_manual(values = pal_hydro)+
  scale_shape_manual(values = shapes_data2)#+
  #coord_cartesian(xlim = c(0,1))

```

## Figure 1 - Stochastic

```{r}

#EWR
VulnerabilityPlot_EWR_Stochastic <- plot_sdl_EWR_vulnerability_S_noclimate + plot_sdl_EWR_vulnerability_S_licvol + 
plot_sdl_EWR_vulnerability_S_mks + plot_sdl_EWR_vulnerability_S_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.02))&
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

#TARGET
VulnerabilityPlot_target_Stochastic <- plot_sdl_target_vulnerability_S_noclimate + plot_sdl_target_vulnerability_S_licvol + 
plot_sdl_target_vulnerability_S_mks + plot_sdl_target_vulnerability_S_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
  coord_cartesian(xlim = c(0,1), ylim = c(0 , 0.003))&
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

#Hydrology
VulnerabilityPlot_WaterAllocation_Stochastic <- plot_sdl_hydro_vulnerability_S_noclimate + plot_sdl_hydro_vulnerability_S_licvol + 
plot_sdl_hydro_vulnerability_S_mks + plot_sdl_hydro_vulnerability_S_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
  coord_cartesian(ylim = c(0, 0.2)) &
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

#Economic
VulnerabilityPlot_Economic_Stochastic <- plot_sdl_economic_vulnerability_S_noclimate + plot_spacer() + 
plot_spacer() + plot_sdl_economic_vulnerability_S_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
  coord_cartesian(xlim = c(90000,130000),ylim = c(2500000, 5000000)) &
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

ggsave(plot = VulnerabilityPlot_EWR_Stochastic, filename = file.path(comp_results, paste0("VulnerabilityPlot_EWR_Stochastic",Sys.Date(),".tiff")), device = "tiff", width = 7, height = 5)

ggsave(plot = VulnerabilityPlot_target_Stochastic, filename = file.path(comp_results, paste0("VulnerabilityPlot_target_Stochastic",Sys.Date(),".tiff")), device = "tiff", width = 7, height = 5)

ggsave(plot = VulnerabilityPlot_WaterAllocation_Stochastic, filename = file.path(comp_results, paste0("VulnerabilityPlot_WaterAllocation_Stochastic",Sys.Date(),".tiff")), device = "tiff", width = 7, height = 5)

ggsave(plot = VulnerabilityPlot_Economic_Stochastic, filename = file.path(comp_results, paste0("VulnerabilityPlot_Economic_Stochastic",Sys.Date(),".tiff")), device = "tiff", width = 7, height = 5)

VulnerabilityPlot_EWR_Stochastic
VulnerabilityPlot_target_Stochastic
VulnerabilityPlot_WaterAllocation_Stochastic
VulnerabilityPlot_Economic_Stochastic

```
## Figure 1 - Historic
```{r}
#EWR
VulnerabilityPlot_EWR_Historic <- plot_sdl_EWR_vulnerability_H_noclimate + plot_sdl_EWR_vulnerability_H_licvol + 
plot_sdl_EWR_vulnerability_H_mks + plot_sdl_EWR_vulnerability_H_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
  coord_cartesian(xlim = c(0,1))&
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

#TARGET
VulnerabilityPlot_target_Historic <- plot_sdl_target_vulnerability_H_noclimate + plot_sdl_target_vulnerability_H_licvol + 
plot_sdl_target_vulnerability_H_mks + plot_sdl_target_vulnerability_H_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
  coord_cartesian(xlim = c(0,1))&
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

#Hydrology
VulnerabilityPlot_WaterAllocation_Historic <- plot_sdl_hydro_vulnerability_H_noclimate + plot_sdl_hydro_vulnerability_H_licvol + 
plot_sdl_hydro_vulnerability_H_mks + plot_sdl_hydro_vulnerability_H_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") &
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

#Economic
VulnerabilityPlot_Economic_Historic <- plot_sdl_economic_vulnerability_H_noclimate + plot_sdl_economic_vulnerability_H_licvol + 
plot_spacer() + plot_sdl_economic_vulnerability_H_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
  coord_cartesian(xlim = c(90000,130000))& 
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

ggsave(plot = VulnerabilityPlot_EWR_Historic, filename = file.path(comp_results, paste0("VulnerabilityPlot_EWR_Historic",Sys.Date(),".tiff")), device = "tiff", width = 7, height = 5)

ggsave(plot = VulnerabilityPlot_target_Historic, filename = file.path(comp_results, paste0("VulnerabilityPlot_target_Historic",Sys.Date(),".tiff")), device = "tiff", width = 7, height = 5)

ggsave(plot = VulnerabilityPlot_WaterAllocation_Historic, filename = file.path(comp_results, paste0("VulnerabilityPlot_WaterAllocation_Historic",Sys.Date(),".tiff")), device = "tiff", width = 7, height = 5)

ggsave(plot = VulnerabilityPlot_Economic_Historic, filename = file.path(comp_results, paste0("VulnerabilityPlot_Economic_Historic",Sys.Date(),".tiff")), device = "tiff", width = 7, height = 5)

VulnerabilityPlot_EWR_Historic
VulnerabilityPlot_target_Historic
VulnerabilityPlot_WaterAllocation_Historic
VulnerabilityPlot_Economic_Historic

```


## 2) Temporal variability - stochastic error band with historic data - no climate change

We dont have time series for Water allocation data (or at least Deakin dont)

```{r}

sdl_EWR_timeseries <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_ewr_timeseries',
                                    max_handling = "remove")

sdl_target_timeseries <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_timeseries',
                                    max_handling = "remove")

#EWR
plot_sdl_EWR_temporal_variability <- sdl_EWR_timeseries|> 
  ggplot(aes(x = ewr_achieved, colour = ewr_code, linetype = Data)) + 
  stat_ecdf(data = sdl_EWR_timeseries, aes(group = scenario), alpha = 0.1) + 
  stat_ecdf(data = sdl_EWR_timeseries, geom = "step", colour = "black") +
  theme_werp_toolkit()+ 
  scale_colour_manual(values = pal_EWR)+ 
  scale_fill_manual(values = pal_EWR)+ 
  scale_linetype_manual(values = linetype_data)+
  facet_wrap(~ewr_code)

#TARGET
plot_sdl_target_temporal_variability <- sdl_target_timeseries|> 
  filter(Evapotranspiration == 1.00 & Rainfall== 1.0 & licvolfactor == 1.0)|>
  ggplot(aes(x = ewr_achieved, colour = env_group, linetype = Data)) + 
  stat_ecdf(data = sdl_target_timeseries, aes(group = scenario), alpha = 0.1) + 
  stat_ecdf(data = sdl_target_timeseries, geom = "step", colour = "black") +
  theme_werp_toolkit()+ 
  scale_colour_manual(values = pal_envgroup)+ 
  scale_fill_manual(values = pal_envgroup)+ 
  scale_linetype_manual(values = linetype_data)+
  facet_wrap(~env_group)

#EWR
plot_sdl_Economic_temporal_variability <- sdl_Economic_timeseries|> 
  filter(names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a")|>
  ggplot(aes(x = economic_benefit, colour = measure, linetype = Data)) + 
  stat_ecdf(data = sdl_Economic_timeseries, aes(group = replicate), alpha = 0.1) + 
  stat_ecdf(data = sdl_Economic_timeseries, geom = "step", colour = "black") +
  theme_werp_toolkit()+ 
  scale_colour_manual(values = pal_hydro)+ 
  scale_fill_manual(values = pal_hydro)+ 
  scale_linetype_manual(values = linetype_data)+
  facet_wrap(~measure)

ggsave(plot = plot_sdl_EWR_temporal_variability, filename = file.path(comp_results, paste0("CDF", "plot_sdl_EWR_temporal_variability_stochasticErrorBand_historic",Sys.Date(),".tiff")), device = "tiff", width = 8, height = 6)

ggsave(plot = plot_sdl_target_temporal_variability, filename = file.path(comp_results, paste0("CDF", "plot_sdl_target_temporal_variability_stochasticErrorBand_historic",Sys.Date(),".tiff")), device = "tiff", width = 8, height = 4)

ggsave(plot = plot_sdl_Economic_temporal_variability, filename = file.path(comp_results, paste0("CDF", "plot_sdl_Economic_temporal_variability",Sys.Date(),".tiff")), device = "tiff", width = 4, height = 2)

plot_sdl_EWR_temporal_variability
plot_sdl_target_temporal_variability
plot_sdl_Economic_temporal_variability
```

## NULL DATA
all non-events evenly dispered in the time series or all at one end

```{r}

null_data <- data.frame(
  ewr_achieved = seq(from = 0, to = 1, by = 0.01),
  ewr_code = "CF",
  env_group = "NF",
  Data = "Null model")

null_data <- null_data |>
  mutate(n_years_achieved = 130*ewr_achieved,
         n_years_not_achieved = 130*(1-ewr_achieved),
         mean_max_interevent = n_years_not_achieved/n_years_achieved)|>
  mutate(mean_max_interevent = ifelse(mean_max_interevent == Inf, 130, mean_max_interevent),
         Data = "Stochastic")

null_data1 <- null_data
null_data1$Data <- "Historic"

null_data <- bind_rows(null_data, null_data1)

```

## 3) Spells plot- stochastic + historic data - no climate change
i dont think we can calculate interevent periods for economic or water allocation data

```{r}

sdl_ewr_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_ewr_baseline',
                                    max_handling = "remove")

sdl_target_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_target_baseline',
                                    max_handling = "remove")

Spellsplot_sdl_EWR <- sdl_ewr_baseline |>
  filter(Mark == "Mk4a" & licvolfactor == 1.0 & names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot(aes(y = mean_max_interevent, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_point() +
  geom_line(data = null_data, aes(y = mean_max_interevent, x = ewr_achieved), colour = "black")+
  geom_line(data = null_data, aes(y = n_years_not_achieved, x = ewr_achieved), colour = "black")+
  facet_wrap(~Data)+
  theme_werp_toolkit()+
  # labs(y = "Mean Maximum_interevent_duration",
  #      x = "Mean ewr_achieved")+
  scale_colour_manual(values = pal_EWR) +
  scale_shape_manual(values = shapes_data2)

#TARGET
Spellsplot_sdl_target <- sdl_target_baseline |>
  filter(Mark == "Mk4a" & licvolfactor == 1.0 & names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot(aes(y = mean_max_interevent, x = ewr_achieved, colour = env_group, shape = Data)) + 
  geom_point() +
  geom_line(data = null_data, aes(y = mean_max_interevent, x = ewr_achieved), colour = "black")+
  geom_line(data = null_data, aes(y = n_years_not_achieved, x = ewr_achieved), colour = "black")+
  facet_wrap(~Data)+
  theme_werp_toolkit()+
  # labs(y = "Mean Maximum_interevent_duration",
  #      x = "Mean ewr_achieved")+
  scale_colour_manual(values = pal_envgroup) +
  scale_shape_manual(values = shapes_data)

ggsave(plot = Spellsplot_sdl_EWR, filename = file.path(comp_results, paste0("Spellsplot_sdl_EWR",Sys.Date(),".tiff")), device = "tiff", width = 8, height = 4)

ggsave(plot = Spellsplot_sdl_target, filename = file.path(comp_results, paste0("Spellsplot_sdl_target",Sys.Date(),".tiff")), device = "tiff", width = 8, height = 4)

```

## 4) Variability - no climate change

```{r}
plot_sdl_EWR_variability_scatter <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() + 
  geom_jitter(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),
              height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic" & 
                             Mark == "Mk4a" & 
                             licvolfactor == 1.0 & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))

#TARGET
plot_sdl_target_variability_scatter <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() + 
  geom_jitter(aes(y = ewr_achieved, x = target, colour = target, shape = Data),
              height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_target_baseline, 
                           Mark == "Mk4a" & 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = ewr_achieved, x = target, colour = target, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))

#Hydrology
plot_sdl_Hydrology_variability_scatter <- sdl_hydrology_spells |>
  filter(Data == "Stochastic" & 
           names_CSIRO_climate_scenario == "Historical climate" & 
           licvolfactor == 1.0 & 
           Mark == "Mk4a")) + 
  ggplot()+
  geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_hydrology_spells, 
                           Data == "Historic" & 
                             Mark == "Mk4a" & 
                             licvolfactor == 1.0 & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = measure_achieved, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_hydro)+
  scale_shape_manual(values = shapes_data)

#Economic
plot_sdl_Economic_variability_scatter <- ggplot(data = filter(sdl_Economic_spells, 
                                                              Data == "Stochastic" & 
                                                                names_CSIRO_climate_scenario == "Historical climate" & 
                                                                licvolfactor == 1.0 & 
                                                                Mark == "Mk4a")) + 
  geom_jitter(aes(y = economic_benefit, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin(aes(y = economic_benefit, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_Economic_spells, 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             Mark == "Mk4a" & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = economic_benefit, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_hydro)+
  scale_shape_manual(values = shapes_data)

#target hydro and Economic
sdl_target_baseline$measure <- sdl_target_baseline$target
sdl_target_baseline$measure_achieved <- sdl_target_baseline$ewr_achieved
sdl_target_baseline$relative_measure_achieved <- sdl_target_baseline$relative_ewr_achieved
sdl_target_baseline$Theme <- "Target"

sdl_hydrology_baseline$Theme <- "Water allocation"
sdl_hydrology_baseline$replicate <- as.character(sdl_hydrology_baseline$replicate)

sdl_Economic_baseline$measure_achieved <- sdl_Economic_baseline$economic_benefit
sdl_Economic_baseline$relative_measure_achieved <- sdl_Economic_baseline$relative_economic_benefit
sdl_Economic_baseline$Theme <- "Economics"
sdl_Economic_baseline$replicate <- as.character(sdl_Economic_baseline$replicate)

sdl_baseline <- bind_rows(sdl_target_baseline, sdl_hydrology_baseline, sdl_Economic_baseline)

plot_sdl_variability_scatter <- ggplot(data = filter(sdl_baseline, 
                                                     Data == "Stochastic" & 
                                                       names_CSIRO_climate_scenario == "Historical climate" & 
                                                       licvolfactor == 1.0 & 
                                                       Mark == "Mk4a")) + 
  geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             Mark == "Mk4a" & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = measure_achieved, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data)+
  ggforce::facet_row(vars(Theme), scales = 'free', space = 'free')


plot_sdl_EWR_variability_scatter
plot_sdl_target_variability_scatter
plot_sdl_Hydrology_variability_scatter
plot_sdl_Economic_variability_scatter

plot_sdl_variability_scatter

ggsave(plot = plot_sdl_EWR_variability_scatter, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climate_variability",Sys.Date(),".tiff")), device = "tiff",  width = 8, height = 5)

ggsave(plot = plot_sdl_target_variability_scatter, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climate_variability",Sys.Date(),".tiff")), device = "tiff",  width = 8, height = 5)

ggsave(plot = plot_sdl_Hydrology_variability_scatter, filename = file.path(comp_results, paste0("scatterplot_sdl_WaterAllocation_climate_variability",Sys.Date(),".tiff")), device = "tiff",  width = 8, height = 5)

ggsave(plot = plot_sdl_Economic_variability_scatter, filename = file.path(comp_results, paste0("scatterplot_sdl_Economic_climate_variability",Sys.Date(),".tiff")), device = "tiff",  width = 8, height = 5)

ggsave(plot = plot_sdl_variability_scatter, filename = file.path(comp_results, paste0("scatterplot_sdlc_climate_variability",Sys.Date(),".tiff")), device = "tiff",  width = 8, height = 5)

```

## 4) Variability - RELATIVE - no climate change

```{r}
#EWR
Scatterplot_sdl_EWR_baseline <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() +
  geom_jitter(aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = ewr_code),  colour = "black", fill = NA) + 
  geom_point(data = filter(sdl_ewr_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate"), 
              aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data)

#target
Scatterplot_sdl_target_baseline <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() +
  geom_jitter(aes(y = relative_ewr_achieved, x = target, colour = target, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = target),  colour = "black", fill = NA) + 
  geom_point(data = filter(sdl_target_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate"), 
              aes(y = relative_ewr_achieved, x = target, colour = target, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data)

#hydrology
Scatterplot_sdl_hydrology_baseline <- sdl_hydrology_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() +
  geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_measure_achieved, x = measure),  colour = "black", fill = NA) + 
  geom_point(data = filter(sdl_hydrology_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate"), 
              aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data)

#Economic
Scatterplot_sdl_Economic_baseline <- sdl_Economic_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() +
  geom_jitter(aes(y = relative_economic_benefit, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_economic_benefit, x = measure),  colour = "black", fill = NA) + 
  geom_point(data = filter(sdl_Economic_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate"), 
              aes(y = relative_economic_benefit, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data)

#TARGET HYDRO ECONOMIC
Scatterplot_sdl_baseline <- ggplot(data = filter(sdl_baseline, 
                                                     Data == "Stochastic" & 
                                                       names_CSIRO_climate_scenario == "Historical climate" & 
                                                       licvolfactor == 1.0 & 
                                                       Mark == "Mk4a")) + 
  geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin(aes(y = relative_measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             Mark == "Mk4a" & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data)+
  facet_grid(~Theme, scales = 'free', space = 'free')
  #ggforce::facet_row(vars(Theme), scales = 'free', space = 'free')

Scatterplot_sdl_EWR_baseline
Scatterplot_sdl_target_baseline
Scatterplot_sdl_hydrology_baseline
Scatterplot_sdl_Economic_baseline
Scatterplot_sdl_baseline

```

## 5) Climate change - with climate change

```{r}
plot_sdl_EWR_climates_scatter <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  geom_jitter(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),
              height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic" & 
                             Mark == "Mk4a" & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)

#TARGET
plot_sdl_target_climates_scatter <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  geom_jitter(aes(y = ewr_achieved, x = target, colour = target, shape = Data),
              height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_target_baseline, 
                           Mark == "Mk4a" & 
                           Data == "Historic" & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = target, colour = target, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)

#Hydrology
plot_sdl_Hydrology_climates_scatter <- sdl_hydrology_baseline |>
  filter(Data == "Stochastic" & 
           licvolfactor == 1.0 & 
           Mark == "Mk4a")|> 
  ggplot()+
  geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_hydrology_baseline, 
                           Data == "Historic" & 
                             Mark == "Mk4a" & 
                             licvolfactor == 1.0 ), 
             aes(y = measure_achieved, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_hydro)+
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)

#Economic
plot_sdl_Economic_climates_scatter <- ggplot(data = filter(sdl_Economic_baseline, 
                                                              Data == "Stochastic" & 
                                                                licvolfactor == 1.0 & 
                                                                Mark == "Mk4a")) + 
  geom_jitter(aes(y = economic_benefit, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin(aes(y = economic_benefit, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_Economic_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             Mark == "Mk4a"), 
             aes(y = economic_benefit, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_hydro)+
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)

#target hydro and Economic
sdl_target_baseline$measure <- sdl_target_baseline$target
sdl_target_baseline$measure_achieved <- sdl_target_baseline$ewr_achieved
sdl_target_baseline$Theme <- "Target"
sdl_hydrology_spells$Theme <- "Water allocation"
sdl_hydrology_spells$replicate <- as.character(sdl_hydrology_spells$replicate)
sdl_Economic_spells$measure_achieved <- sdl_Economic_spells$economic_benefit
sdl_Economic_spells$Theme <- "Economics"
sdl_Economic_spells$replicate <- as.character(sdl_Economic_spells$replicate)

sdl_spells <- bind_rows(sdl_target_baseline, sdl_hydrology_spells, sdl_Economic_spells)

plot_sdl_climates_scatter <- ggplot(data = filter(sdl_spells, 
                                                     Data == "Stochastic" &
                                                       licvolfactor == 1.0 & 
                                                       Mark == "Mk4a")) + 
  geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_spells, 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             Mark == "Mk4a" ), 
             aes(y = measure_achieved, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data)+
  ggforce::facet_row(vars(Theme), scales = 'free', space = 'free')


plot_sdl_EWR_climates_scatter
plot_sdl_target_climates_scatter
plot_sdl_Hydrology_climates_scatter
plot_sdl_Economic_climates_scatter

plot_sdl_climates_scatter

ggsave(plot = plot_sdl_EWR_climates_scatter, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climate",Sys.Date(),".tiff")), device = "tiff",  width = 8, height = 5)

ggsave(plot = plot_sdl_target_climates_scatter, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climate",Sys.Date(),".tiff")), device = "tiff",  width = 8, height = 5)

ggsave(plot = plot_sdl_Hydrology_climates_scatter, filename = file.path(comp_results, paste0("scatterplot_sdl_WaterAllocation_climate",Sys.Date(),".tiff")), device = "tiff",  width = 8, height = 5)

ggsave(plot = plot_sdl_Economic_variability_scatter, filename = file.path(comp_results, paste0("scatterplot_sdl_Economic_climate",Sys.Date(),".tiff")), device = "tiff",  width = 8, height = 5)

ggsave(plot = plot_sdl_variability_scatter, filename = file.path(comp_results, paste0("scatterplot_sdl_climate",Sys.Date(),".tiff")), device = "tiff",  width = 8, height = 5)

```

## 5) Climate change - RELATIVE

```{r}
#EWR
Scatterplot_sdl_EWR_climates_baseline <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  geom_jitter(aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = ewr_code),  colour = "black", fill = NA) + 
  geom_point(data = filter(sdl_ewr_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0), 
              aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)

#target
Scatterplot_sdl_target_climates_baseline <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  geom_jitter(aes(y = relative_ewr_achieved, x = target, colour = target, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = target),  colour = "black", fill = NA) + 
  geom_point(data = filter(sdl_target_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0), 
              aes(y = relative_ewr_achieved, x = target, colour = target, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)

#hydrology
Scatterplot_sdl_hydrology_climates_baseline <- sdl_hydrology_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_measure_achieved, x = measure),  colour = "black", fill = NA) + 
  geom_point(data = filter(sdl_hydrology_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0), 
              aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)

#Economic
Scatterplot_sdl_Economic_climates_baseline <- sdl_Economic_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  geom_jitter(aes(y = relative_economic_benefit, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_economic_benefit, x = measure),  colour = "black", fill = NA) + 
  geom_point(data = filter(sdl_Economic_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0), 
              aes(y = relative_economic_benefit, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)

#TARGET HYDRO ECONOMIC
Scatterplot_sdl_climates_baseline <- ggplot(data = filter(sdl_baseline, 
                                                     Data == "Stochastic" &
                                                       licvolfactor == 1.0 & 
                                                       Mark == "Mk4a")) + 
  geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin(aes(y = relative_measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             Mark == "Mk4a"), 
             aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data),fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data)+
  facet_grid(~Theme, scales = 'free', space = 'free')
  #ggforce::facet_row(vars(Theme), scales = 'free', space = 'free')

Scatterplot_sdl_EWR_climates_baseline
Scatterplot_sdl_target_climates_baseline
Scatterplot_sdl_hydrology_climates_baseline
Scatterplot_sdl_Economic_climates_baseline
Scatterplot_sdl_climates_baseline






```


## 6) ewater adaptation (changing HEW)

```{r}

plot_sdl_EWR_variability_sh_adaptation <- ggplot() + 
  geom_violin(data = filter(sdl_ewr_baseline, Data == "Stochastic"), aes(y = ewr_achieved, x = ewr_code, group = ewr_code),
              colour = "grey") + 
  geom_point(data = filter(sdl_ewr_baseline, Data == "Historic"), 
              aes(y = ewr_achieved, x = ewr_code, group = ewr_code, alpha = licvolfactor, shape = Data, fill = names_CSIRO_climate_scenario), 
             size = 3) + 
  geom_point(data = filter(sdl_ewr_baseline, Data == "Historic"), 
              aes(y = ewr_achieved, x = ewr_code, group = ewr_code, shape = Data), 
             size = 3) + 
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_CSIRO_climate_scenario)+
  #scale_linetype_manual(values = linetype_data)+
  scale_shape_manual(values = shapes_data)+
  theme_werp_toolkit()+
  #theme(legend.box = "horizontal")+
  guides(fill=guide_legend(override.aes=list(shape=21)),
         colour=guide_legend(override.aes=list(shape=21)),
         alpha=guide_legend(override.aes=list(shape=21)))+
  facet_wrap(~names_CSIRO_climate_scenario, nrow = 1)

#TARGET
plot_sdl_target_variability_sh_adaptation <- ggplot() +  
  geom_violin(data = filter(sdl_target_baseline, Data == "Stochastic"), aes(y = ewr_achieved, x = env_group, group = env_group),
              colour = "grey") + 
  geom_point(data = filter(sdl_target_baseline, Data == "Historic"), 
              aes(y = ewr_achieved, x = env_group, group = env_group, alpha = licvolfactor, shape = Data, fill = names_CSIRO_climate_scenario),
             size = 3) + 
  geom_point(data = filter(sdl_target_baseline, Data == "Historic"), 
              aes(y = ewr_achieved, x = env_group, group = env_group, shape = Data),
             size = 3) +
  #geom_boxplot() +
  theme_werp_toolkit()+
  scale_colour_manual(values = pal_envgroup)+
  scale_fill_manual(values = pal_CSIRO_climate_scenario)+
  #scale_linetype_manual(values = linetype_data)+
  scale_shape_manual(values = shapes_data)+
  #theme(legend.box = "horizontal")+
  guides(fill=guide_legend(override.aes=list(shape=21)),
         colour=guide_legend(override.aes=list(shape=21)))+
  facet_wrap(~names_CSIRO_climate_scenario)

ggsave(plot = plot_sdl_EWR_variability_sh_adaptation, filename = file.path(comp_results, paste0("plot_sdl_EWR_variability_stoch_and_historic_climatechange_adaptation",Sys.Date(),".tiff")), device = "tiff", width = 10, height = 8)

ggsave(plot = plot_sdl_target_variability_sh_adaptation, filename = file.path(comp_results, paste0("plot_sdl_target_variability_stoch_and_historic_climatechange_adaptation",Sys.Date(),".tiff")), device = "tiff", width = 10, height = 8)


plot_sdl_EWR_relativechange_adaptation <- ggplot() + 
  geom_point(data = filter(sdl_ewr_baseline), 
              aes(y = rel_ewr_achieved, x = ewr_code, group = ewr_code, alpha = licvolfactor, shape = Data, fill = names_CSIRO_climate_scenario), 
             size = 3) + 
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_CSIRO_climate_scenario)+
  #scale_linetype_manual(values = linetype_data)+
  scale_shape_manual(values = shapes_data)+
  theme_werp_toolkit()+
  #theme(legend.box = "horizontal")+
  guides(fill=guide_legend(override.aes=list(shape=21)),
         colour=guide_legend(override.aes=list(shape=21)),
         alpha=guide_legend(override.aes=list(shape=21)))+
  facet_wrap(~names_CSIRO_climate_scenario, nrow = 1)

#TARGET
plot_sdl_target_relativechange_adaptation <- ggplot(data = filter(sdl_target_baseline), aes(y = rel_ewr_achieved, x = env_group,  alpha = licvolfactor, shape = Data, fill = names_CSIRO_climate_scenario)) +  
  geom_point(position=position_dodge(width=0.5), size = 3) + 
  #geom_boxplot() +
  theme_werp_toolkit()+
  #scale_colour_manual(values = pal_envgroup)+
  scale_fill_manual(values = pal_CSIRO_climate_scenario)+
  #scale_linetype_manual(values = linetype_data)+
  scale_shape_manual(values = shapes_data)+
  #theme(legend.box = "horizontal")+
  guides(fill=guide_legend(override.aes=list(shape=21)),
         alpha=guide_legend(override.aes=list(shape=21)))#+
  #facet_wrap(~names_CSIRO_climate_scenario)

ggsave(plot = plot_sdl_EWR_relativechange_adaptation, filename = file.path(comp_results, paste0("plot_sdl_EWR_relativechange_adaptation",Sys.Date(),".tiff")), device = "tiff", width = 10, height = 8)

ggsave(plot = plot_sdl_target_relativechange_adaptation, filename = file.path(comp_results, paste0("plot_sdl_target_relativechange_adaptation",Sys.Date(),".tiff")), device = "tiff", width = 6, height = 5)

plot_sdl_EWR_both_relativechange_adaptation <- plot_sdl_EWR_variability_sh_adaptation + 
plot_sdl_EWR_relativechange_adaptation + plot_layout(ncol = 1, guides = "collect", axis_titles ="collect")
  
plot_sdl_target_both_relativechange_adaptation <- plot_sdl_target_variability_sh_adaptation + plot_sdl_target_relativechange_adaptation + plot_layout(ncol = 2, guides = "collect")

ggsave(plot = plot_sdl_EWR_both_relativechange_adaptation, filename = file.path(comp_results, paste0("plot_sdl_4panels_adptation",Sys.Date(),".tiff")), device = "tiff", width = 10, height = 5)

ggsave(plot = plot_sdl_target_both_relativechange_adaptation, filename = file.path(comp_results, paste0("plot_target_4panels_adaptaion",Sys.Date(),".tiff")), device = "tiff", width = 10, height = 5)
```

## 6) eWater management (Mks)

```{r}

plot_sdl_EWR_variability_sh_management <- ggplot() + 
  geom_violin(data = filter(sdl_ewr_baseline, Data == "Stochastic" & Mark == "Mk4a"), aes(y = ewr_achieved, x = ewr_code, group = ewr_code, scale = "width"),
              colour = "grey") + 
  geom_point(data = filter(sdl_ewr_baseline, Data == "Historic"), 
              aes(y = ewr_achieved, x = ewr_code, group = ewr_code, alpha = Mark, shape = Data, fill = names_CSIRO_climate_scenario), 
             size = 3) + 
  geom_point(data = filter(sdl_ewr_baseline, Data == "Historic"), 
              aes(y = ewr_achieved, x = ewr_code, group = ewr_code, shape = Data), 
             size = 3) + 
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_CSIRO_climate_scenario)+
  #scale_linetype_manual(values = linetype_data)+
  scale_shape_manual(values = shapes_data)+
  theme_werp_toolkit()+
  #theme(legend.box = "horizontal")+
  guides(fill=guide_legend(override.aes=list(shape=21)),
         colour=guide_legend(override.aes=list(shape=21)),
         alpha=guide_legend(override.aes=list(shape=21)))+
  facet_wrap(~names_CSIRO_climate_scenario, nrow = 1)

#TARGET
plot_sdl_target_variability_sh_management <- ggplot() +  
  geom_violin(data = filter(sdl_target_baseline, Data == "Stochastic" & Mark == "Mk4a"), aes(y = ewr_achieved, x = env_group, group = env_group),
              colour = "grey") + 
  geom_point(data = filter(sdl_target_baseline, Data == "Historic"), 
              aes(y = ewr_achieved, x = env_group, group = env_group, alpha = Mark, shape = Data, fill = names_CSIRO_climate_scenario),
             size = 3) + 
  geom_point(data = filter(sdl_target_baseline, Data == "Historic"), 
              aes(y = ewr_achieved, x = env_group, group = env_group, shape = Data),
             size = 3) +
  #geom_boxplot() +
  theme_werp_toolkit()+
  scale_colour_manual(values = pal_envgroup)+
  scale_fill_manual(values = pal_CSIRO_climate_scenario)+
  #scale_linetype_manual(values = linetype_data)+
  scale_shape_manual(values = shapes_data)+
  #theme(legend.box = "horizontal")+
  guides(fill=guide_legend(override.aes=list(shape=21)),
         colour=guide_legend(override.aes=list(shape=21)))+
  facet_wrap(~names_CSIRO_climate_scenario, nrow = 1)

ggsave(plot = plot_sdl_EWR_variability_sh_management, filename = file.path(comp_results, paste0("plot_sdl_EWR_variability_stoch_and_historic_climatechange_management",Sys.Date(),".tiff")), device = "tiff", width = 10, height = 8)

ggsave(plot = plot_sdl_target_variability_sh_management, filename = file.path(comp_results, paste0("plot_sdl_target_variability_stoch_and_historic_climatechange_management",Sys.Date(),".tiff")), device = "tiff", width = 10, height = 8)


plot_sdl_EWR_relativechange_management <- ggplot() + 
  geom_point(data = filter(sdl_ewr_baseline), 
              aes(y = rel_ewr_achieved, x = ewr_code, group = ewr_code, alpha = licvolfactor, shape = Data, fill = names_CSIRO_climate_scenario), 
             size = 3) + 
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_CSIRO_climate_scenario)+
  #scale_linetype_manual(values = linetype_data)+
  scale_shape_manual(values = shapes_data)+
  theme_werp_toolkit()+
  #theme(legend.box = "horizontal")+
  guides(fill=guide_legend(override.aes=list(shape=21)),
         colour=guide_legend(override.aes=list(shape=21)),
         alpha=guide_legend(override.aes=list(shape=21)))+
  facet_wrap(~names_CSIRO_climate_scenario, nrow = 1)

#TARGET
plot_sdl_target_relativechange_management <- ggplot(data = filter(sdl_target_baseline), aes(y = rel_ewr_achieved, x = env_group,  alpha = licvolfactor, shape = Data, fill = names_CSIRO_climate_scenario)) +  
  geom_point(position=position_dodge(width=0.5), size = 3) + 
  #geom_boxplot() +
  theme_werp_toolkit()+
  #scale_colour_manual(values = pal_envgroup)+
  scale_fill_manual(values = pal_CSIRO_climate_scenario)+
  #scale_linetype_manual(values = linetype_data)+
  scale_shape_manual(values = shapes_data)+
  #theme(legend.box = "horizontal")+
  guides(fill=guide_legend(override.aes=list(shape=21)),
         alpha=guide_legend(override.aes=list(shape=21)))#+
  #facet_wrap(~names_CSIRO_climate_scenario)

ggsave(plot = plot_sdl_EWR_relativechange_management, filename = file.path(comp_results, paste0("plot_sdl_EWR_relativechange_management",Sys.Date(),".tiff")), device = "tiff", width = 10, height = 8)

ggsave(plot = plot_sdl_target_relativechange_management, filename = file.path(comp_results, paste0("plot_sdl_target_relativechange_management",Sys.Date(),".tiff")), device = "tiff", width = 6, height = 5)

plot_sdl_EWR_both_relativechange_management <- plot_sdl_EWR_variability_sh_management + 
plot_sdl_EWR_relativechange_management + plot_layout(ncol = 1, guides = "collect", axis_titles ="collect")
  
plot_sdl_target_both_relativechange_management <- plot_sdl_target_variability_sh_management + plot_sdl_target_relativechange_management + plot_layout(ncol = 2, guides = "collect")

ggsave(plot = plot_sdl_EWR_both_relativechange_management, filename = file.path(comp_results, paste0("plot_sdl_4panels_management",Sys.Date(),".tiff")), device = "tiff", width = 10, height = 5)

ggsave(plot = plot_sdl_target_both_relativechange_management, filename = file.path(comp_results, paste0("plot_target_4panels_management",Sys.Date(),".tiff")), device = "tiff", width = 10, height = 5)
```

## 7) radar plot

```{r}

```















