---
title: "Comparer"
format: docx
editor: visual
echo: FALSE
execute: 
  cache: FALSE
---

```{r setup}
#| include: false
#| warning: false
#| message: false

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file(),
                     cache.lazy = FALSE,
                     warning = FALSE, 
                     message = FALSE)

```

```{r}
#| label: Librarys
#| include: false
#| warning: false
#| message: false

devtools::load_all(path = file.path("~/Georgia/WERP_toolkit"))
#library(werptoolkitr)
library(dplyr)
library(sf)
library(ggplot2)
library(patchwork)
library(tidyr)
library(ggridges)
```

```{r}
#| label: Functions
#| include: false
#| warning: false
#| message: false
source('R/paths.R')
source('R/read_in_aggs.R')
source('R/agg_variables.R')

```

```{r}
#| label: Function stolen from my scatch site
#| include: false
ggsave_multi <- function(filename, plot = last_plot(), device, ...) {

  extnames <- lapply(device, \(x) paste0(filename, '.', x))
  lapply(extnames, \(x) ggsave(
    filename = x, plot = plot,
    ...
  ))
  # similar to the ggsave return
  return(invisible(unlist(extnames)))
}
```

## Data

```{r}
#| label: Data
#| include: false
#| warning: false
#| message: false
#EWR tool
#Only read in what is necessary

#Economic
# RUN 0_Shok_data_sorting.qmd if data gets updated (26/07/24)

# ##Timeseries:
# sdl_Economic_timeseries <- clean_factors(read.csv(file.path(Economic_results, "Economic_yearly.csv")))
# sdl_Economic_timeseries$measure <- "Agricultural benefit"

## Spells:
sdl_Economic_spells <- clean_factors(read.csv(file.path(Economic_results, "Economic_summary.csv")))|>
  dplyr::mutate(scenario = paste(licvolfactor, Evapotranspiration, Rainfall, Old_Mark, Data, replicate, sep = "_"),
                measure = "Agricultural benefit",
                Theme = "Economics",
                Mark = "Delivery strategy 1",
                replicate = as.character(replicate))|>
#Normalise:
  ungroup()|>
  #Scale 0 to 1
  # dplyr::mutate(measure_achieved = (economic_benefit-werptoolkitr::LimitingFactor(economic_benefit))/(werptoolkitr::CompensatingFactor(economic_benefit)-werptoolkitr::LimitingFactor(economic_benefit)))
  #Scale to 1
  dplyr::mutate(measure_achieved = economic_benefit / werptoolkitr::CompensatingFactor(economic_benefit))
#Relativise:
dimgroups <- c('measure', 'SWSDLName')
sdl_Economic_baseline <- werptoolkitr::baseline_compare(val_df = sdl_Economic_spells,
                            compare_col = 'scenario',
                            base_lev = "1_1_1_Mk4a_Historic_0",
                            group_cols = dimgroups,
                            comp_fun = relative,
                            values_col = 'measure_achieved',
                            failmissing = FALSE)

## Vulnerability
sdl_economic_vulnerability <- sdl_Economic_baseline |>
  dplyr::group_by(Data, Mk, Mark, licvol_factor, licvolfactor, Evapotranspiration, Rainfall, names_CSIRO_climate_scenario, names_CSIRO_climate_scenario2, Theme, measure)|>
  dplyr::summarise(
    variance_measure_achieved = werptoolkitr::Variance(measure_achieved),
    measure_achieved = werptoolkitr::ArithmeticMean(measure_achieved))

#Water allocation - hydro
# RUN 0_Ash_data_sorting_reliability_resilience.qmd if data gets updated (26/07/24)

#Dont need timeseries

## Spells:
sdl_hydro_spells <- clean_factors(read.csv(file.path(hydro_results, "hydrology_summary.csv")))|>
  dplyr::mutate(scenario = paste(licvolfactor, Evapotranspiration, Rainfall, Old_Mark, Data, replicate, sep = "_"))|>
  dplyr::mutate(reliability_resilience_achieved = measure_achieved, #keeping unnormalised data
                Theme = "Water allocation",
                replicate = as.character(replicate))|>
  #Normalise:
  dplyr::ungroup()|>
  dplyr::group_by(to_scale)|>
  #Scale 0 to 1
  # dplyr::mutate(measure_achieved = ifelse(to_scale != "FALSE", (reliability_resilience_achieved-werptoolkitr::LimitingFactor(reliability_resilience_achieved))/(werptoolkitr::CompensatingFactor(reliability_resilience_achieved)-werptoolkitr::LimitingFactor(reliability_resilience_achieved)), reliability_resilience_achieved))|>
  #Scale to 1
  dplyr::mutate(measure_achieved = reliability_resilience_achieved / werptoolkitr::CompensatingFactor(reliability_resilience_achieved))|>
  
  #Inverse resilience: #length of time that allocations aren't met (the resilience measure)
  dplyr::mutate(measure_achieved = ifelse(to_scale != "FALSE", 1-measure_achieved, measure_achieved))

# data = filter(sdl_hydro_spells, Data == "Historic" & licvolfactor == 1.0 & Mark == "Delivery strategy 1" & climate %in% c("r1_2_e1_0", "r0_8_e1_07"))

#Relativise:
dimgroups <- c('measure', 'SWSDLName')
sdl_hydro_baseline <- werptoolkitr::baseline_compare(val_df = sdl_hydro_spells,
                            compare_col = 'scenario',
                            base_lev = "1_1_1_Mk4a_Historic_0",
                            group_cols = dimgroups,
                            comp_fun = relative,
                            values_col = 'measure_achieved',
                            failmissing = FALSE)

## Vulnerability
sdl_hydro_vulnerability <- sdl_hydro_baseline |>
  dplyr::group_by(Data, Mk, Mark, licvol_factor, licvolfactor, Evapotranspiration, Rainfall, names_CSIRO_climate_scenario, names_CSIRO_climate_scenario2, Theme, measure)|>
  dplyr::summarise(
    variance_measure_achieved = werptoolkitr::Variance(measure_achieved),
    measure_achieved = werptoolkitr::ArithmeticMean(measure_achieved))

rm(sdl_Economic_spells)
#rm(sdl_hydro_spells)

#TWO
sdl_two_baseline <- bind_rows(sdl_hydro_baseline, sdl_Economic_baseline)
sdl_two_vulnerability <- bind_rows(sdl_hydro_vulnerability, sdl_economic_vulnerability)

```

## Palettes

will need to change some palettes

shapes: triangles = stochastic; circles = historic data

violins: always stochastic data

Shading (alpha): used for climate, licvolfactor, and marks - lighter = less water (i think climate is currently the wrong way around)

Colour: is always the response variable (e.g. and individual EWR or target or economic benefit).

```{r}
#| label: palettes
#| include: false
#| warning: false
#| message: false



sdl_ewr_baseline <- read_in_aggs(project_dir = project_dir,
                          data_type = 'historical',
                          info_list = aggregation_info,
                          aggname = 'sdl_ewr_baseline',
                            mark = 'all',
                            licvol = 'all',
                            climate = 'all',
                          max_handling = "remove")

scenarios <- sdl_ewr_baseline |>
  distinct(Rainfall, Evapotranspiration, licvolfactor, Mark)
rm(sdl_ewr_baseline)

# Qualitative
# pal_SDL <- make_pal(unique(sdl_objective_nonrounding_agg$sdl_units$SWSDLName), 
#                     palette = "impressionist.colors::la_recolte_des_foins_eragny")

# pal_gauge <- make_pal(unique(gauges_to_plot),                       
#                       palette = 'ggsci::nrc_npg')

scale_evap_pal <- make_pal(as.character(unique(scenarios$Evapotranspiration)),
                      palette = 'nationalparkcolors::Redwoods')

scale_rain_pal <- make_pal(as.character(unique(scenarios$Rainfall)),
                      palette = 'nationalparkcolors::Redwoods')

# pal_scale_evap_historical_comp <- make_pal(as.character(unique(scenarios$names_scale_evap_historical_comp)),
#                       palette = 'nationalparkcolors::Redwoods')

# pal_scenario <- make_pal(rev(as.character(unique(scenarios$scenario))),
#                       palette = 'scico::roma')

pal_climate_scenario <- make_pal(
  rev(c("SR0.8_SE1.07", "SR0.8_SE1.00", "SR1.0_SE1.07",
         "SR1.0_SE1.00", "SR1.2_SE1.07", "SR1.2_SE1.00", NA)),
                      palette = 'scico::imola')

# pal_MDBA_climate_scenario <- make_pal(rev(as.character(unique(scenarios$names_MDBA_climate_scenario))),
#                       palette = 'scico::roma')

# these have to use quantitative even though they're not, or we run out of colors.
pal_env = list(EB = 'grDevices::Grays',
                EF = 'grDevices::Purp',
                NF = 'grDevices::Mint',
                NV = 'grDevices::Burg',
                OS = 'grDevices::Blues 2',
                WB = 'grDevices::Peach')

# use the first level of each of those to make a named pal. I wish there were an easier way
pal_envgroup <- purrr::imap_chr(pal_env,
                                \(x,y) make_pal(levels = y, palette = x)) |> 
  werptoolkitr:::as_colors()

pal_Target <-  stats::setNames(c("#029676FF", "#1B1B1BFF", "#005D67FF", "#73224EFF", "#023FA5FF", "#EA4C3BFF", 
                                 "#4873B8", "#B7A447", "#FDC010"), 
            c('Priority ecosystem functions', 'Native fish', 'Native vegetation', 'Flow-dependent frogs', 'Waterbirds', 
               "End of system flows", "Water allocation", "Agricultural benefits"))
class(pal_Target) <- 'colors'

pal_EWR <- stats::setNames(c("#FA5F16", '#7B3014FF', "#B83923", '#DB8062', 
                             '#C0AED9FF', '#8C37E5FF', '#AE56DEFF', "#7640A9FF", '#622E82FF', 
                             '#4092E1FF', '#4873B8', '#211DF0FF', '#6094BFFF', '#4677A5FF', '#00298CFF'), 
                                          c("CF", "VF", "BF1", "BF2", 
                                            "SF1", "SF2", "SF3", "LF1", "LF2", 
                                            "OB-WL", "OB-WM", "OB-WS1", "OB-WS2", "OB-WS3", "OB-WS4"))
class(pal_EWR) <- 'colors'

pal_hydro <- stats::setNames(c("#7F0038FF", '#C31E6EFF', "#FDC010", '#033800FF', "#7640A9FF"),
                             c("General security reliability", "General security resilience", "Delivery ability", "High security resilience", "Agricultural benefit"))
class(pal_hydro) <- 'colors'

pal_theme <- stats::setNames(c("#029676FF", "#1B1B1BFF", "#005D67FF", "#73224EFF", "#023FA5FF", "#EA4C3BFF", 
                                 "#7F0038FF", '#C31E6EFF', "#FDC010", '#033800FF', "#7640A9FF"),
                             c('Priority ecosystem functions', 'Native fish','Native vegetation', 'Flow-dependent frogs', 'Waterbirds', "End of system flows", 
                              "General security reliability", "General security resilience", "Delivery ability", "High security resilience", "Agricultural benefit"))
class(pal_theme) <- 'colors'


# Quantitative- sequential achievement
pal_achieve <- 'grDevices::Blue-Yellow'

# quantitative- diverging achievement (e.g. relative to baseline)
pal_compare <- 'scico::bam'

pal_scene <- make_pal(unique(scenarios$scenario),                       
                      palette = "viridis::mako", #'ggsci::nrc_npg', 
                      refvals = 'base', refcols = 'black')

# Data sets
shapes_data <- c(21,24)
names(shapes_data) <- c("Historic", "Stochastic")

shapes_data2 <- c(24,21)
names(shapes_data2) <- c("Stochastic", "Historic")

linetype_data <- c("dotted", "solid")
names(linetype_data) <- c("Historic", "Stochastic")

linetype_data2 <- c("solid", "dotted")
names(linetype_data2) <- c("Stochastic", "Historic")

# SHOW FISH
size_target <- c(3,4,3,3,3)
names(size_target)  <- c('Priority ecosystem functions', 'Native fish', 'Native vegetation', 'Flow-dependent frogs', 'Waterbirds')

shapes_theme <-  c(21, 22, 23, 24, 25,
                        21, 
                        21, 22, 23, 24, 25)

names(shapes_theme) <- c('Priority ecosystem functions', 'Native fish','Native vegetation', 'Flow-dependent frogs', 'Waterbirds', "End of system flows", "General security reliability", "General security resilience", "Delivery ability", "High security resilience", "Agricultural benefit")


#PALETTE OPTIONS:
pal_licvolfactor <- stats::setNames(
  c('#03071e', '#370617', '#6a040f',  '#9d0208', '#d00000', '#dc2f02',"#e85d04"),
  c(0.5, 0.7, 0.9, 1.0, 1.1, 1.3, 1.5))
class(pal_licvolfactor) <- 'colors'

pal_licvolfactor <- stats::setNames(
  c('#000000', '#2A2A2A', '#555555',  '#808080', '#AAAAAA', '#D5D5D5',"#FFFFFF"),
  c(0.5, 0.7, 0.9, 1.0, 1.1, 1.3, 1.5))
class(pal_licvolfactor) <- 'colors'

pal_CSIRO_climate_scenario <- stats::setNames(
  c("#000000","#333333","#808080","#AAAAAA","#D5D5D5","#FFFFFF"),
  c("Just Wet", "Hot and Wet", "Historical climate",  "Just Hot", "Just Dry", "Hot and Dry"))
class(pal_CSIRO_climate_scenario) <- 'colors'

pal_mark <- stats::setNames(
  c("#000000","#808080","#CCCCCC","#FFFFFF"),
  c("Mk4", "Mk4a", "Mk5a", "Mk5"))
class(pal_mark) <- 'colors'

pal_licvolfactor <- stats::setNames(
  c('#B2182BFF', '#D6604DFF', '#F4A582FF',  '#FFFFFF', '#92C5DEFF', "#172869FF", "#0C2340FF"),
  c("0.5 times current", '0.7 times current', '0.9 times current', '1 times current', '1.1 times current', '1.3 times current', '1.5 times current'))
class(pal_licvolfactor) <- 'colors'

pal_licvolfactor2 <- stats::setNames(
  c('#B2182BFF', '#D6604DFF', '#F4A582FF',  'black', '#92C5DEFF', "#172869FF", "#0C2340FF"),
  c("0.5 times current", '0.7 times current', '0.9 times current', '1 times current', '1.1 times current', '1.3 times current', '1.5 times current'))
class(pal_licvolfactor2) <- 'colors'

# pal_mark <- stats::setNames(
#   c("#B2182BFF","#FFFFFF","#92C5DEFF","#172869FF", "#FCAADEFF","#EF5FAFFF","#C31E6EFF"),
#   c("Mk4", "Mk4a", "Mk5a", "Mk5", 'Mk4a_0.3', 'Mk4a_0.5', 'Mk4a_0.7'))
# class(pal_mark) <- 'colors'

pal_mark <- stats::setNames(
  c("#FFFFFF","#92C5DEFF", '#2166ACFF', "#172869FF", "#FCAADEFF","#EF5FAFFF","#C31E6EFF"),
  c("Delivery strategy 1", "Delivery strategy 2", "Delivery strategy 3", "Delivery strategy 4", 'Delivery strategy 5', 'Delivery strategy 6', 'Delivery strategy 7'))
class(pal_mark) <- 'colors'

pal_mark2 <- stats::setNames(
  c("black","#92C5DEFF", '#2166ACFF', "#172869FF", "#FCAADEFF","#EF5FAFFF","#C31E6EFF"),
  c("Delivery strategy 1", "Delivery strategy 2", "Delivery strategy 3", "Delivery strategy 4", 'Delivery strategy 5', 'Delivery strategy 6', 'Delivery strategy 7'))
class(pal_mark2) <- 'colors'

pal_CSIRO_climate_scenario <- stats::setNames(
  c('#2166ACFF', '#92C5DEFF', '#F7F7F7FF',  '#F4A582FF', '#D6604DFF', '#B2182BFF', '#1A1A1AFF'),
  c("Just Wet", "Hot and Wet", "Historical climate",  "Just Hot", "Just Dry", "Hot and Dry", NA))
class(pal_CSIRO_climate_scenario) <- 'colors'

pal_theme2 <- stats::setNames(c("#AAAAAA", '#AAAAAA', "#AAAAAA", '#AAAAAA', '#AAAAAA', '#AAAAAA',
                                            '#AAAAAA', '#AAAAAA', '#AAAAAA', '#AAAAAA', '#AAAAAA', '#AAAAAA',
                                            '#AAAAAA', '#AAAAAA', '#AAAAAA',
                               "#AAAAAA", "#AAAAAA", "#AAAAAA", "#AAAAAA", "#AAAAAA", "#AAAAAA", 
                                 "#AAAAAA", "#AAAAAA", "#AAAAAA", "#AAAAAA", '#AAAAAA', "#AAAAAA", '#AAAAAA', "#AAAAAA"),
                             c("CF", "VF", "BF1", "BF2", "SF1", "SF2",
                                            "SF3", "LF1", "LF2", "OB-WL", "OB-WM", "OB-WS1",
                                            "OB-WS2", "OB-WS3", "OB-WS4",
                               'Priority ecosystem functions', 'Native fish',
                               'Native vegetation', 
                               'Flow-dependent frogs', 'Waterbirds', "End of system flows", 
                              "Something", "Water allocation", "Agricultural benefits", 
                              "General security reliability","General security resilience", "Delivery ability", "High security resilience", 
                              "Agricultural benefit"))
class(pal_theme2) <- 'colors'

pal_theme <- stats::setNames(c("#555555FF", '#7B3014FF', "#9E3D22FF", '#C35322FF', '#E77129FF', '#F59843FF',
                                            '#FCAD52FF', '#FFC07CFF', '#FFEDDAFF', '#D6E8F3FF', '#A3CCE5FF', '#7DAED1FF',
                                            '#6094BFFF', '#4677A5FF', '#2B5C8AFF',
                               "#029676FF", "#1B1B1BFF", "#005D67FF", "#73224EFF", "#023FA5FF", "#EA4C3BFF", 
                                 "#4873B8", "#B7A447", "#FDC010AA", "#7F0038FF", '#C31E6EFF', "#FDC010", '#033800FF', "#7640A9FF"),
                             c("CF", "VF", "BF1", "BF2", "SF1", "SF2",
                                            "SF3", "LF1", "LF2", "OB-WL", "OB-WM", "OB-WS1",
                                            "OB-WS2", "OB-WS3", "OB-WS4",
                               'Priority ecosystem functions', 'Native fish',
                               'Native vegetation', 
                               'Flow-dependent frogs', 'Waterbirds', "End of system flows", 
                              "Something", "Water allocation", "Agricultural benefits", "General security reliability", 
               "General security resilience", "Delivery ability", "High security resilience", "Agricultural benefit"))
class(pal_theme) <- 'colors'


SWSDLName_subset <-  "Macquarie-Castlereagh"

ewr_table <- get_ewr_table()
SWSDLName_info <- ewr_table |>
  filter(LTWPShortName == SWSDLName_subset)|>
  distinct(LTWPShortName, PlanningUnitID, PlanningUnitName, Gauge)

gauges_to_plot <- SWSDLName_info$Gauge
SWSDLName_subset <-  "Macquarie–Castlereagh" # fixing the dash
#maybe make palette based on end of sys flow???


```

## MAP

```{r}
#| label: MAP
#| echo: false
#| warning: false
#| message: false

gauges_df <- get_ewr_gauges()|>
  #st_drop_geometry() |>
  mutate(OWNER = case_when(owner == "NSW - NSW Department of Industry – Lands and Water" ~ "NSW",
                           owner == "VIC - Department of Environment, Land, Water and Planning"~ "VIC",
                           owner == "SA - Department of Environment, Water and Natural Resources"~ "SA",
                           owner == "QLD - Department of Natural Resources, Mines and Energy"~ "QLD",
                           owner == NA ~ NA))

Map_Macquarie <- ggplot(data = sdl_units,  aes(geometry = geometry)) +
  geom_sf(fill = "white")+
  geom_sf(data = filter(gauges_df, gauge %in% gauges_to_plot),  aes(geometry = geometry), colour = "#fcaa20")+
  geom_sf(data = filter(sdl_units, SWSDLName == SWSDLName_subset),  aes(geometry = geometry), fill = "#fcaa20", colour = "#fcaa20", alpha = 0.1)+ 
  geom_sf_text(data = filter(sdl_units, SWSDLName == SWSDLName_subset), label = "Macquarie", colour = "#fcaa20") +
  theme(legend.position = "none",
        axis.text = element_blank())+
  theme_werp_toolkit(legend.position = "none")

inset_map <- ggplot(ozmaps::ozmap_country) +
  geom_sf(fill = 'grey20') +              
  geom_sf(data = basin, fill = "white") +
  theme_werp_toolkit(axis.ticks = element_blank(), 
                         axis.text=element_blank())+
  coord_sf(xlim = c(110, 155), ylim = c(-45,-8), expand = FALSE) 
inset_map

# Why on earth does this print a dataframe of the corners?
overview_map <- Map_Macquarie +
  patchwork::inset_element(inset_map,  left = 0.0001, bottom = 0.7,
                                      right = 0.35, top = 0.99)

overview_map

# ggsave_multi(plot = Map_Macquarie, filename = file.path(comp_results, paste0("Map_Macquarie", Sys.Date(), ".tiff")), device = c('png', 'svg'),
#        width = 8, height = 5)

# example that will save as png and svg if we want.
ggsave_multi(plot = overview_map, filename = file.path(comp_results, paste0("Map_Macquarie", Sys.Date())), device = c("png", "svg"),
       width = 16, height = 12, units = 'cm')

```

#EWR TABLE
```{r}
ewr_table_421019 <- ewr_table |> 
  filter(Gauge %in% 421019)

#write.csv(ewr_table_421019, file.path(comp_results, paste0("ewr_table_421019_", Sys.Date(), ".csv")))

```


## 1) Vulnerability plot

quadrant lines = the means for stochastic sequences under all climates.

```{r}

sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = c('licvolfactor_1_0',"licvolfactor_1_0"),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

mean_EWR_Stoch_ach <- mean(filter(sdl_EWR_vulnerability, Data == "Stochastic", licvolfactor == 1.0 & Mark == "Delivery strategy 1")$ewr_achieved, na.rm = TRUE)
mean_EWR_Stoch_var <- mean(filter(sdl_EWR_vulnerability, Data == "Stochastic", licvolfactor == 1.0 & Mark == "Delivery strategy 1")$variance_ewr_achieved, na.rm = TRUE)
mean_target_Stoch_ach <-  mean(filter(sdl_target_vulnerability, Data == "Stochastic", licvolfactor == 1.0 & Mark == "Delivery strategy 1")$ewr_achieved, na.rm = TRUE)
mean_target_Stoch_var <- mean(filter(sdl_target_vulnerability, Data == "Stochastic", licvolfactor == 1.0 & Mark == "Delivery strategy 1")$variance_ewr_achieved, na.rm = TRUE)
mean_hydro_Stoch_ach <-  mean(filter(sdl_two_vulnerability, Theme == "Water allocation", Data == "Stochastic", licvolfactor == 1.0 & Mark == "Delivery strategy 1")$measure_achieved, na.rm = TRUE)
  mean_hydro_Stoch_var <- mean(filter(sdl_two_vulnerability, Theme == "Water allocation", Data == "Stochastic", licvolfactor == 1.0 & Mark == "Delivery strategy 1")$variance_measure_achieved, na.rm = TRUE)
  mean_economic_Stoch_ach <-  mean(filter(sdl_two_vulnerability, Theme == "Economics", Data == "Stochastic", licvolfactor == 1.0 & Mark == "Delivery strategy 1")$measure_achieved, na.rm = TRUE)
  mean_economic_Stoch_var <- mean(filter(sdl_two_vulnerability, Theme == "Economics", Data == "Stochastic", licvolfactor == 1.0 & Mark == "Delivery strategy 1")$variance_measure_achieved, na.rm = TRUE)


```

### 1A) Vulnerability - no climate change

(top left)

no fill

```{r}
#| label: 1A) Vulnerability 
#| echo: false
#| warning: false
#| message: false

#EWR
plot_sdl_EWR_vulnerability_S_noclimate <- ggplot(data = filter(sdl_EWR_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  annotate("rect", xmin = Inf, xmax = mean_EWR_Stoch_ach, ymin = Inf, ymax = mean_EWR_Stoch_var, fill= "#d7dafd")  + 
    annotate("rect", xmin = -Inf, xmax = mean_EWR_Stoch_ach, ymin = -Inf, ymax = mean_EWR_Stoch_var , fill= "#ffffff") +    
    annotate("rect", xmin = mean_EWR_Stoch_ach, xmax = Inf, ymin = mean_EWR_Stoch_var, ymax = -Inf, fill= "#ffe6fe") +    
    annotate("rect", xmin = mean_EWR_Stoch_ach, xmax = -Inf, ymin = Inf, ymax = mean_EWR_Stoch_var, fill= "#e7ffff") +
  geom_point(size = 3.5, fill = "white") +
  ggrepel::geom_text_repel(data = filter(sdl_EWR_vulnerability, names_CSIRO_climate_scenario %in% c("Historical climate")), aes(label = ewr_code), size = 3, segment.size =0.25) +
  theme_werp_toolkit()+
  theme(legend.position = "none")+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
    guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("",override.aes=list(shape = 24, size = 4), byrow = TRUE))+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.022)) +
  labs(x = "Outcome achievement", y = "Variance in achievement")+
  annotate(geom = "text", x = 0, y = 0.022, label = "ai) Historical scenario ", hjust = 0, size = 3)

#TARGET
plot_sdl_target_vulnerability_S_noclimate <- ggplot(data = filter(sdl_target_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) +
    annotate("rect", xmin = Inf, xmax = mean_target_Stoch_ach, ymin = Inf, ymax = mean_target_Stoch_var, fill= "#d7dafd")  + 
    annotate("rect", xmin = -Inf, xmax = mean_target_Stoch_ach, ymin = -Inf, ymax = mean_target_Stoch_var , fill= "#ffffff") +    
    annotate("rect", xmin = mean_target_Stoch_ach, xmax = Inf, ymin = mean_target_Stoch_var, ymax = -Inf, fill= "#ffe6fe") +    
    annotate("rect", xmin = mean_target_Stoch_ach, xmax = -Inf, ymin = Inf, ymax = mean_target_Stoch_var, fill= "#e7ffff") +
  geom_point(data = filter(sdl_target_vulnerability, target == "Native fish"), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data), size = 5, fill = "white") +
    geom_point(size = 3.5, fill = "white") +
    ggrepel::geom_text_repel(data = filter(distinct(sdl_target_vulnerability, target, .keep_all = TRUE), names_CSIRO_climate_scenario %in% c("Historical climate") & Data == "Stochastic"), aes(label = target), colour = "black", size = 3, , segment.size =0.25, position = ggpp::position_nudge_to(y = 0.00175, x = 0.85), min.segment.length = 0, arrow = arrow(length = unit(0.015, "npc")), direction = "y") +
  theme_werp_toolkit()+
  theme(legend.position = "none")+
  # geom_vline(size = 0.25, xintercept = mean_target_Stoch_ach) +
  #   geom_hline(size = 0.25, yintercept = mean_target_Stoch_var) +
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
    guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("",override.aes=list(shape = 24, size = 4), byrow = TRUE))+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.0035)) +
  labs(x = "Outcome achievement", y = "Variance in achievement")+
  annotate(geom = "text", x = 0, y = 0.0035, label = "ai) Historical scenario ", hjust = 0, size = 3)

#TWO:
plot_sdl_two_vulnerability_S_noclimate <- ggplot(data = filter(sdl_two_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Delivery strategy 1"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
    annotate("rect", xmin = Inf, xmax = mean_hydro_Stoch_ach, ymin = Inf, ymax = mean_hydro_Stoch_var, fill= "#d7dafd")  + 
    annotate("rect", xmin = -Inf, xmax = mean_hydro_Stoch_ach, ymin = -Inf, ymax = mean_hydro_Stoch_var , fill= "#ffffff") +    
    annotate("rect", xmin = mean_hydro_Stoch_ach, xmax = Inf, ymin = mean_hydro_Stoch_var, ymax = -Inf, fill= "#ffe6fe") +    
    annotate("rect", xmin = mean_hydro_Stoch_ach, xmax = -Inf, ymin = Inf, ymax = mean_hydro_Stoch_var, fill= "#e7ffff") +
  geom_point(size = 3.5, fill = "white") +
  ggrepel::geom_text_repel(data = filter(sdl_two_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Delivery strategy 1"), aes(label = measure, y = variance_measure_achieved, x = measure_achieved, colour = measure),linetype = "dotted", colour = "black", size = 3, , segment.size =0.25, position = ggpp::position_nudge_to(y = 0.02, x = 0.3), min.segment.length = 0, arrow = arrow(length = unit(0.015, "npc")), direction = "y") +
  theme_werp_toolkit()+
  #theme(legend.position = "none")+
  # geom_vline(size = 0.25, xintercept = mean_hydro_Stoch_ach) +
  # geom_hline(size = 0.25, yintercept = mean_hydro_Stoch_var) +
  # geom_vline(size = 0.25, xintercept = mean_economic_Stoch_ach, linetype = "dashed", colour = pal_theme[names(pal_theme)=="Agricultural benefit"]) +
  # geom_hline(size = 0.25, yintercept = mean_economic_Stoch_var, linetype = "dashed", colour = pal_theme[names(pal_theme)=="Agricultural benefit"]) +
  scale_colour_manual(values = pal_theme) +
  scale_shape_manual(values = shapes_data2)+
    guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("",override.aes=list(shape = 24, size = 4), byrow = TRUE))+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.055)) +
  labs(x = "Outcome achievement", y = "Variance in achievement")+
  annotate(geom = "text", x = 0, y = 0.055, label = "bi) Historical scenario ", hjust = 0, size = 3)


plot_sdl_EWR_vulnerability_S_noclimate
plot_sdl_target_vulnerability_S_noclimate
plot_sdl_two_vulnerability_S_noclimate
```

### 1B) Vulnerability - no climate change - with ewater adaptation (HEW licvol)

(top right)

fill: light = licvol factor 0.5; dark = licvol factor 1.5; linked in order by the lines

There are no economic data for licvol (other than historic/no change licvol)

```{r}
#| label: 1B) Vulnerability 
#| echo: false
#| warning: false
#| message: false

sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = "all",#c('licvolfactor_1_0', 'licvolfactor_1_5', 'licvolfactor_0_5'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = "all",#c('licvolfactor_1_0', 'licvolfactor_1_5', 'licvolfactor_0_5'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")
licvolfactor_ends <- c(0.5, 1.0, 1.5)

#EWR
plot_sdl_EWR_vulnerability_S_licvol <- ggplot(data = filter(sdl_EWR_vulnerability, licvolfactor %in% licvolfactor_ends), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
    annotate("rect", xmin = Inf, xmax = mean_EWR_Stoch_ach, ymin = Inf, ymax = mean_EWR_Stoch_var, fill= "#d7dafd")  + 
    annotate("rect", xmin = -Inf, xmax = mean_EWR_Stoch_ach, ymin = -Inf, ymax = mean_EWR_Stoch_var , fill= "#ffffff") +    
    annotate("rect", xmin = mean_EWR_Stoch_ach, xmax = Inf, ymin = mean_EWR_Stoch_var, ymax = -Inf, fill= "#ffe6fe") +    
    annotate("rect", xmin = mean_EWR_Stoch_ach, xmax = -Inf, ymin = Inf, ymax = mean_EWR_Stoch_var, fill= "#e7ffff") +
  geom_line(data = filter(sdl_EWR_vulnerability))+
  geom_point(aes(fill = licvol_factor), size = 3.5) +
  geom_point(size = 3.5) +
  ggrepel::geom_text_repel(data = filter(sdl_EWR_vulnerability, names_CSIRO_climate_scenario %in% c("Historical climate") & licvolfactor == 1.5), aes(label = ewr_code), size = 3, segment.size =0.25) +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  # geom_vline(size = 0.25, xintercept = mean_EWR_Stoch_ach) +
  #   geom_hline(size = 0.25, yintercept = mean_EWR_Stoch_var) +
  scale_fill_manual(values = pal_licvolfactor)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("aiii) Relative env. water volume scenarios",override.aes=list(shape = 24, size = 4), ncol = 1, title.position="top", title.hjust = 0.5, byrow = TRUE))+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.022)) +
  labs(x = "Outcome achievement", y = "Variance in achievement")+
  annotate(geom = "text", x = 0, y = 0.022, label = "aiii) Relative env. water volume scenarios", hjust = 0, size = 3)

#Target
plot_sdl_target_vulnerability_S_licvol <- ggplot(data = filter(sdl_target_vulnerability, licvolfactor %in% licvolfactor_ends), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) +
      annotate("rect", xmin = Inf, xmax = mean_target_Stoch_ach, ymin = Inf, ymax = mean_target_Stoch_var, fill= "#d7dafd")  + 
    annotate("rect", xmin = -Inf, xmax = mean_target_Stoch_ach, ymin = -Inf, ymax = mean_target_Stoch_var , fill= "#ffffff") +    
    annotate("rect", xmin = mean_target_Stoch_ach, xmax = Inf, ymin = mean_target_Stoch_var, ymax = -Inf, fill= "#ffe6fe") +    
    annotate("rect", xmin = mean_target_Stoch_ach, xmax = -Inf, ymin = Inf, ymax = mean_target_Stoch_var, fill= "#e7ffff") +
  geom_line()+
    geom_point(data = filter(sdl_target_vulnerability, target == "Native fish", licvolfactor %in% licvolfactor_ends), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data), size = 3.5) +
  geom_point(aes(fill = licvol_factor), size = 3.5) +
  geom_point(size = 3.5) +
    ggrepel::geom_text_repel(data = filter(sdl_target_vulnerability, names_CSIRO_climate_scenario %in% c("Historical climate")& licvolfactor == 1.5), aes(label = target), colour = "black", size = 3, segment.size =0.25, position = ggpp::position_nudge_to(y = 0.00175, x = 0.85), min.segment.length = 0, arrow = arrow(length = unit(0.015, "npc")), direction = "y") +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        legend.spacing.y = unit(1.0, 'cm'))+
  # geom_vline(size = 0.25, xintercept = mean_target_Stoch_ach) +
  #   geom_hline(size = 0.25, yintercept = mean_target_Stoch_var) +
  scale_fill_manual(values = pal_licvolfactor)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
  guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("aiii) Relative env. water volume scenarios",override.aes=list(shape = 24, size = 4), ncol = 1, title.position="top", title.hjust = 0.5, byrow = TRUE))+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.0035)) +
  labs(x = "Outcome achievement", y = "Variance in achievement")+
  annotate(geom = "text", x = 0, y = 0.0035, label = "aiii) Relative env. water volume scenarios", hjust = 0, size = 3)

# #TWO:
# plot_sdl_two_vulnerability_S_licvol <- ggplot(data = filter(sdl_two_vulnerability, licvolfactor %in% licvolfactor_ends & names_CSIRO_climate_scenario == "Historical climate" & Mark == "Delivery strategy 1"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) +
#   geom_line()+
#   geom_jitter(aes(fill = licvol_factor),size = 3.5) +
#   geom_point(size = 3.5) +
#   ggrepel::geom_text_repel(data = filter(sdl_two_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.5 & Mark == "Delivery strategy 1"), aes(label = measure, y = variance_measure_achieved, x = measure_achieved, colour = measure),linetype = "dotted", colour = "black", size = 3, segment.size =0.25, position = ggpp::position_nudge_to(y = 0.02, x = 0.6), min.segment.length = 0, arrow = arrow(length = unit(0.015, "npc")), direction = "y") +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal")+
#   geom_vline(size = 0.25, xintercept = mean_hydro_Stoch_ach) +
#   geom_hline(size = 0.25, yintercept = mean_hydro_Stoch_var) +
#   geom_vline(size = 0.25, xintercept = mean_economic_Stoch_ach, linetype = "dashed", colour = pal_theme[names(pal_theme)=="Agricultural benefit"]) +
#   geom_hline(size = 0.25, yintercept = mean_economic_Stoch_var, linetype = "dashed", colour = pal_theme[names(pal_theme)=="Agricultural benefit"])+
#   scale_fill_manual(values = pal_licvolfactor)+
#   scale_colour_manual(values = pal_theme)+
#   scale_shape_manual(values = shapes_data2) +
#     guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("",override.aes=list(shape = 24, size = 4), ncol = 1, title.position="top", title.hjust = 0.5))+
#   coord_cartesian(xlim = c(0,1),ylim = c(0, 0.055)) +
#   labs(x = "Outcome achievement", y = "Variance in achievement")+
#   annotate(geom = "text", x = 0, y = 0.055, label = "OMIT) Relative environmental water volume scenarios", hjust = 0, size = 3)

plot_sdl_EWR_vulnerability_S_licvol
plot_sdl_target_vulnerability_S_licvol



```

### 1C) Vulnerability - no climate change - with ewater management (marks)

(bottom left)

fill: light = Mk4; dark = Mk5; linked in order by the lines (Mk4, Mk4a, Mk5a, MK5)

Marks are irrelevant for Economic results

```{r}
#| label: 1C) Vulnerability 
#| echo: false
#| warning: false
#| message: false

sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR', 'MACQ_CC_EFR_mkiv', 'MACQ_CC_EFR_mkv', 'MACQ_CC_EFR_mkva'),
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR', 'MACQ_CC_EFR_mkiv', 'MACQ_CC_EFR_mkv', 'MACQ_CC_EFR_mkva'), 
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

#EWR
plot_sdl_EWR_vulnerability_S_mks <- ggplot(data = filter(sdl_EWR_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
    annotate("rect", xmin = Inf, xmax = mean_EWR_Stoch_ach, ymin = Inf, ymax = mean_EWR_Stoch_var, fill= "#d7dafd")  + 
    annotate("rect", xmin = -Inf, xmax = mean_EWR_Stoch_ach, ymin = -Inf, ymax = mean_EWR_Stoch_var , fill= "#ffffff") +    
    annotate("rect", xmin = mean_EWR_Stoch_ach, xmax = Inf, ymin = mean_EWR_Stoch_var, ymax = -Inf, fill= "#ffe6fe") +    
    annotate("rect", xmin = mean_EWR_Stoch_ach, xmax = -Inf, ymin = Inf, ymax = mean_EWR_Stoch_var, fill= "#e7ffff") +
  geom_line()+
  geom_point(aes(fill = Mark), size = 3.5) +
  geom_point(size = 3.5) +
  ggrepel::geom_text_repel(data = filter(sdl_EWR_vulnerability, names_CSIRO_climate_scenario %in% c("Historical climate") & Mark == "Delivery strategy 1"), aes(label = ewr_code), size = 3, segment.size =0.25) +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  # geom_vline(size = 0.25, xintercept = mean_EWR_Stoch_ach) +
  #   geom_hline(size = 0.25, yintercept = mean_EWR_Stoch_var) +
  scale_fill_manual(values = pal_mark)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("aiv) Delivery strategy scenarios",override.aes=list(shape = 24, size = 4), ncol = 1, title.position="top", title.hjust = 0.5, byrow = TRUE))+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.022)) +
  labs(x = "Outcome achievement", y = "Variance in achievement")+
  annotate(geom = "text", x = 0, y = 0.022, label = "aiv) Delivery strategy scenarios", hjust = 0, size = 3)

#TARGET
plot_sdl_target_vulnerability_S_mks <- ggplot(data = filter(sdl_target_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) +
      annotate("rect", xmin = Inf, xmax = mean_target_Stoch_ach, ymin = Inf, ymax = mean_target_Stoch_var, fill= "#d7dafd")  + 
    annotate("rect", xmin = -Inf, xmax = mean_target_Stoch_ach, ymin = -Inf, ymax = mean_target_Stoch_var , fill= "#ffffff") +    
    annotate("rect", xmin = mean_target_Stoch_ach, xmax = Inf, ymin = mean_target_Stoch_var, ymax = -Inf, fill= "#ffe6fe") +    
    annotate("rect", xmin = mean_target_Stoch_ach, xmax = -Inf, ymin = Inf, ymax = mean_target_Stoch_var, fill= "#e7ffff") +
  geom_line()+
    geom_point(data = filter(sdl_target_vulnerability, target == "Native fish"), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data), size = 5) +
  geom_point(aes(fill = Mark), size = 3.5) +
  geom_point(size = 3.5) +
    ggrepel::geom_text_repel(data = filter(sdl_target_vulnerability, names_CSIRO_climate_scenario %in% c("Historical climate") & Mark == "Delivery strategy 1"), aes(label = target), colour = "black", size = 3, segment.size =0.25, position = ggpp::position_nudge_to(y = 0.00175, x = 0.85), min.segment.length = 0, arrow = arrow(length = unit(0.015, "npc")), direction = "y") +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  # geom_vline(size = 0.25, xintercept = mean_target_Stoch_ach) +
  # geom_hline(size = 0.25, yintercept = mean_target_Stoch_var) +
  scale_fill_manual(values = pal_mark)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
  guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("aiv) Delivery strategy scenarios",override.aes=list(shape = 24, size = 4), ncol = 1, title.position="top", title.hjust = 0.5, byrow = TRUE))+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.0035)) +
  labs(x = "Outcome achievement", y = "Variance in achievement")+
  annotate(geom = "text", x = 0, y = 0.0035, label = "aiv) Delivery strategy scenarios", hjust = 0, size = 3)

# #TWO:
# plot_sdl_two_vulnerability_S_mks <- ggplot(data = filter(sdl_two_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) +
#   geom_line()+
#   geom_point(aes(fill = Mark), size = 3.5) +
#   geom_point(size = 3.5) +
#   ggrepel::geom_text_repel(data = filter(sdl_two_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Delivery strategy 1"), aes(label = measure, y = variance_measure_achieved, x = measure_achieved, colour = measure),linetype = "dotted", colour = "black", size = 3, segment.size =0.25, position = ggpp::position_nudge_to(y = 0.02, x = 0.6), min.segment.length = 0, arrow = arrow(length = unit(0.015, "npc")), direction = "y") +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal")+
#   geom_vline(size = 0.25, xintercept = mean_hydro_Stoch_ach) +
#   geom_hline(size = 0.25, yintercept = mean_hydro_Stoch_var) +
#   geom_vline(size = 0.25, xintercept = mean_economic_Stoch_ach, linetype = "dashed", colour = pal_theme[names(pal_theme)=="Agricultural benefit"]) +
#   geom_hline(size = 0.25, yintercept = mean_economic_Stoch_var, linetype = "dashed", colour = pal_theme[names(pal_theme)=="Agricultural benefit"]) +
#   scale_fill_manual(values = pal_mark)+
#   scale_colour_manual(values = pal_theme) +
#   scale_shape_manual(values = shapes_data2)+
#     guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("",override.aes=list(shape = 24, size = 4), ncol = 1, title.position="top", title.hjust = 0.5))+
#   coord_cartesian(xlim = c(0,1),ylim = c(0, 0.055)) +
#   labs(x = "Outcome achievement", y = "Variance in achievement")+
#   annotate(geom = "text", x = 0, y = 0.055, label = "OMIT) Delivery strategy scenarios", hjust = 0, size = 3)


plot_sdl_EWR_vulnerability_S_mks
plot_sdl_target_vulnerability_S_mks


```

### 1D) Vulnerability - With climate change (no adaptation or management)

(bottom right)

fill: light = "Just wet"; dark = "hot and dry"; linked in order by the lines ("Just Wet", "Hot and Wet","Historical climate","Just Hot","Just Dry","Hot and Dry")

NEED to reverse order of the factor, but only for these figs. not sure how right now.

```{r}
#| label: 1D) Vulnerability 
#| echo: false
#| warning: false
#| message: false

sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR_mkiv'), 
                                    licvol = c('licvolfactor_1_0'),
                                    climate = "all",#c('r0_8_e1_07', 'r1_0_e1_0', 'r1_2_e1_0'),
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR_mkiv'), 
                                    licvol = c('licvolfactor_1_0'),
                                    climate = "all",#c('r0_8_e1_07', 'r1_0_e1_0', 'r1_2_e1_0'),
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

#EWR
plot_sdl_EWR_vulnerability_S_climate <- ggplot(data = filter(sdl_EWR_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) +   
  annotate("rect", xmin = Inf, xmax = mean_EWR_Stoch_ach, ymin = Inf, ymax = mean_EWR_Stoch_var, fill= "#d7dafd")  + 
    annotate("rect", xmin = -Inf, xmax = mean_EWR_Stoch_ach, ymin = -Inf, ymax = mean_EWR_Stoch_var , fill= "#ffffff") +    
    annotate("rect", xmin = mean_EWR_Stoch_ach, xmax = Inf, ymin = mean_EWR_Stoch_var, ymax = -Inf, fill= "#ffe6fe") +    
    annotate("rect", xmin = mean_EWR_Stoch_ach, xmax = -Inf, ymin = Inf, ymax = mean_EWR_Stoch_var, fill= "#e7ffff") +
  # geom_vline(size = 0.25, xintercept = mean_EWR_Stoch_ach) +
  # geom_hline(size = 0.25, yintercept = mean_EWR_Stoch_var) +
  geom_line()+
  geom_point(aes(fill = names_CSIRO_climate_scenario2), size = 3.5) +
  geom_point(size = 3.5) +
  ggrepel::geom_text_repel(data = filter(sdl_EWR_vulnerability, names_CSIRO_climate_scenario %in% c("Just Wet")), aes(label = ewr_code), size = 3, segment.size =0.25) +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  scale_fill_manual(values = pal_CSIRO_climate_scenario)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
    guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("aii) Climate scenarios",override.aes=list(shape = 24, size = 4), ncol = 1, title.position="top", title.hjust = 0.5, byrow = TRUE))+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.022)) +
  labs(x = "Outcome achievement", y = "Variance in achievement")+
  annotate(geom = "text", x = 0, y = 0.022, label = "aii) Climate scenarios", hjust = 0, size = 3)

#TARGET
plot_sdl_target_vulnerability_S_climate <- ggplot(data = filter(sdl_target_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) +
      annotate("rect", xmin = Inf, xmax = mean_target_Stoch_ach, ymin = Inf, ymax = mean_target_Stoch_var, fill= "#d7dafd")  + 
    annotate("rect", xmin = -Inf, xmax = mean_target_Stoch_ach, ymin = -Inf, ymax = mean_target_Stoch_var , fill= "#ffffff") +    
    annotate("rect", xmin = mean_target_Stoch_ach, xmax = Inf, ymin = mean_target_Stoch_var, ymax = -Inf, fill= "#ffe6fe") +    
    annotate("rect", xmin = mean_target_Stoch_ach, xmax = -Inf, ymin = Inf, ymax = mean_target_Stoch_var, fill= "#e7ffff") +
  # geom_vline(size = 0.25, xintercept = mean_target_Stoch_ach) +
  # geom_hline(size = 0.25, yintercept = mean_target_Stoch_var) +
  geom_line(aes( colour = target))+
  geom_point(data = filter(sdl_target_vulnerability, target == "Native fish"), aes(y = variance_ewr_achieved, x = ewr_achieved, shape = Data), size = 5, fill = "white") +
  geom_point(data = filter(sdl_target_vulnerability), aes(fill = names_CSIRO_climate_scenario2), size = 3.5)+ 
  ggrepel::geom_text_repel(data = filter(sdl_target_vulnerability, names_CSIRO_climate_scenario %in% c("Just Wet")), aes(label = target), colour = "black", size = 3, segment.size =0.25, position = ggpp::position_nudge_to(y = 0.0029, x = 0.85), min.segment.length = 0, arrow = arrow(length = unit(0.015, "npc")), direction = "y") +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  scale_fill_manual(values = pal_CSIRO_climate_scenario)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
  scale_size_manual(values = size_target)+
  guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("aii & bii) Climate scenarios",override.aes=list(shape = 24, size = 4), ncol = 1, title.position="top", title.hjust = 0.5, byrow = TRUE))+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.0035)) +
  labs(x = "Outcome achievement", y = "Variance in achievement")+
  annotate(geom = "text", x = 0, y = 0.0035, label = "aii) Climate scenarios", hjust = 0, size = 3)

#TWO:
plot_sdl_two_vulnerability_S_climate <- ggplot(data = filter(sdl_two_vulnerability, licvolfactor == 1.0 & Mark == "Delivery strategy 1"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) +
      annotate("rect", xmin = Inf, xmax = mean_hydro_Stoch_ach, ymin = Inf, ymax = mean_hydro_Stoch_var, fill= "#d7dafd")  + 
    annotate("rect", xmin = -Inf, xmax = mean_hydro_Stoch_ach, ymin = -Inf, ymax = mean_hydro_Stoch_var , fill= "#ffffff") +    
    annotate("rect", xmin = mean_hydro_Stoch_ach, xmax = Inf, ymin = mean_hydro_Stoch_var, ymax = -Inf, fill= "#ffe6fe") +    
    annotate("rect", xmin = mean_hydro_Stoch_ach, xmax = -Inf, ymin = Inf, ymax = mean_hydro_Stoch_var, fill= "#e7ffff") +
  # geom_vline(size = 0.25, xintercept = mean_hydro_Stoch_ach) +
  # geom_hline(size = 0.25, yintercept = mean_hydro_Stoch_var) +
  # geom_vline(size = 0.25, xintercept = mean_economic_Stoch_ach, linetype = "dashed", colour = pal_theme[names(pal_theme)=="Agricultural benefit"]) +
  # geom_hline(size = 0.25, yintercept = mean_economic_Stoch_var, linetype = "dashed", colour = pal_theme[names(pal_theme)=="Agricultural benefit"]) +
  geom_line()+
  geom_point(aes(fill = names_CSIRO_climate_scenario2), size = 3.5) +
  geom_point(size = 3.5) +
  ggrepel::geom_text_repel(data = filter(sdl_two_vulnerability, names_CSIRO_climate_scenario == "Hot and Dry" & licvolfactor == 1.0 & Mark == "Delivery strategy 1"), aes(label = measure, y = variance_measure_achieved, x = measure_achieved, colour = measure),linetype = "dotted", colour = "black", size = 3, segment.size =0.25, position = ggpp::position_nudge_to(y = 0.02, x = 0.3), min.segment.length = 0, arrow = arrow(length = unit(0.015, "npc")), direction = "y") +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal", legend.position = 'bottom')+
  scale_fill_manual(values = pal_CSIRO_climate_scenario)+
  scale_colour_manual(values = pal_theme) +
  scale_shape_manual(values = shapes_data2)+
    guides(alpha = "none", shape = "none", colour = "none", fill = guide_legend("aii & bii) Climate scenarios",override.aes=list(shape = 24, size = 4), ncol = 1, title.position="top", title.hjust = 0.5, byrow = TRUE))+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.055)) +
  labs(x = "Outcome achievement", y = "Variance in achievement")+
  annotate(geom = "text", x = 0, y = 0.055, label = "bii) Climate scenarios", hjust = 0, size = 3)


plot_sdl_EWR_vulnerability_S_climate
plot_sdl_target_vulnerability_S_climate
plot_sdl_two_vulnerability_S_climate
```

## Figure 1 - Vulnerability - Stochastic data

```{r}
#| label: Figure 1 - Stochastic Vulnerability 
#| echo: false
#| warning: false
#| message: false

#EWR
VulnerabilityPlot_EWR_Stochastic <- plot_sdl_EWR_vulnerability_S_noclimate +
  plot_sdl_EWR_vulnerability_S_climate +
  plot_sdl_EWR_vulnerability_S_licvol + 
  plot_sdl_EWR_vulnerability_S_mks +
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & theme(legend.position = 'bottom') 

#TARGET + TWO
VulnerabilityPlot_target_Stochastic <- plot_sdl_target_vulnerability_S_noclimate +
  plot_sdl_target_vulnerability_S_climate +
  plot_sdl_target_vulnerability_S_licvol + 
  plot_sdl_target_vulnerability_S_mks +  
  plot_sdl_two_vulnerability_S_noclimate+
  plot_sdl_two_vulnerability_S_climate +
  plot_layout(ncol = 2, axes = "collect", guides = "collect") & theme(legend.position = 'bottom') &
  theme(legend.spacing.y = unit(0, 'cm'))

VulnerabilityPlot_EWR_Stochastic
VulnerabilityPlot_target_Stochastic


ggsave_multi(plot = VulnerabilityPlot_EWR_Stochastic, filename = file.path(comp_results, paste0("VulnerabilityPlot_EWR_Stochastic",Sys.Date())), device = c('png', 'pdf'), width = 8, height = 8)

ggsave_multi(plot = VulnerabilityPlot_target_Stochastic, filename = file.path(comp_results, paste0("VulnerabilityPlot_targetTWO_Stochastic",Sys.Date())), device = c('png', 'pdf'), width = 8, height = 12)


```

```{r}
#| label: Fig 1. Vulnerabiliy in EWRs - Stochastic
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Fig 1. Vulnerabiliy in EWRs - Stochastic

VulnerabilityPlot_EWR_Stochastic

```

```{r}
#| label: Fig 1. Vulnerabiliy in ecological targets - Stochastic
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Fig 1. Vulnerabiliy in ecological targets - Stochastic

VulnerabilityPlot_target_Stochastic

```

```{r}
#| label: Fig 1. Vulnerabiliy in economic benefits and water allocation relilience and reliabitity - Stochastic
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Fig 1. Vulnerabiliy in economic benefits and water allocation relilience and reliabitity - Stochastic

#VulnerabilityPlot_two_Stochastic

```

## Figs 4 - 7

Violins = stochastic variability

Circle points = historic data (with ewater adaptation and management for figs 6 and 7)

Normal and relative versions

have left triangle points on for only climate variability

## 4) Climate variability

historic CFs are now in the cloud of stochastic points; but small fresh 2 is at the very top.

```{r}
#| label: Figure 4 - Climate variability 
#| echo: false
#| warning: false
#| message: false


sdl_ewr_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_ewr_baseline',
                                    max_handling = "remove")

sdl_target_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_target_baseline',
                                    max_handling = "remove")

scatterplot_sdl_EWR_climate_variability <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Delivery strategy 1" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() + 
  geom_jitter(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),
              height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic" & 
                             Mark == "Delivery strategy 1" & 
                             licvolfactor == 1.0 & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = ewr_achieved, x = ewr_code, shape = Data), colour = "black", fill = "white", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))+
  labs(y = "Outcome achievement")

#TARGET
scatterplot_sdl_target_climate_variability <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Delivery strategy 1" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() + 
  geom_jitter(aes(y = ewr_achieved, x = target, colour = target, shape = Data),
              height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_target_baseline, 
                           Mark == "Delivery strategy 1" & 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = ewr_achieved, x = target, shape = Data), colour = "black", fill = "white", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_Target)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))+
  labs(y = "Outcome achievement")

scatterplot_sdl_two_climate_variability <- ggplot(data = filter(sdl_two_baseline, 
                                                     Data == "Stochastic" & 
                                                       names_CSIRO_climate_scenario == "Historical climate" & 
                                                       licvolfactor == 1.0 & 
                                                       Mark == "Delivery strategy 1")) + 
  geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_two_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             Mark == "Delivery strategy 1" & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = measure_achieved, x = measure, shape = Data), colour = "black", fill = "white", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))+
  labs(y = "Outcome achievement")

scatterplot_sdl_EWRtargetTWO_climate_variability <- scatterplot_sdl_EWR_climate_variability +
scatterplot_sdl_target_climate_variability +
scatterplot_sdl_two_climate_variability + plot_layout(nrow = 3, axes = "collect") 

ggsave_multi(plot = scatterplot_sdl_EWRtargetTWO_climate_variability, filename = file.path(comp_results, paste0("scatterplot_sdl_EWRtargetTWO_climate_variability",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

```

## 5) Climate change

```{r}
#| label: Figure 5 - Climate change 
#| echo: false
#| warning: false
#| message: false

scatterplot_sdl_EWR_climates <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Delivery strategy 1" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic" & 
                             Mark == "Delivery strategy 1" & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = ewr_code, shape = Data), colour = "black", fill = "white", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))+
  labs(y = "Outcome achievement")

#TARGET
scatterplot_sdl_target_climates <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Delivery strategy 1" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = target, colour = target, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_target_baseline, 
                           Mark == "Delivery strategy 1" & 
                           Data == "Historic" & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = target, shape = Data), colour = "black", fill = "white", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_Target)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))+
  labs(y = "Outcome achievement")

#Economic
scatterplot_sdl_two_climates <- ggplot(data = filter(sdl_two_baseline, 
                                                              Data == "Stochastic" & 
                                                                licvolfactor == 1.0 & 
                                                                Mark == "Delivery strategy 1")) + 
  #geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_two_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             Mark == "Delivery strategy 1"), 
             aes(y = measure_achieved, x = measure, shape = Data), colour = "black", fill = "white", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_hydro)+
  scale_fill_manual(values = pal_licvolfactor)+   scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))+
  labs(y = "Outcome achievement")

scatterplot_sdl_EWR_climates
scatterplot_sdl_targetTWO_climates <- scatterplot_sdl_target_climates + 
scatterplot_sdl_two_climates + plot_layout(nrow = 2, axes = "collect")

ggsave_multi(plot = scatterplot_sdl_EWR_climates, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climate",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 4)

ggsave_multi(plot = scatterplot_sdl_targetTWO_climates, filename = file.path(comp_results, paste0("scatterplot_sdl_targetTWO_climate",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 10)

```

## 6) ewater adaptation (licvol)

```{r}
#| label: Figure 6 - ewater adaptation 
#| echo: false
#| warning: false
#| message: false

scatterplot_sdl_EWR_climates_licvol <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Delivery strategy 1" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic" & 
                             Mark == "Delivery strategy 1" & 
                             licvolfactor %in% licvolfactor_ends), 
             aes(y = ewr_achieved, x = ewr_code, shape = Data, fill = licvol_factor), colour = "black", size = 3, position = position_dodge(width = 0.75)) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_licvolfactor)+
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  theme(legend.box = "horizontal")+
  guides(shape = "none", colour = "none", fill = guide_legend("Relative env. water volume", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

#TARGET
scatterplot_sdl_target_climates_licvol <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Delivery strategy 1" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = target, colour = target, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_target_baseline, 
                           Mark == "Delivery strategy 1" & 
                           Data == "Historic" & 
                             licvolfactor %in% licvolfactor_ends), 
             aes(y = ewr_achieved, x = target, shape = Data, fill = licvol_factor), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend("Relative env. water volume", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

#two
scatterplot_sdl_two_climates_licvol <- ggplot(data = filter(sdl_two_baseline, 
                                                              Data == "Stochastic" & 
                                                                licvolfactor == 1.0 & 
                                                                Mark == "Delivery strategy 1")) + 
  #geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_two_baseline, 
                           Data == "Historic" & 
                             Mark == "Delivery strategy 1" & 
                             licvolfactor %in% licvolfactor_ends), 
             aes(y = measure_achieved, x = measure, shape = Data, fill = licvol_factor), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend("Relative env. water volume", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

scatterplot_sdl_EWR_climates_licvol

scatterplot_sdl_targetTWO_climates_licvol <- 
scatterplot_sdl_target_climates_licvol +
scatterplot_sdl_two_climates_licvol + plot_layout(nrow = 2, axes = "collect", guides = "collect") 


ggsave_multi(plot = scatterplot_sdl_EWR_climates_licvol, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climates_licvol",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 4)

ggsave_multi(plot = scatterplot_sdl_targetTWO_climates_licvol, filename = file.path(comp_results, paste0("scatterplot_sdl_targetTWO_climates_licvol",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 10)


```

## 7) eWater management (Mks)

```{r}
#| label: Figure 7 - eWater management
#| echo: false
#| warning: false
#| message: false

sdl_ewr_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR', 'MACQ_CC_EFR_mkiv', 'MACQ_CC_EFR_mkv', 'MACQ_CC_EFR_mkva'),
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'all',
                                    aggname = 'sdl_ewr_baseline',
                                    max_handling = "remove")

sdl_target_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR', 'MACQ_CC_EFR_mkiv', 'MACQ_CC_EFR_mkv', 'MACQ_CC_EFR_mkva'),
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'all',
                                    aggname = 'sdl_target_baseline',
                                    max_handling = "remove")

scatterplot_sdl_EWR_climates_mks <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Delivery strategy 1" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic"  & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = ewr_code, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  theme(legend.box = "horizontal")+
  guides(shape = "none", colour = "none", fill = guide_legend("Delivery strategy", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

#TARGET
scatterplot_sdl_target_climates_mks <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Delivery strategy 1" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_target_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = target, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_mark)+      
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend("Delivery strategy", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

#hydro
scatterplot_sdl_hydro_climates_mks <- sdl_two_baseline |>
  filter(Data == "Stochastic" & 
           licvolfactor == 1.0 & 
           Mark == "Delivery strategy 1",
         Theme == "Water allocation")|> 
  ggplot()+
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_hydro_baseline, 
                           Data == "Historic" &  
                             licvolfactor == 1.0 ), 
             aes(y = measure_achieved, x = measure, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend("Delivery strategy", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

scatterplot_sdl_EWR_climates_mks
scatterplot_sdl_target_climates_mks
scatterplot_sdl_hydro_climates_mks


ggsave_multi(plot = scatterplot_sdl_EWR_climates_mks, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 4)

ggsave_multi(plot = scatterplot_sdl_target_climates_mks, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_hydro_climates_mks, filename = file.path(comp_results, paste0("scatterplot_sdl_WaterAllocation_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)


```

## 8) Targeted EWR management

I very well may be duplicating work above, but will be easier to think through if I just build this I think. The targeted approach does do something; the green, blue, and red do not fall on teh purple points @fig-experiment and @fig-experiment-targets.

```{r}
#| label: targeted-data-in 
#| echo: false
#| warning: false
#| message: false

sdl_ewr_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR_mkiv',
                                             'MACQ_CC_EFR_mkva',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_3',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_5',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_7'),
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'all',
                                    aggname = 'sdl_ewr_baseline',
                                    max_handling = "remove")

sdl_target_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR_mkiv',
                                             'MACQ_CC_EFR_mkva',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_3',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_5',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_7'),
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'all',
                                    aggname = 'sdl_target_baseline',
                                    max_handling = "remove")


EWR_select <- c("VF", "BF2", "SF1", "SF2", "SF3", "LF2", "OB-WS4")

#EWR
scatterplot_sdl_EWR_climates_mks_exp <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Delivery strategy 1" & 
           licvolfactor == 1.0 &
           ewr_code %in% EWR_select)|>
  ggplot() + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic"  & 
                             licvolfactor == 1.0 &
           ewr_code %in% EWR_select), 
             aes(y = ewr_achieved, x = ewr_code, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  theme(legend.box = "horizontal")+
  guides(shape = "none", colour = "none", fill = guide_legend("Delivery strategy", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

#EWR ALLL
scatterplot_sdl_EWR_climates_mks_exp2 <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Delivery strategy 1" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic"  & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = ewr_code, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  theme(legend.box = "horizontal", legend.position = "bottom")+
  guides(shape = "none", colour = "none", fill = guide_legend("Delivery strategy", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

#TARGET
scatterplot_sdl_target_climates_mks_exp <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Delivery strategy 1" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_target_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = target, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_mark)+      
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend("Delivery strategy", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

scatterplot_sdl_EWR_climates_mks_exp
scatterplot_sdl_target_climates_mks_exp



ggsave_multi(plot = scatterplot_sdl_EWR_climates_mks_exp, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climates_mks_experiment",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 4)
scatterplot_sdl_EWR_climates_mks_exp2
ggsave_multi(plot = scatterplot_sdl_EWR_climates_mks_exp2, filename = file.path(comp_results, paste0("scatterplot_sdl_allEWR_climates_mks_experiment",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 7)

ggsave_multi(plot = scatterplot_sdl_target_climates_mks_exp, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climates_mks_experiment",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

```

## another look at things

I was expecting this plot, but didn't see it and I'm curious about it. I made 4; ewrs and targets with the effect of licvolfactor @fig-licvolewr-diffs-variance and @fig-licvoltarget-diffs-variance, and Mark @fig-markewr-diffs-variance and @fig-marktarget-diffs-variance.

```{r}
#| label: read-in-stoch-summaries
#| include: false
variance_climmark <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR',
                                             'MACQ_CC_EFR_mkiv',
                                             'MACQ_CC_EFR_mkv',
                                             'MACQ_CC_EFR_mkva'),
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'all',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

variance_licclim <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

variance_climmark_target <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR',
                                             'MACQ_CC_EFR_mkiv',
                                             'MACQ_CC_EFR_mkv',
                                             'MACQ_CC_EFR_mkva'),
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'all',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

variance_licclim_target <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

```

```{r}
#| label: fig-markewr-diffs-variance
#| fig-cap: How much does mark matter, with points as means and error bars as 1 sd over the stochastic runs. This is only for licvolfactor = 1.

mark_ewr_variance <- ggplot(filter(variance_climmark, Data == 'Stochastic'), 
       aes(x = ewr_code, y = ewr_achieved,
           fill = Mark,colour = Mark,
           ymin = ewr_achieved-sqrt(variance_ewr_achieved),
           ymax = ewr_achieved + sqrt(variance_ewr_achieved))) +
  geom_point(position = position_dodge(width = 1), shape = 21) +
  geom_linerange(position = position_dodge(width = 1)) +
  facet_wrap(~names_CSIRO_climate_scenario2) +
  scale_fill_manual(values = pal_mark)+    
  scale_colour_manual(values = pal_mark2)+   
  theme_werp_toolkit(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
    theme(legend.position = "bottom")+
  guides(shape = "none", colour = "none", fill = guide_legend("Delivery strategy", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

ggsave_multi(plot = mark_ewr_variance, 
             filename = file.path(comp_results, "mark_ewr_variance"),
             device = c("png", "svg"),
       width = 24, height = 24, units = 'cm')

mark_ewr_variance
```

```{r}
#| label: fig-licvolewr-diffs-variance
#| fig-cap: How much does licvolfactor matter, with points as means and error bars as 1 sd over the stochastic runs. This is only for Mark 4a.

licvol_ewr_variance <- ggplot(filter(variance_licclim, Data == 'Stochastic'), 
       aes(x = ewr_code, y = ewr_achieved,
           color = licvol_factor, fill = licvol_factor,
           ymin = ewr_achieved-sqrt(variance_ewr_achieved),
           ymax = ewr_achieved + sqrt(variance_ewr_achieved))) +
  geom_point(position = position_dodge(width = 1)) +
  geom_linerange(position = position_dodge(width = 1)) +
  facet_wrap(~names_CSIRO_climate_scenario2) +
  theme_werp_toolkit(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
  theme(legend.position = "bottom")+
    scale_fill_manual(values = pal_licvolfactor)+    
  scale_colour_manual(values = pal_licvolfactor2)+   
  guides(shape = "none", colour = "none", fill = guide_legend("Relative env. water volume", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

ggsave_multi(plot = licvol_ewr_variance, 
             filename = file.path(comp_results, "licvol_ewr_variance"),
             device = c("png", "svg"),
       width = 24, height = 24, units = 'cm')

licvol_ewr_variance
```

```{r}
#| label: fig-marktarget-diffs-variance
#| fig-cap: How much does mark matter, with points as means and error bars as 1 sd over the stochastic runs. This is only for licvolfactor = 1.
mark_target_variance <- ggplot(filter(variance_climmark_target, 
                                      Data == 'Stochastic'), 
       aes(x = names_CSIRO_climate_scenario2, y = ewr_achieved,
           color = Mark, fill = Mark,
           ymin = ewr_achieved-sqrt(variance_ewr_achieved),
           ymax = ewr_achieved + sqrt(variance_ewr_achieved))) +
  geom_point(position = position_dodge(width = 1)) +
  geom_linerange(position = position_dodge(width = 1)) +
  facet_wrap(~target) +
  theme_werp_toolkit(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
    theme(legend.position = "bottom")+
    scale_fill_manual(values = pal_mark)+    
  scale_colour_manual(values = pal_mark2)+ 
  guides(shape = "none", colour = "none", fill = guide_legend("Delivery strategy", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

ggsave_multi(plot = mark_target_variance, 
             filename = file.path(comp_results, "mark_target_variance"),
             device = c("png", "svg"),
       width = 24, height = 24, units = 'cm')

mark_target_variance
```

```{r}
#| label: fig-licvoltarget-diffs-variance
#| fig-cap: How much does licvolfactor matter, with points as means and error bars as 1 sd over the stochastic runs. This is only for Mark 4a.
licvol_target_variance <- ggplot(filter(variance_licclim_target, Data == 'Stochastic'), 
       aes(x = names_CSIRO_climate_scenario2, y = ewr_achieved,
           color = licvol_factor, fill = licvol_factor,
           ymin = ewr_achieved-sqrt(variance_ewr_achieved),
           ymax = ewr_achieved + sqrt(variance_ewr_achieved))) +
  geom_point(position = position_dodge(width = 1)) +
  geom_linerange(position = position_dodge(width = 1)) +
  facet_wrap(~target) +
  theme_werp_toolkit(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), axis.title.x = element_blank())+
    theme(legend.position = "bottom")+
      scale_fill_manual(values = pal_licvolfactor)+    
  scale_colour_manual(values = pal_licvolfactor2)+  
  guides(shape = "none", colour = "none", fill = guide_legend("Relative env. water volume", override.aes=list(shape = 21), ncol = 1, title.position="top", title.hjust = 0.5))+
  labs(y = "Outcome achievement")

ggsave_multi(plot = licvol_target_variance, 
             filename = file.path(comp_results, "licvol_target_variance"),
             device = c("png", "svg"),
       width = 24, height = 24, units = 'cm')

licvol_target_variance
```

## OTHER

```{r}

# The majority of agricultural benefits are associated with high-value crops irrigated using high-security water licences, which are always delivered when dam levels exceed the level of the off-take. These benefits should remain viable, with high-security water being deliverable x%    of the time even under extreme climate change.

days_burrendong_lt_dead_storage <- read.csv(file.path(hydro_results, "days_burrendong_lt_dead_storage_merged.csv"))|>
  dplyr::mutate(measure = "days_burrendong_lt_dead_storage")
days_burrendong_lt_dead_storage <- clean_factors(days_burrendong_lt_dead_storage)

temp <- days_burrendong_lt_dead_storage |>
  filter(measure == "Delivery ability")|>
  filter(names_CSIRO_climate_scenario2 == "Hot and Dry")|>
  filter(Data == "Historic")|>
  mutate(n_0 = ifelse(Current.volume == 0, 0, 1),
         percent_days = (Current.volume/366)*100)|>
  reframe(mean_percent_days = 100-mean(percent_days))



```


