---
title: "Comparer"
format: docx
editor: visual
echo: FALSE
execute: 
  cache: FALSE
---

```{r setup}
#| include: false
#| warning: false
#| message: false

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file(),
                     cache.lazy = FALSE,
                     warning = FALSE, 
                     message = FALSE)

```

```{r}
#| label: Librarys
#| include: false
#| warning: false
#| message: false

library(werptoolkitr)
library(dplyr)
library(sf)
library(ggplot2)
library(patchwork)
library(tidyr)
library(ggridges)
```

```{r}
#| label: Functions
#| include: false
#| warning: false
#| message: false
source('R/paths.R')
source('R/read_in_aggs.R')
source('R/agg_variables.R')

```

```{r}
#| label: Function stolen from my scatch site
#| include: false
ggsave_multi <- function(filename, plot = last_plot(), device, ...) {

  extnames <- lapply(device, \(x) paste0(filename, '.', x))
  lapply(extnames, \(x) ggsave(
    filename = x, plot = plot,
    ...
  ))
  # similar to the ggsave return
  return(invisible(unlist(extnames)))
}
```

## Data

```{r}
#| label: Data
#| include: false
#| warning: false
#| message: false
#EWR tool
#Only read in what is necessary

#Economic
# RUN 0_Shok_data_sorting.qmd if data gets updated (26/07/24)

# ##Timeseries:
# sdl_Economic_timeseries <- clean_factors(read.csv(file.path(Economic_results, "Economic_yearly.csv")))
# sdl_Economic_timeseries$measure <- "economic_benefit"

## Spells:
sdl_Economic_spells <- clean_factors(read.csv(file.path(Economic_results, "Economic_summary.csv")))|>
  dplyr::mutate(scenario = paste(licvolfactor, Evapotranspiration, Rainfall, Mark, Data, replicate, sep = "_"),
                measure = "economic_benefit",
                Theme = "Economics",
                replicate = as.character(replicate))|>
#Normalise:
  ungroup()|>
  dplyr::mutate(measure_achieved = (economic_benefit-werptoolkitr::LimitingFactor(economic_benefit))/(werptoolkitr::CompensatingFactor(economic_benefit)-werptoolkitr::LimitingFactor(economic_benefit)))
#Relativise:
dimgroups <- c('measure', 'SWSDLName')
sdl_Economic_baseline <- werptoolkitr::baseline_compare(val_df = sdl_Economic_spells,
                            compare_col = 'scenario',
                            base_lev = "1_1_1_Mk4a_Historic_0",
                            group_cols = dimgroups,
                            comp_fun = relative,
                            values_col = 'measure_achieved',
                            failmissing = FALSE)

## Vulnerability
sdl_economic_vulnerability <- sdl_Economic_baseline |>
  dplyr::group_by(Data, Mk, Mark, licvolfactor, Evapotranspiration, Rainfall, names_CSIRO_climate_scenario, Theme, measure)|>
  dplyr::summarise(
    variance_measure_achieved = werptoolkitr::Variance(measure_achieved),
    measure_achieved = werptoolkitr::ArithmeticMean(measure_achieved))

#Water allocation - hydro
# RUN 0_Ash_data_sorting_reliability_resilience.qmd if data gets updated (26/07/24)

#Dont need timeseries

## Spells:
sdl_hydro_spells <- clean_factors(read.csv(file.path(hydro_results, "hydrology_summary.csv")))|>
  dplyr::mutate(scenario = paste(licvolfactor, Evapotranspiration, Rainfall, Mark, Data, replicate, sep = "_"))|>
  dplyr::mutate(reliability_resilience_achieved = measure_achieved, #keeping unnormalised data
                Theme = "Water allocation",
                replicate = as.character(replicate))|>
  #Normalise:
  dplyr::ungroup()|>
  dplyr::group_by(measure)|>
  dplyr::mutate(measure_achieved = (reliability_resilience_achieved-werptoolkitr::LimitingFactor(reliability_resilience_achieved))/(werptoolkitr::CompensatingFactor(reliability_resilience_achieved)-werptoolkitr::LimitingFactor(reliability_resilience_achieved)))|>
  #Inverse resilience:
  dplyr::mutate(measure_achieved = ifelse(measure %in% c("GS_resilience", "HS_resilience"), 1-measure_achieved, measure_achieved))

#Relativise:
dimgroups <- c('measure', 'SWSDLName')
sdl_hydro_baseline <- werptoolkitr::baseline_compare(val_df = sdl_hydro_spells,
                            compare_col = 'scenario',
                            base_lev = "1_1_1_Mk4a_Historic_0",
                            group_cols = dimgroups,
                            comp_fun = relative,
                            values_col = 'measure_achieved',
                            failmissing = FALSE)

## Vulnerability
sdl_hydro_vulnerability <- sdl_hydro_baseline |>
  dplyr::group_by(Data, Mk, Mark, licvolfactor, Evapotranspiration, Rainfall, names_CSIRO_climate_scenario, Theme, measure)|>
  dplyr::summarise(
    variance_measure_achieved = werptoolkitr::Variance(measure_achieved),
    measure_achieved = werptoolkitr::ArithmeticMean(measure_achieved))

rm(sdl_Economic_spells)
rm(sdl_hydro_spells)

#TWO
sdl_two_baseline <- bind_rows(sdl_hydro_baseline, sdl_Economic_baseline)
sdl_two_vulnerability <- bind_rows(sdl_hydro_vulnerability, sdl_economic_vulnerability)

```

## Palettes

will need to change some palettes

shapes: triangles = stochastic; circles = historic data

violins: always stochastic data

Shading (alpha): used for climate, licvolfactor, and marks - lighter = less water (i think climate is currently the wrong way around)

Colour: is always the response variable (e.g. and individual EWR or target or economic benefit).

```{r}
#| label: palettes
#| include: false
#| warning: false
#| message: false



sdl_ewr_baseline <- read_in_aggs(project_dir = project_dir,
                          data_type = 'historical',
                          info_list = aggregation_info,
                          aggname = 'sdl_ewr_baseline',
                            mark = 'all',
                            licvol = 'all',
                            climate = 'all',
                          max_handling = "remove")

scenarios <- sdl_ewr_baseline |>
  distinct(Rainfall, Evapotranspiration, licvolfactor, Mark)
rm(sdl_ewr_baseline)

# Qualitative
# pal_SDL <- make_pal(unique(sdl_objective_nonrounding_agg$sdl_units$SWSDLName), 
#                     palette = "impressionist.colors::la_recolte_des_foins_eragny")

# pal_gauge <- make_pal(unique(gauges_to_plot),                       
#                       palette = 'ggsci::nrc_npg')

scale_evap_pal <- make_pal(as.character(unique(scenarios$Evapotranspiration)),
                      palette = 'nationalparkcolors::Redwoods')

scale_rain_pal <- make_pal(as.character(unique(scenarios$Rainfall)),
                      palette = 'nationalparkcolors::Redwoods')

# pal_scale_evap_historical_comp <- make_pal(as.character(unique(scenarios$names_scale_evap_historical_comp)),
#                       palette = 'nationalparkcolors::Redwoods')

# pal_scenario <- make_pal(rev(as.character(unique(scenarios$scenario))),
#                       palette = 'scico::roma')

pal_climate_scenario <- make_pal(
  rev(c("SR0.8_SE1.07", "SR0.8_SE1.00", "SR1.0_SE1.07",
         "SR1.0_SE1.00", "SR1.2_SE1.07", "SR1.2_SE1.00", NA)),
                      palette = 'scico::imola')

# pal_MDBA_climate_scenario <- make_pal(rev(as.character(unique(scenarios$names_MDBA_climate_scenario))),
#                       palette = 'scico::roma')

# these have to use quantitative even though they're not, or we run out of colors.
pal_env = list(EB = 'grDevices::Grays',
                EF = 'grDevices::Purp',
                NF = 'grDevices::Mint',
                NV = 'grDevices::Burg',
                OS = 'grDevices::Blues 2',
                WB = 'grDevices::Peach')

# use the first level of each of those to make a named pal. I wish there were an easier way
pal_envgroup <- purrr::imap_chr(pal_env,
                                \(x,y) make_pal(levels = y, palette = x)) |> 
  werptoolkitr:::as_colors()

pal_Target <-  stats::setNames(c("#1B1B1BFF", "#A1D8B6FF", "#005D67FF", "#67223FFF", "#023FA5FF", "#EA4C3BFF", 
                                 "#4873B8", "#B7A447", "#FDC010"), 
            c('Priority ecosystem function', 'Native fish', 'Native vegetation', 'Other species', 'Waterbirds', 
               "End of system flows", "Water allocation", "Agricultural benefits"))
class(pal_Target) <- 'colors'

pal_EWR <- stats::setNames(c("#555555FF", '#7B3014FF', "#9E3D22FF", '#C35322FF', '#E77129FF', '#F59843FF',
                                            '#FCAD52FF', '#FFC07CFF', '#FFEDDAFF', '#D6E8F3FF', '#A3CCE5FF', '#7DAED1FF',
                                            '#6094BFFF', '#4677A5FF', '#2B5C8AFF'), 
                                          c("CF", "VF", "BF1", "BF2", "SF1", "SF2",
                                            "SF3", "LF1", "LF2", "OB-WL", "OB-WM", "OB-WS1",
                                            "OB-WS2", "OB-WS3", "OB-WS4"))
class(pal_EWR) <- 'colors'

pal_hydro <- stats::setNames(c("#7F0038FF", '#C31E6EFF', "#326812FF", '#033800FF', "#7640A9FF"),
                             c("GS_reliability", "GS_resilience", "HS_reliability", "HS_resilience", "economic_benefit"))
class(pal_hydro) <- 'colors'

pal_theme <- stats::setNames(c("#1B1B1BFF", "#A1D8B6FF", "#005D67FF", "#67223FFF", "#023FA5FF", "#EA4C3BFF", 
                                 "#4873B8", "#B7A447", "#FDC010", "#7F0038FF", '#C31E6EFF', "#326812FF", '#033800FF', "#7640A9FF"),
                             c('Priority ecosystem function', 'Native fish',
                               'Native vegetation', 
                               'Other species', 'Waterbirds', "End of system flows", 
                              "Something", "Water allocation", "Agricultural benefits", "GS_reliability", 
               "GS_resilience", "HS_reliability", "HS_resilience", "economic_benefit"))
class(pal_theme) <- 'colors'


# Quantitative- sequential achievement
pal_achieve <- 'grDevices::Blue-Yellow'

# quantitative- diverging achievement (e.g. relative to baseline)
pal_compare <- 'scico::bam'

pal_scene <- make_pal(unique(scenarios$scenario),                       
                      palette = "viridis::mako", #'ggsci::nrc_npg', 
                      refvals = 'base', refcols = 'black')

# Data sets
shapes_data <- c(21,24)
names(shapes_data) <- c("Historic", "Stochastic")

shapes_data2 <- c(24,21)
names(shapes_data2) <- c("Stochastic", "Historic")

linetype_data <- c("dotted", "solid")
names(linetype_data) <- c("Historic", "Stochastic")

linetype_data2 <- c("solid", "dotted")
names(linetype_data2) <- c("Stochastic", "Historic")

# SHOW FISH
size_target <- c(3,4,3,3,3)
names(size_target)  <- c('Priority ecosystem function', 'Native fish', 'Native vegetation', 'Other species', 'Waterbirds')

#PALETTE OPTIONS:
pal_licvolfactor <- stats::setNames(
  c('#03071e', '#370617', '#6a040f',  '#9d0208', '#d00000', '#dc2f02',"#e85d04"),
  c(0.5, 0.7, 0.9, 1.0, 1.1, 1.3, 1.5))
class(pal_licvolfactor) <- 'colors'

pal_licvolfactor <- stats::setNames(
  c('#000000', '#2A2A2A', '#555555',  '#808080', '#AAAAAA', '#D5D5D5',"#FFFFFF"),
  c(0.5, 0.7, 0.9, 1.0, 1.1, 1.3, 1.5))
class(pal_licvolfactor) <- 'colors'

pal_CSIRO_climate_scenario <- stats::setNames(
  c("#000000","#333333","#808080","#AAAAAA","#D5D5D5","#FFFFFF"),
  c("Just Wet", "Hot and Wet", "Historical climate",  "Just Hot", "Just Dry", "Hot and Dry"))
class(pal_CSIRO_climate_scenario) <- 'colors'

pal_mark <- stats::setNames(
  c("#000000","#808080","#CCCCCC","#FFFFFF"),
  c("Mk4", "Mk4a", "Mk5a", "Mk5"))
class(pal_mark) <- 'colors'

pal_licvolfactor <- stats::setNames(
  c('#B2182BFF', '#D6604DFF', '#F4A582FF',  '#FFFFFF', '#92C5DEFF', '#2166ACFF',"#172869FF"),
  c(0.5, 0.7, 0.9, 1.0, 1.1, 1.3, 1.5))
class(pal_licvolfactor) <- 'colors'

pal_mark <- stats::setNames(
  c("#B2182BFF","#FFFFFF","#92C5DEFF","#172869FF", "#FCAADEFF","#EF5FAFFF","#C31E6EFF"),
  c("Mk4", "Mk4a", "Mk5a", "Mk5", 'Mk4a_0.3', 'Mk4a_0.5', 'Mk4a_0.7'))
class(pal_mark) <- 'colors'

pal_CSIRO_climate_scenario <- stats::setNames(
  c('#2166ACFF', '#92C5DEFF', '#F7F7F7FF',  '#F4A582FF', '#D6604DFF', '#B2182BFF', '#1A1A1AFF'),
  c("Just Wet", "Hot and Wet", "Historical climate",  "Just Hot", "Just Dry", "Hot and Dry", NA))
class(pal_CSIRO_climate_scenario) <- 'colors'

pal_theme2 <- stats::setNames(c("#AAAAAA", '#AAAAAA', "#AAAAAA", '#AAAAAA', '#AAAAAA', '#AAAAAA',
                                            '#AAAAAA', '#AAAAAA', '#AAAAAA', '#AAAAAA', '#AAAAAA', '#AAAAAA',
                                            '#AAAAAA', '#AAAAAA', '#AAAAAA',
                               "#AAAAAA", "#AAAAAA", "#AAAAAA", "#AAAAAA", "#AAAAAA", "#AAAAAA", 
                                 "#AAAAAA", "#AAAAAA", "#AAAAAA", "#AAAAAA", '#AAAAAA', "#AAAAAA", '#AAAAAA', "#AAAAAA"),
                             c("CF", "VF", "BF1", "BF2", "SF1", "SF2",
                                            "SF3", "LF1", "LF2", "OB-WL", "OB-WM", "OB-WS1",
                                            "OB-WS2", "OB-WS3", "OB-WS4",
                               'Priority ecosystem function', 'Native fish',
                               'Native vegetation', 
                               'Other species', 'Waterbirds', "End of system flows", 
                              "Something", "Water allocation", "Agricultural benefits", 
                              "GS_reliability","GS_resilience", "HS_reliability", "HS_resilience", 
                              "economic_benefit"))
class(pal_theme2) <- 'colors'

pal_theme <- stats::setNames(c("#555555FF", '#7B3014FF', "#9E3D22FF", '#C35322FF', '#E77129FF', '#F59843FF',
                                            '#FCAD52FF', '#FFC07CFF', '#FFEDDAFF', '#D6E8F3FF', '#A3CCE5FF', '#7DAED1FF',
                                            '#6094BFFF', '#4677A5FF', '#2B5C8AFF',
                               "#1B1B1BFF", "#A1D8B6FF", "#005D67FF", "#67223FFF", "#023FA5FF", "#EA4C3BFF", 
                                 "#4873B8", "#B7A447", "#FDC010", "#7F0038FF", '#C31E6EFF', "#326812FF", '#033800FF', "#7640A9FF"),
                             c("CF", "VF", "BF1", "BF2", "SF1", "SF2",
                                            "SF3", "LF1", "LF2", "OB-WL", "OB-WM", "OB-WS1",
                                            "OB-WS2", "OB-WS3", "OB-WS4",
                               'Priority ecosystem function', 'Native fish',
                               'Native vegetation', 
                               'Other species', 'Waterbirds', "End of system flows", 
                              "Something", "Water allocation", "Agricultural benefits", "GS_reliability", 
               "GS_resilience", "HS_reliability", "HS_resilience", "economic_benefit"))
class(pal_theme) <- 'colors'


SWSDLName_subset <-  "Macquarie-Castlereagh"

ewr_table <- get_ewr_table()
SWSDLName_info <- ewr_table |>
  filter(LTWPShortName == SWSDLName_subset)|>
  distinct(LTWPShortName, PlanningUnitID, PlanningUnitName, Gauge)

gauges_to_plot <- SWSDLName_info$Gauge
SWSDLName_subset <-  "Macquarie–Castlereagh" # fixing the dash
#maybe make palette based on end of sys flow???


```

## MAP

```{r}
#| label: MAP
#| echo: false
#| warning: false
#| message: false

gauges_df <- get_ewr_gauges()|>
  #st_drop_geometry() |>
  mutate(OWNER = case_when(owner == "NSW - NSW Department of Industry – Lands and Water" ~ "NSW",
                           owner == "VIC - Department of Environment, Land, Water and Planning"~ "VIC",
                           owner == "SA - Department of Environment, Water and Natural Resources"~ "SA",
                           owner == "QLD - Department of Natural Resources, Mines and Energy"~ "QLD",
                           owner == NA ~ NA))

Map_Macquarie <- ggplot(data = sdl_units,  aes(geometry = geometry)) +
  geom_sf(fill = "white")+
  geom_sf(data = filter(gauges_df, gauge %in% gauges_to_plot),  aes(geometry = geometry), colour = "#fcaa20")+
  geom_sf(data = filter(sdl_units, SWSDLName == SWSDLName_subset),  aes(geometry = geometry), fill = "#fcaa20", colour = "#fcaa20", alpha = 0.1)+ 
  geom_sf_text(data = filter(sdl_units, SWSDLName == SWSDLName_subset), aes(label = SWSDLName), colour = "#fcaa20") +
  theme(legend.position = "none")+
  theme_werp_toolkit(legend.position = "none")

Map_Macquarie

# ggsave_multi(plot = Map_Macquarie, filename = file.path(comp_results, paste0("Map_Macquarie", Sys.Date(), ".tiff")), device = c('png', 'svg'),
#        width = 8, height = 5)

# example that will save as png and svg if we want.
ggsave_multi(plot = Map_Macquarie, filename = file.path(comp_results, paste0("Map_Macquarie", Sys.Date())), device = c("png", "svg"),
       width = 16, height = 12, units = 'cm')
```

## 1) Vulnerability plot

quadrant lines = the means for stochastic sequences under the historic climate.

### 1A) Vulnerability - no climate change

(top left)

no fill

```{r}
#| label: 1A) Vulnerability 
#| echo: false
#| warning: false
#| message: false

sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = c('licvolfactor_1_0',"licvolfactor_1_0"),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

#Combining target hydro and Economic
# sdl_target_vulnerability$measure <- sdl_target_vulnerability$target
# sdl_target_vulnerability$measure_achieved <- sdl_target_vulnerability$ewr_achieved
# sdl_target_vulnerability$variance_measure_achieved <- sdl_target_vulnerability$variance_ewr_achieved
# sdl_target_vulnerability$relative_measure_achieved <- sdl_target_vulnerability$relative_ewr_achieved
# sdl_target_vulnerability$Theme <- "Target"

# mean_EWR_Stoch_var <- mean(filter(sdl_EWR_vulnerability, Data == "Stochastic")$variance_ewr_achieved) #0.01 
# mean_EWR_Stoch_ach <- mean(filter(sdl_EWR_vulnerability, Data == "Stochastic")$ewr_achieved) #0.01 
# 
# mean_target_Stoch_var <- mean(filter(sdl_target_vulnerability, Data == "Stochastic")$variance_ewr_achieved)
# mean_target_Stoch_ach <- mean(filter(sdl_target_vulnerability, Data == "Stochastic")$ewr_achieved)
# 
# mean_hydro_Stoch_var <- mean(filter(sdl_hydro_vulnerability, Data == "Stochastic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a")$variance_measure_achieved)
# mean_hydro_Stoch_ach <- mean(filter(sdl_hydro_vulnerability, Data == "Stochastic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a")$measure_achieved)
# mean_economic_Stoch_var <- mean(filter(sdl_economic_vulnerability, Data == "Stochastic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a")$variance_measure_achieved)
# mean_economic_Stoch_ach <- mean(filter(sdl_economic_vulnerability, Data == "Stochastic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a")$measure_achieved)

mean_EWR_Stoch_var <- 0.01
mean_EWR_Stoch_ach <- 0.5
mean_target_Stoch_var <-  0.01
mean_target_Stoch_ach <- 0.5
mean_hydro_Stoch_var <-  0.01
  mean_hydro_Stoch_ach <- 0.5
  mean_economic_Stoch_var <-  0.01
  mean_economic_Stoch_ach <- 0.5
#EWR
plot_sdl_EWR_vulnerability_S_noclimate <- ggplot(data = filter(sdl_EWR_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none")+
  geom_vline(xintercept = mean_EWR_Stoch_ach) +
    geom_hline(yintercept = mean_EWR_Stoch_var) +
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_EWR_vulnerability_H_noclimate <- ggplot(data = filter(sdl_EWR_vulnerability, Data == "Historic"), 
                                                 #V1#aes(y = factor(variance_ewr_achieved), 
                                                 aes(y = factor(ewr_code),
                                                 x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_EWR_Stoch_ach) +
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))

#TARGET
plot_sdl_target_vulnerability_S_noclimate <- ggplot(data = filter(sdl_target_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none")+
  geom_vline(xintercept = mean_target_Stoch_ach) +
    geom_hline(yintercept = mean_target_Stoch_var) +
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_target_vulnerability_H_noclimate <- ggplot(data = filter(sdl_target_vulnerability, Data == "Historic"),
                                                    #V1#aes(y = factor(variance_ewr_achieved),
                                                    aes(y = target,
                                                    x = ewr_achieved, colour = target, shape = Data)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_target_Stoch_ach) +
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))

# 
# #hydro:
# plot_sdl_hydro_vulnerability_S_noclimate <- ggplot(data = filter(sdl_hydro_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.position = "none")+
#   geom_vline(xintercept = mean_hydro_Stoch_ach) +
#     geom_hline(yintercept = mean_hydro_Stoch_var) +
#   scale_colour_manual(values = pal_hydro) +
#   scale_shape_manual(values = shapes_data2)# +
#   #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))
# 
# plot_sdl_hydro_vulnerability_H_noclimate <- ggplot(data = filter(sdl_hydro_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a"), 
#                                                    #V1#aes(y = factor(variance_measure_achieved), 
#                                                    aes(y = factor(measure), 
#                                                    x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.position = "none",
#         #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
#         axis.title.y = element_blank())+
#   geom_vline(xintercept = mean_hydro_Stoch_ach) +
#   scale_colour_manual(values = pal_hydro)+
#   scale_shape_manual(values = shapes_data2)#+
#   #coord_cartesian(xlim = c(0,1))
# 
# #Economic:
# plot_sdl_economic_vulnerability_S_noclimate <- ggplot(data = filter(sdl_economic_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.position = "none")+
#   geom_vline(xintercept = mean_economic_Stoch_ach) +
#   geom_hline(yintercept = mean_economic_Stoch_var) +
#   scale_colour_manual(values = pal_hydro) +
#   scale_shape_manual(values = shapes_data2)# +
#   #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))
# 
# plot_sdl_economic_vulnerability_H_noclimate <- ggplot(data = filter(sdl_economic_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a"), 
#                                                       #V1#aes(y = factor(variance_measure_achieved), 
#                                                       aes(y = factor(measure), 
#                                                           x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.position = "none",
#         #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
#         axis.title.y = element_blank())+
#   geom_vline(xintercept = mean_economic_Stoch_ach) +
#   scale_colour_manual(values = pal_hydro)+
#   scale_shape_manual(values = shapes_data2)#+
#   #coord_cartesian(xlim = c(0,1))


#TWO:
plot_sdl_two_vulnerability_S_noclimate <- ggplot(data = filter(sdl_two_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  #theme(legend.position = "none")+
  geom_vline(xintercept = 0.5) +
  geom_hline(yintercept = 0.01) +
  scale_colour_manual(values = pal_theme) +
  scale_shape_manual(values = shapes_data2)# +
  #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_two_vulnerability_H_noclimate <- ggplot(data = filter(sdl_two_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a"), 
                                                      #V1#aes(y = factor(variance_measure_achieved), 
                                                      aes(y = factor(measure), 
                                                          x = measure_achieved, colour = measure, shape = Data)) + 
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.position = "none",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data2)#+
  #coord_cartesian(xlim = c(0,1))

```

### 1B) Vulnerability - no climate change - with ewater adaptation (HEW licvol)

(top right)

fill: light = licvol factor 0.5; dark = licvol factor 1.5; linked in order by the lines

There are no economic data for licvol (other than historic/no change licvol)

```{r}
#| label: 1B) Vulnerability 
#| echo: false
#| warning: false
#| message: false

sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = "all",#c('licvolfactor_1_0', 'licvolfactor_1_5', 'licvolfactor_0_5'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = "all",#c('licvolfactor_1_0', 'licvolfactor_1_5', 'licvolfactor_0_5'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

#Combining target hydro and Economic
# sdl_target_vulnerability$measure <- sdl_target_vulnerability$target
# sdl_target_vulnerability$measure_achieved <- sdl_target_vulnerability$ewr_achieved
# sdl_target_vulnerability$variance_measure_achieved <- sdl_target_vulnerability$variance_ewr_achieved
# sdl_target_vulnerability$relative_measure_achieved <- sdl_target_vulnerability$relative_ewr_achieved
# sdl_target_vulnerability$Theme <- "Target"

sdl_hydro_vulnerability$Theme <- "Water allocation"
sdl_Economic_baseline$Theme <- "Economic"

sdl_two_vulnerability <- bind_rows(sdl_hydro_vulnerability, sdl_Economic_baseline)
sdl_two_vulnerability$Theme <- factor(sdl_two_vulnerability$Theme, levels = c("Water allocation", "Economics"))

#EWR
plot_sdl_EWR_vulnerability_S_licvol <- ggplot(data = filter(sdl_EWR_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = mean_EWR_Stoch_ach) +
    geom_hline(yintercept = mean_EWR_Stoch_var) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_EWR_vulnerability_H_licvol <- ggplot(data = filter(sdl_EWR_vulnerability, Data == "Historic"), 
                                              #V1#aes(y = factor(variance_ewr_achieved),
                                              aes(y = ewr_code,
                                                  x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_EWR_Stoch_ach) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))

#Target
plot_sdl_target_vulnerability_S_licvol <- ggplot(data = filter(sdl_target_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = target, size = target, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = mean_target_Stoch_ach) +
    geom_hline(yintercept = mean_target_Stoch_var) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
  scale_size_manual(values = size_target)+
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_target_vulnerability_H_licvol <- ggplot(data = filter(sdl_target_vulnerability, Data == "Historic"),
                                                 #V1#aes(y = factor(variance_ewr_achieved),
                                                 aes(y = target,
                                                     x = ewr_achieved, colour = target, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = target, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_target_Stoch_ach) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))

# #hydro:
# plot_sdl_hydro_vulnerability_S_licvol <- ggplot(data = filter(sdl_hydro_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = licvolfactor)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal")+
#   geom_vline(xintercept = mean_hydro_Stoch_ach) +
#     geom_hline(yintercept = mean_hydro_Stoch_var) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro) +
#   scale_shape_manual(values = shapes_data2)# +
#   #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))
# 
# plot_sdl_hydro_vulnerability_H_licvol <- ggplot(data = filter(sdl_hydro_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), 
#                                                 #V1#aes(y = factor(variance_measure_achieved), 
#                                                 aes(y = measure, 
#                                                     x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = licvolfactor)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal",
#         #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
#         axis.title.y = element_blank())+
#   geom_vline(xintercept = mean_hydro_Stoch_ach) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro)+
#   scale_shape_manual(values = shapes_data2)#+
#   #coord_cartesian(xlim = c(0,1))

#Economic:
# scatterplot_sdl_economic_vulnerability_S_licvol <- ggplot(data = filter(sdl_economic_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = licvolfactor)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal")+
#   geom_vline(xintercept = mean_economic_Stoch_ach) +
#   geom_hline(yintercept = mean_economic_Stoch_var) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro) +
#   scale_shape_manual(values = shapes_data2)# +
#   #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

# plot_sdl_economic_vulnerability_H_licvol <- ggplot(data = filter(sdl_economic_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), 
#                                                    #V1#aes(y = factor(variance_measure_achieved),
#                                                    aes(y = measure, 
#                                                        x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = licvolfactor)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal",
#         #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
#         axis.title.y = element_blank())+
#   geom_vline(xintercept = mean_economic_Stoch_ach) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro)+
#   scale_shape_manual(values = shapes_data2)#+
#   #coord_cartesian(xlim = c(0,1))

#TWO:
plot_sdl_two_vulnerability_S_licvol <- ggplot(data = filter(sdl_two_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = measure, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = 0.5) +
    geom_hline(yintercept = 0.01) +
  scale_fill_manual(values = pal_theme)+
  scale_colour_manual(values = pal_theme) +
  scale_shape_manual(values = shapes_data2)# +
  #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_two_vulnerability_H_licvol <- ggplot(data = filter(sdl_two_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"),
                                                #V1#aes(y = factor(variance_measure_achieved),
                                                aes(y = measure,
                                                    x = measure_achieved, colour = measure, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = measure, alpha = licvolfactor)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_fill_manual(values = pal_theme)+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data2)#+
  #coord_cartesian(xlim = c(0,1))

```

### 1C) Vulnerability - no climate change - with ewater management (marks)

(bottom left)

fill: light = Mk4; dark = Mk5; linked in order by the lines (Mk4, Mk4a, Mk5a, MK5)

Marks are irrelevant for Economic results

```{r}
#| label: 1C) Vulnerability 
#| echo: false
#| warning: false
#| message: false

sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR', 'MACQ_CC_EFR_mkiv', 'MACQ_CC_EFR_mkv', 'MACQ_CC_EFR_mkva'),
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR', 'MACQ_CC_EFR_mkiv', 'MACQ_CC_EFR_mkv', 'MACQ_CC_EFR_mkva'), 
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

#EWR
plot_sdl_EWR_vulnerability_S_mks <- ggplot(data = filter(sdl_EWR_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = mean_EWR_Stoch_ach) +
    geom_hline(yintercept = mean_EWR_Stoch_var) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_EWR_vulnerability_H_mks <- ggplot(data = filter(sdl_EWR_vulnerability, Data == "Historic"), 
                                           #V1#aes(y = factor(variance_ewr_achieved), 
                                           aes(y = ewr_code, 
                                               x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_EWR_Stoch_ach) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))

#TARGET
plot_sdl_target_vulnerability_S_mks <- ggplot(data = filter(sdl_target_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = target, size = target, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = mean_target_Stoch_ach) +
  geom_hline(yintercept = mean_target_Stoch_var) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
  scale_size_manual(values = size_target)+
  coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_target_vulnerability_H_mks <- ggplot(data = filter(sdl_target_vulnerability, Data == "Historic"),
                                              #V1#aes(y = factor(variance_ewr_achieved),
                                              aes(y = target,
                                                  x = ewr_achieved, colour = target, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = target, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_target_Stoch_ach) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1))
# 
# #hydro:
# plot_sdl_hydro_vulnerability_S_mks <- ggplot(data = filter(sdl_hydro_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = Mark)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal")+
#   geom_vline(xintercept = mean_hydro_Stoch_ach) +
#     geom_hline(yintercept = mean_hydro_Stoch_var) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro) +
#   scale_shape_manual(values = shapes_data2)# +
#   #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))
# 
# plot_sdl_hydro_vulnerability_H_mks <- ggplot(data = filter(sdl_hydro_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0), 
#                                              #V1#aes(y = factor(variance_measure_achieved), 
#                                              aes(y = measure, 
#                                                  x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = Mark)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal",
#         #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
#         axis.title.y = element_blank())+
#   geom_vline(xintercept = mean_hydro_Stoch_ach) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro)+
#   scale_shape_manual(values = shapes_data2)#+
#   #coord_cartesian(xlim = c(0,1))

#Economic:
# scatterplot_sdl_economic_vulnerability_S_mks <- ggplot(data = filter(sdl_economic_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = licvolfactor)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal")+
#   geom_vline(xintercept = mean_economic_Stoch_ach) +
#   geom_hline(yintercept = mean_economic_Stoch_var) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro) +
#   scale_shape_manual(values = shapes_data2)# +
#   #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

# scatterplot_sdl_economic_vulnerability_H_mks <- ggplot(data = filter(sdl_economic_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & Mark == "Mk4a"), aes(y = factor(variance_measure_achieved), x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = licvolfactor)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal",
#         axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
#   geom_vline(xintercept = mean_economic_Stoch_ach) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro)+
#   scale_shape_manual(values = shapes_data2)#+
#   #coord_cartesian(xlim = c(0,1))

#TWO:
plot_sdl_two_vulnerability_S_mks <- ggplot(data = filter(sdl_two_vulnerability, names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = measure, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = 0.5) +
    geom_hline(yintercept = 0.01) +
  scale_fill_manual(values = pal_theme)+
  scale_colour_manual(values = pal_theme) +
  scale_shape_manual(values = shapes_data2)# +
  #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_two_vulnerability_H_mks <- ggplot(data = filter(sdl_two_vulnerability, Data == "Historic" & names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0),
                                             #V1#aes(y = factor(variance_measure_achieved),
                                             aes(y = measure,
                                                 x = measure_achieved, colour = measure, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = measure, alpha = Mark)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_fill_manual(values = pal_theme)+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data2)#+
  #coord_cartesian(xlim = c(0,1))

```

### 1D) Vulnerability - With climate change (no adaptation or management)

(bottom right)

fill: light = "Just wet"; dark = "hot and dry"; linked in order by the lines ("Just Wet", "Hot and Wet","Historical climate","Just Hot","Just Dry","Hot and Dry")

NEED to reverse order of the factor, but only for these figs. not sure how right now.

```{r}
#| label: 1D) Vulnerability 
#| echo: false
#| warning: false
#| message: false

sdl_EWR_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR_mkiv'), 
                                    licvol = c('licvolfactor_1_0'),
                                    climate = "all",#c('r0_8_e1_07', 'r1_0_e1_0', 'r1_2_e1_0'),
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

sdl_target_vulnerability <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR_mkiv'), 
                                    licvol = c('licvolfactor_1_0'),
                                    climate = "all",#c('r0_8_e1_07', 'r1_0_e1_0', 'r1_2_e1_0'),
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

#EWR
plot_sdl_EWR_vulnerability_S_climate <- ggplot(data = filter(sdl_EWR_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = mean_EWR_Stoch_ach) +
    geom_hline(yintercept = mean_EWR_Stoch_var) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.02))#, ylim = c(0 , 0.003))

plot_sdl_EWR_vulnerability_H_climate <- ggplot(data = filter(sdl_EWR_vulnerability, Data == "Historic"), 
                                               #V1#aes(y = factor(variance_ewr_achieved), 
                                                   aes(y = ewr_code,
                                                   x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_line()+
  geom_point(aes(fill = ewr_code, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_EWR_Stoch_ach) +
  scale_fill_manual(values = pal_EWR)+
  scale_colour_manual(values = pal_EWR)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1), ylim = c(0, 0.02))

#TARGET
plot_sdl_target_vulnerability_S_climate <- ggplot(data = filter(sdl_target_vulnerability), aes(y = variance_ewr_achieved, x = ewr_achieved, colour = target, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = target, size = target, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = mean_target_Stoch_ach) +
  geom_hline(yintercept = mean_target_Stoch_var) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2) +
  scale_size_manual(values = size_target)+
  coord_cartesian(xlim = c(0,1), ylim = c(0, 0.02))

plot_sdl_target_vulnerability_H_climate <- ggplot(data = filter(sdl_target_vulnerability, Data == "Historic"),
                                                  #V1#aes(y = factor(variance_ewr_achieved),
                                                      aes(y = target,
                                                      x = ewr_achieved, colour = target, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = target, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = mean_target_Stoch_ach) +
  scale_fill_manual(values = pal_Target)+
  scale_colour_manual(values = pal_Target)+
  scale_shape_manual(values = shapes_data2)+
  coord_cartesian(xlim = c(0,1), ylim = c(0, 0.02))

# #hydro:
# plot_sdl_hydro_vulnerability_S_climate <- ggplot(data = filter(sdl_hydro_vulnerability, licvolfactor == 1.0 & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = names_CSIRO_climate_scenario)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal")+
#   geom_vline(xintercept = mean_hydro_Stoch_ach) +
#     geom_hline(yintercept = mean_hydro_Stoch_var) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro) +
#   scale_shape_manual(values = shapes_data2)# +
#   #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))
# 
# plot_sdl_hydro_vulnerability_H_climate <- ggplot(data = filter(sdl_hydro_vulnerability, Data == "Historic" & licvolfactor == 1.0 & Mark == "Mk4a"), 
#                                                  #V1#aes(y = factor(variance_measure_achieved), 
#                                                      aes(y = measure,
#                                                      x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = names_CSIRO_climate_scenario)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal",
#         #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
#         axis.title.y = element_blank())+
#   geom_vline(xintercept = mean_hydro_Stoch_ach) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro)+
#   scale_shape_manual(values = shapes_data2)#+
#   #coord_cartesian(xlim = c(0,1))
# 
# #Economic:
# plot_sdl_economic_vulnerability_S_climate <- ggplot(data = filter(sdl_economic_vulnerability, licvolfactor == 1.0 & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) +
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = names_CSIRO_climate_scenario)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal")+
#   geom_vline(xintercept = mean_economic_Stoch_ach) +
#   geom_hline(yintercept = mean_economic_Stoch_var) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro) +
#   scale_shape_manual(values = shapes_data2)# +
#   #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))
# 
# plot_sdl_economic_vulnerability_H_climate <- ggplot(data = filter(sdl_economic_vulnerability, Data == "Historic" & licvolfactor == 1.0 & Mark == "Mk4a"), 
#                                                     #V1#aes(y = factor(variance_measure_achieved), 
#                                                     aes(y = measure,
#                                                     x = measure_achieved, colour = measure, shape = Data)) + 
#   geom_line()+
#   geom_point(aes(fill = measure, alpha = names_CSIRO_climate_scenario)) +
#   geom_point() +
#   theme_werp_toolkit()+
#   theme(legend.box = "horizontal",
#         #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
#         axis.title.y = element_blank())+
#   geom_vline(xintercept = mean_economic_Stoch_ach) +
#   scale_fill_manual(values = pal_hydro)+
#   scale_colour_manual(values = pal_hydro)+
#   scale_shape_manual(values = shapes_data2)#+
#   #coord_cartesian(xlim = c(0,1))

#TWO:
plot_sdl_two_vulnerability_S_climate <- ggplot(data = filter(sdl_two_vulnerability, licvolfactor == 1.0 & Mark == "Mk4a"), aes(y = variance_measure_achieved, x = measure_achieved, colour = measure, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = measure, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal")+
  geom_vline(xintercept = 0.5) +
    geom_hline(yintercept = 0.01) +
  scale_fill_manual(values = pal_theme)+
  scale_colour_manual(values = pal_theme) +
  scale_shape_manual(values = shapes_data2)# +
  #coord_cartesian(xlim = c(0,1))#, ylim = c(0 , 0.003))

plot_sdl_two_vulnerability_H_climate <- ggplot(data = filter(sdl_two_vulnerability, Data == "Historic" & licvolfactor == 1.0 & Mark == "Mk4a"),
                                                 #V1#aes(y = factor(variance_measure_achieved),
                                                     aes(y = measure,
                                                     x = measure_achieved, colour = measure, shape = Data)) +
  geom_line()+
  geom_point(aes(fill = measure, alpha = names_CSIRO_climate_scenario)) +
  geom_point() +
  theme_werp_toolkit()+
  theme(legend.box = "horizontal",
        #V1#axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank())+
        axis.title.y = element_blank())+
  geom_vline(xintercept = 0.5) +
  scale_fill_manual(values = pal_theme)+
  scale_colour_manual(values = pal_theme)+
  scale_shape_manual(values = shapes_data2)#+
  #coord_cartesian(xlim = c(0,1))

```

## Figure 1 - Vulnerability - Stochastic data

```{r}
#| label: Figure 1 - Stochastic Vulnerability 
#| echo: false
#| warning: false
#| message: false

#EWR
VulnerabilityPlot_EWR_Stochastic <- plot_sdl_EWR_vulnerability_S_noclimate + plot_sdl_EWR_vulnerability_S_licvol + 
plot_sdl_EWR_vulnerability_S_mks + plot_sdl_EWR_vulnerability_S_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
  coord_cartesian(xlim = c(0,1),ylim = c(0, 0.02))&
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

#TARGET
VulnerabilityPlot_target_Stochastic <- plot_sdl_target_vulnerability_S_noclimate + plot_sdl_target_vulnerability_S_licvol + 
plot_sdl_target_vulnerability_S_mks + plot_sdl_target_vulnerability_S_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
  coord_cartesian(xlim = c(0,1), ylim = c(0 , 0.003))&
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

# #hydro
# VulnerabilityPlot_WaterAllocation_Stochastic <- plot_sdl_hydro_vulnerability_S_noclimate + plot_sdl_hydro_vulnerability_S_licvol + 
# plot_sdl_hydro_vulnerability_S_mks + plot_sdl_hydro_vulnerability_S_climate + 
#   plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
#   coord_cartesian(xlim = c(0,1),ylim = c(0, 0.2)) &
#   guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))
# 
# #Economic
# VulnerabilityPlot_Economic_Stochastic <- plot_sdl_economic_vulnerability_S_noclimate + plot_spacer() + 
# plot_spacer() + plot_sdl_economic_vulnerability_S_climate + 
#   plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
#   coord_cartesian(xlim = c(0,1),ylim = c(2500000, 5000000)) &
#   guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

#TWO
VulnerabilityPlot_two_Stochastic <- plot_sdl_two_vulnerability_S_noclimate + plot_sdl_two_vulnerability_S_licvol + 
plot_sdl_two_vulnerability_S_mks + plot_sdl_two_vulnerability_S_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
  #coord_cartesian(xlim = c(0,1),ylim = c(0, 0.05)) &
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))


ggsave_multi(plot = VulnerabilityPlot_EWR_Stochastic, filename = file.path(comp_results, paste0("VulnerabilityPlot_EWR_Stochastic",Sys.Date())), device = c('png', 'svg'), width = 7, height = 5)

ggsave_multi(plot = VulnerabilityPlot_target_Stochastic, filename = file.path(comp_results, paste0("VulnerabilityPlot_target_Stochastic",Sys.Date())), device = c('png', 'svg'), width = 7, height = 5)

# ggsave_multi(plot = VulnerabilityPlot_WaterAllocation_Stochastic, filename = file.path(comp_results, paste0("VulnerabilityPlot_WaterAllocation_Stochastic",Sys.Date())), device = c('png', 'svg'), width = 7, height = 5)
# 
# ggsave_multi(plot = VulnerabilityPlot_Economic_Stochastic, filename = file.path(comp_results, paste0("VulnerabilityPlot_Economic_Stochastic",Sys.Date())), device = c('png', 'svg'), width = 7, height = 5)

ggsave_multi(plot = VulnerabilityPlot_two_Stochastic, filename = file.path(comp_results, paste0("VulnerabilityPlot_two_Stochastic",Sys.Date())), device = c('png', 'svg'), width = 7, height = 5)

# VulnerabilityPlot_EWR_Stochastic
# print("Fig 1. Vulnerabiliy in EWRs - Stochastic")
# VulnerabilityPlot_target
# print("Fig 1. Vulnerabiliy in target groups - Stochastic")
# VulnerabilityPlot_WaterAllocation_Stochastic
# print("Fig 1. Vulnerabiliy in water allocation - Stochastic")
# VulnerabilityPlot_Economic_Stochastic
# print("Fig 1. Vulnerabiliy in economic benefits - Stochastic")
```

```{r}
#| label: Fig 1. Vulnerabiliy in EWRs - Stochastic
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Fig 1. Vulnerabiliy in EWRs - Stochastic

VulnerabilityPlot_EWR_Stochastic

```

```{r}
#| label: Fig 1. Vulnerabiliy in ecological targets - Stochastic
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Fig 1. Vulnerabiliy in ecological targets - Stochastic

VulnerabilityPlot_target_Stochastic

```

```{r}
#| label: Fig 1. Vulnerabiliy in economic benefits and water allocation relilience and reliabitity - Stochastic
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Fig 1. Vulnerabiliy in economic benefits and water allocation relilience and reliabitity - Stochastic

VulnerabilityPlot_two_Stochastic

```


## Figure 1 - Vulnerability - Historic data

```{r}
#| label: Figure 1 - Historic Vulnerability 
#| echo: false
#| warning: false
#| message: false

#EWR
VulnerabilityPlot_EWR_Historic <- plot_sdl_EWR_vulnerability_H_noclimate + plot_sdl_EWR_vulnerability_H_licvol + 
plot_sdl_EWR_vulnerability_H_mks + plot_sdl_EWR_vulnerability_H_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
  coord_cartesian(xlim = c(0,1))&
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

#TARGET
VulnerabilityPlot_target_Historic <- plot_sdl_target_vulnerability_H_noclimate + plot_sdl_target_vulnerability_H_licvol +
plot_sdl_target_vulnerability_H_mks + plot_sdl_target_vulnerability_H_climate +
  plot_layout(nrow = 2, axes = "collect", guides = "collect") &
  coord_cartesian(xlim = c(0,1))&
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))
# 
# #hydro
# VulnerabilityPlot_WaterAllocation_Historic <- plot_sdl_hydro_vulnerability_H_noclimate + plot_sdl_hydro_vulnerability_H_licvol + 
# plot_sdl_hydro_vulnerability_H_mks + plot_sdl_hydro_vulnerability_H_climate + 
#   plot_layout(nrow = 2, axes = "collect", guides = "collect") &
#   guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))
# 
# #Economic
# VulnerabilityPlot_Economic_Historic <- plot_sdl_economic_vulnerability_H_noclimate + plot_sdl_economic_vulnerability_H_licvol + 
# plot_spacer() + plot_sdl_economic_vulnerability_H_climate + 
#   plot_layout(nrow = 2, axes = "collect", guides = "collect") & 
#   coord_cartesian(xlim = c(90000,130000))& 
#   guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

#TWO
VulnerabilityPlot_two_Historic <- plot_sdl_two_vulnerability_H_noclimate + plot_sdl_two_vulnerability_H_licvol + 
plot_sdl_two_vulnerability_H_mks + plot_sdl_two_vulnerability_H_climate + 
  plot_layout(nrow = 2, axes = "collect", guides = "collect") &
  guides(alpha = "none", shape = "none", colour = guide_legend(""), fill = guide_legend(""))

ggsave_multi(plot = VulnerabilityPlot_EWR_Historic, filename = file.path(comp_results, paste0("VulnerabilityPlot_EWR_Historic",Sys.Date())), device = c('png', 'svg'), width = 7, height = 5)

ggsave_multi(plot = VulnerabilityPlot_target_Historic, filename = file.path(comp_results, paste0("VulnerabilityPlot_target_Historic",Sys.Date())), device = c('png', 'svg'), width = 7, height = 5)

# ggsave_multi(plot = VulnerabilityPlot_WaterAllocation_Historic, filename = file.path(comp_results, paste0("VulnerabilityPlot_WaterAllocation_Historic",Sys.Date())), device = c('png', 'svg'), width = 7, height = 5)
# 
# ggsave_multi(plot = VulnerabilityPlot_Economic_Historic, filename = file.path(comp_results, paste0("VulnerabilityPlot_Economic_Historic",Sys.Date())), device = c('png', 'svg'), width = 7, height = 5)

ggsave_multi(plot = VulnerabilityPlot_two_Historic, filename = file.path(comp_results, paste0("VulnerabilityPlot_two_Historic",Sys.Date())), device = c('png', 'svg'), width = 7, height = 5)

# VulnerabilityPlot_EWR_Historic
# print("Fig 1. Vulnerabiliy in EWRs - Historic")
# VulnerabilityPlot_target_Historic
# print("Fig 1. Vulnerabiliy in target groups - Historic")
# VulnerabilityPlot_WaterAllocation_Historic
# print("Fig 1. Vulnerabiliy in water allocation - Historic")
# VulnerabilityPlot_Economic_Historic
# print("Fig 1. Vulnerabiliy in economic benefits - Historic")

```

```{r}
#| label: Fig 1. Vulnerabiliy in EWRs - Historic
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Fig 1. Vulnerabiliy in EWRs - Historic

VulnerabilityPlot_EWR_Historic

```
```{r}
#| label: Fig 1. Vulnerabiliy in ecological targets - Historic
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Fig 1. Vulnerabiliy in ecological targets - Historic

VulnerabilityPlot_target_Historic

```


```{r}
#| label: Fig 1. Vulnerabiliy in Economic benfits and water allocation relilience and reliabitity - Historic
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Fig 1. Vulnerabiliy in Economic benfits and water allocation relilience and reliabitity - Historic

VulnerabilityPlot_two_Historic

```


## 2) Temporal variability - DONT RUN

stochastic error band with historic data - no climate change We dont have time series for Water allocation data (or at least Deakin don't)

```{r}
#| label: Figure 2 - Temporal variability 
#| eval: false
#| warning: false
#| message: false

sdl_EWR_timeseries <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_ewr_timeseries',
                                    max_handling = "remove")

sdl_target_timeseries <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_timeseries',
                                    max_handling = "remove")

#EWR
plot_sdl_EWR_temporal_variability <- sdl_EWR_timeseries|> 
  ggplot(aes(x = ewr_achieved, colour = ewr_code, linetype = Data)) + 
  stat_ecdf(data = sdl_EWR_timeseries, aes(group = scenario), alpha = 0.1) + 
  stat_ecdf(data = sdl_EWR_timeseries, geom = "step", colour = "black") +
  theme_werp_toolkit()+
  theme(legend.position = "none")+
  scale_colour_manual(values = pal_EWR)+ 
  scale_fill_manual(values = pal_EWR)+ 
  scale_linetype_manual(values = linetype_data)+
  facet_wrap(~ewr_code)

#TARGET
plot_sdl_target_temporal_variability <- sdl_target_timeseries|> 
  filter(Evapotranspiration == 1.00 & Rainfall== 1.0 & licvolfactor == 1.0)|>
  ggplot(aes(x = ewr_achieved, colour = env_group, linetype = Data)) + 
  stat_ecdf(data = sdl_target_timeseries, aes(group = scenario), alpha = 0.1) + 
  stat_ecdf(data = sdl_target_timeseries, geom = "step", colour = "black") +
  theme_werp_toolkit()+ 
    theme(legend.position = "none")+
  scale_colour_manual(values = pal_envgroup)+ 
  scale_fill_manual(values = pal_envgroup)+ 
  scale_linetype_manual(values = linetype_data)+
  facet_wrap(~env_group)

#Economic
plot_sdl_Economic_temporal_variability <- sdl_Economic_timeseries|> 
  filter(names_CSIRO_climate_scenario == "Historical climate" & licvolfactor == 1.0 & Mark == "Mk4a")|>
  ggplot(aes(x = economic_benefit, colour = measure, linetype = Data)) + 
  stat_ecdf(data = sdl_Economic_timeseries, aes(group = replicate), alpha = 0.1) + 
  stat_ecdf(data = sdl_Economic_timeseries, geom = "step", colour = "black") +
  theme_werp_toolkit()+ 
  theme(legend.position = "none")+
  scale_colour_manual(values = pal_hydro)+ 
  scale_fill_manual(values = pal_hydro)+ 
  scale_linetype_manual(values = linetype_data)+
  facet_wrap(~measure)

ggsave_multi(plot = plot_sdl_EWR_temporal_variability, filename = file.path(comp_results, paste0("CDF", "plot_sdl_EWR_temporal_variability_stochasticErrorBand_historic",Sys.Date())), device = c('png', 'svg'), width = 8, height = 6)

ggsave_multi(plot = plot_sdl_target_temporal_variability, filename = file.path(comp_results, paste0("CDF", "plot_sdl_target_temporal_variability_stochasticErrorBand_historic",Sys.Date())), device = c('png', 'svg'), width = 8, height = 4)

ggsave_multi(plot = plot_sdl_Economic_temporal_variability, filename = file.path(comp_results, paste0("CDF", "plot_sdl_Economic_temporal_variability",Sys.Date())), device = c('png', 'svg'), width = 4, height = 2)

plot_sdl_EWR_temporal_variability
print("Fig 2. Temporal variability in EWRs")
plot_sdl_target_temporal_variability
print("Fig 2. Temporal variability in target groups")
plot_sdl_Economic_temporal_variability
print("Fig 2. Temporal variability in economic benefits")
```

## NULL DATA

Null models = all non-events evenly dispersed in the time series or all at one end

```{r}
#| label: NULL DATA 
#| eval: false
#| warning: false
#| message: false

null_data <- data.frame(
  ewr_achieved = seq(from = 0, to = 1, by = 0.01),
  ewr_code = "CF",
  env_group = "NF",
  Data = "Null model")

null_data <- null_data |>
  mutate(n_years_achieved = 130*ewr_achieved,
         n_years_not_achieved = 130*(1-ewr_achieved),
         mean_max_interevent = n_years_not_achieved/n_years_achieved)|>
  mutate(mean_max_interevent = ifelse(mean_max_interevent == Inf, 130, mean_max_interevent),
         Data = "Stochastic")

null_data1 <- null_data
null_data1$Data <- "Historic"

null_data <- bind_rows(null_data, null_data1)

```

## 3) Spells plots - no climate change - DONT RUN

i dont think we can calculate interevent periods for economic or water allocation data

not sure what is going on with the CFs

```{r}
#| label: Figure 3 - Spells plots 
#| eval: false
#| warning: false
#| message: false

sdl_ewr_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_ewr_baseline',
                                    max_handling = "remove")

sdl_target_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_target_baseline',
                                    max_handling = "remove")

Spellsplot_sdl_EWR <- sdl_ewr_baseline |>
  filter(Mark == "Mk4a" & licvolfactor == 1.0 & names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot(aes(y = mean_max_interevent, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_point() +
  geom_line(data = null_data, aes(y = mean_max_interevent, x = ewr_achieved), colour = "black")+
  geom_line(data = null_data, aes(y = n_years_not_achieved, x = ewr_achieved), colour = "black")+
  facet_wrap(~Data)+
  theme_werp_toolkit()+
  # labs(y = "Mean Maximum_interevent_duration",
  #      x = "Mean ewr_achieved")+
  scale_colour_manual(values = pal_EWR) +
  scale_shape_manual(values = shapes_data2)+
  guides(shape = "none")

#TARGET
Spellsplot_sdl_target <- sdl_target_baseline |>
  filter(Mark == "Mk4a" & licvolfactor == 1.0 & names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot(aes(y = mean_max_interevent, x = ewr_achieved, colour = env_group, shape = Data)) + 
  geom_point() +
  geom_line(data = null_data, aes(y = mean_max_interevent, x = ewr_achieved), colour = "black")+
  geom_line(data = null_data, aes(y = n_years_not_achieved, x = ewr_achieved), colour = "black")+
  facet_wrap(~Data)+
  theme_werp_toolkit()+
  # labs(y = "Mean Maximum_interevent_duration",
  #      x = "Mean ewr_achieved")+
  scale_colour_manual(values = pal_envgroup) +
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  guides(shape = "none")

ggsave_multi(plot = Spellsplot_sdl_EWR, filename = file.path(comp_results, paste0("Spellsplot_sdl_EWR",Sys.Date())), device = c('png', 'svg'), width = 8, height = 4)
ggsave_multi(plot = Spellsplot_sdl_target, filename = file.path(comp_results, paste0("Spellsplot_sdl_target",Sys.Date())), device = c('png', 'svg'), width = 8, height = 4)

Spellsplot_sdl_EWR
print("Fig 3. Spells plot for EWRs")
Spellsplot_sdl_target
print("Fig 3. Spells plot for  target groups")

```

## Figs 4 - 7

Violins = stochastic variability

Circle points = historic data (with ewater adaptation and management for figs 6 and 7)

Normal and relative versions

have left triangle points on for only climate variability

## 4) Climate variability

historic CFs are now in the cloud of stochastic points; but small fresh 2 is at the very top.

```{r}
#| label: Figure 4 - Climate variability 
#| echo: false
#| warning: false
#| message: false


sdl_ewr_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_ewr_baseline',
                                    max_handling = "remove")

sdl_target_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv', 
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_target_baseline',
                                    max_handling = "remove")

scatterplot_sdl_EWR_climate_variability <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() + 
  geom_jitter(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),
              height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic" & 
                             Mark == "Mk4a" & 
                             licvolfactor == 1.0 & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = ewr_achieved, x = ewr_code, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#TARGET
scatterplot_sdl_target_climate_variability <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() + 
  geom_jitter(aes(y = ewr_achieved, x = target, colour = target, shape = Data),
              height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_target_baseline, 
                           Mark == "Mk4a" & 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = ewr_achieved, x = target, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_Target)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#hydro
scatterplot_sdl_hydro_climate_variability <- sdl_hydro_baseline |>
  filter(Data == "Stochastic" &
           names_CSIRO_climate_scenario == "Historical climate" &
           licvolfactor == 1.0 &
           Mark == "Mk4a") |>
  ggplot()+
  geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) +
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_hydro_baseline,
                           Data == "Historic" &
                             Mark == "Mk4a" &
                             licvolfactor == 1.0 &
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_hydro)+
  scale_fill_manual(values = pal_licvolfactor)+
  scale_shape_manual(values = shapes_data)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#Economic
scatterplot_sdl_Economic_climate_variability <- ggplot(data = filter(sdl_Economic_baseline,
                                                              Data == "Stochastic" &
                                                                names_CSIRO_climate_scenario == "Historical climate" &
                                                                licvolfactor == 1.0 &
                                                                Mark == "Mk4a")) +
  geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) +
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_Economic_baseline,
                           Data == "Historic" &
                             licvolfactor == 1.0 &
                             Mark == "Mk4a" &
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_hydro)+
  scale_fill_manual(values = pal_licvolfactor)+
  scale_shape_manual(values = shapes_data)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))


scatterplot_sdl_two_climate_variability <- ggplot(data = filter(sdl_two_baseline, 
                                                     Data == "Stochastic" & 
                                                       names_CSIRO_climate_scenario == "Historical climate" & 
                                                       licvolfactor == 1.0 & 
                                                       Mark == "Mk4a")) + 
  geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_two_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             Mark == "Mk4a" & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)

scatterplot_sdl_EWR_climate_variability
print("Fig 4. Climate variability on EWRs")
scatterplot_sdl_target_climate_variability
print("Fig 4. Climate variability on target groups")
# scatterplot_sdl_hydro_climate_variability
# print("Fig 4. Climate variability on water allocation")
# scatterplot_sdl_Economic_climate_variability
# print("Fig 4. Climate variability on economic benefits")

scatterplot_sdl_two_climate_variability
print("Fig 4. Climate variability on target groups, water allocation and economic benefits")

ggsave_multi(plot = scatterplot_sdl_EWR_climate_variability, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climate_variability",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_target_climate_variability, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climate_variability",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

# ggsave_multi(plot = scatterplot_sdl_hydro_climate_variability, filename = file.path(comp_results, paste0("scatterplot_sdl_WaterAllocation_climate_variability",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)
# 
# ggsave_multi(plot = scatterplot_sdl_Economic_climate_variability, filename = file.path(comp_results, paste0("scatterplot_sdl_Economic_climate_variability",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_two_climate_variability, filename = file.path(comp_results, paste0("scatterplot_sdl_two_climate_variability",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

```

## 4) RELATIVE Climate variability

```{r}
#| label: Figure 4 - RELATIVE Climate variability 
#| echo: false
#| warning: false
#| message: false

#EWR
scatterplot_sdl_EWR_climate_variability_baseline <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() +
  geom_jitter(aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = ewr_code,  colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate"), 
              aes(y = relative_ewr_achieved, x = ewr_code, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#target
scatterplot_sdl_target_climate_variability_baseline <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() +
  geom_jitter(aes(y = relative_ewr_achieved, x = target, colour = target, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = target,  colour = target), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_target_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate"), 
              aes(y = relative_ewr_achieved, x = target, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#hydro
scatterplot_sdl_hydro_climate_variability_baseline <- sdl_hydro_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() +
  geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_measure_achieved, x = measure,  colour = measure), fill = NA, scale = "width") +
  geom_point(data = filter(sdl_hydro_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate"), 
              aes(y = relative_measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#Economic
scatterplot_sdl_Economic_climate_variability_baseline <- sdl_Economic_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate")|>
  ggplot() +
  geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin( aes(y = relative_measure_achieved, x = measure,  colour = measure), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_Economic_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 & 
           names_CSIRO_climate_scenario == "Historical climate"), 
              aes(y = relative_measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#TARGET HYDRO ECONOMIC
scatterplot_sdl_two_climate_variability_baseline <- ggplot(data = filter(sdl_two_baseline, 
                                                     Data == "Stochastic" & 
                                                       names_CSIRO_climate_scenario == "Historical climate" & 
                                                       licvolfactor == 1.0 & 
                                                       Mark == "Mk4a")) + 
  geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data),
              height = 0) + 
  geom_violin(aes(y = relative_measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_two_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             Mark == "Mk4a" & 
                             names_CSIRO_climate_scenario == "Historical climate"), aes(y = relative_measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  facet_grid(~Theme, scales = 'free', space = 'free')+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))
  #ggforce::facet_row(vars(Theme), scales = 'free', space = 'free')

scatterplot_sdl_EWR_climate_variability_baseline
print("Fig 4. Climate variability on EWRs relative to historical climate")
scatterplot_sdl_target_climate_variability_baseline
print("Fig 4. Climate variability on target groups relative to historical climate")
# scatterplot_sdl_hydro_climate_variability_baseline
# print("Fig 4. Climate variability on water allocation relative to historical climate")
# scatterplot_sdl_Economic_climate_variability_baseline
# print("Fig 4. Climate variability on economic benefits relative to historical climate")
scatterplot_sdl_two_climate_variability_baseline
print("Fig 4. Climate variability on target groups, water allocation and economic benefits relative to historical climate")

ggsave_multi(plot = scatterplot_sdl_EWR_climate_variability_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climate_variability_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_target_climate_variability_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climate_variability_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

# ggsave_multi(plot = scatterplot_sdl_hydro_climate_variability_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_WaterAllocation_climate_variability_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)
# 
# ggsave_multi(plot = scatterplot_sdl_Economic_climate_variability_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_Economic_climate_variability_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_two_climate_variability_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_two_climate_variability_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

```

## 5) Climate change

```{r}
#| label: Figure 5 - Climate change 
#| echo: false
#| warning: false
#| message: false

scatterplot_sdl_EWR_climates <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic" & 
                             Mark == "Mk4a" & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = ewr_code, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#TARGET
scatterplot_sdl_target_climates <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = target, colour = target, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_target_baseline, 
                           Mark == "Mk4a" & 
                           Data == "Historic" & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = target, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_Target)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#hydro
scatterplot_sdl_hydro_climates <- sdl_hydro_baseline |>
  filter(Data == "Stochastic" & 
           licvolfactor == 1.0 & 
           Mark == "Mk4a")|> 
  ggplot()+
  #geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_hydro_baseline, 
                           Data == "Historic" & 
                             Mark == "Mk4a" & 
                             licvolfactor == 1.0 ), 
             aes(y = measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_hydro)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#Economic
scatterplot_sdl_two_climates <- ggplot(data = filter(sdl_two_baseline, 
                                                              Data == "Stochastic" & 
                                                                licvolfactor == 1.0 & 
                                                                Mark == "Mk4a")) + 
  #geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_two_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0 & 
                             Mark == "Mk4a"), 
             aes(y = measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_hydro)+
  scale_fill_manual(values = pal_licvolfactor)+   scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

scatterplot_sdl_EWR_climates
print("Fig 5. Climate change on EWRs")
scatterplot_sdl_target_climates
print("Fig 5. Climate change on target groups")
scatterplot_sdl_hydro_climates
print("Fig 5. Climate change on water allocation")
scatterplot_sdl_two_climates
print("Fig 5. Climate change on economic benefits")

ggsave_multi(plot = scatterplot_sdl_EWR_climates, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climate",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_target_climates, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climate",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_hydro_climates, filename = file.path(comp_results, paste0("scatterplot_sdl_WaterAllocation_climate",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_two_climates, filename = file.path(comp_results, paste0("scatterplot_sdl_two_climate",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

```

## 5) RELATIVE Climate change

```{r}
#| label: Figure 5 - RELATIVE Climate change 
#| echo: false
#| warning: false
#| message: false

#EWR
scatterplot_sdl_EWR_climates_baseline <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0), 
              aes(y = relative_ewr_achieved, x = ewr_code, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_licvolfactor)+   scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#target
scatterplot_sdl_target_climates_baseline <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_ewr_achieved, x = target, colour = target, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = target,  colour = target), fill = NA, scale = "width") +
  geom_point(data = filter(sdl_target_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0), 
              aes(y = relative_ewr_achieved, x = target, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#hydro
scatterplot_sdl_hydro_climates_baseline <- sdl_hydro_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_measure_achieved, x = measure,  colour = measure), fill = NA, scale = "width") +
  geom_point(data = filter(sdl_hydro_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0), 
              aes(y = relative_measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#two
scatterplot_sdl_two_climates_baseline <- sdl_two_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_measure_achieved, x = measure,  colour = measure), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_two_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0), 
              aes(y = relative_measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#TWO
scatterplot_sdl_two_climates_baseline <- sdl_two_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_measure_achieved, x = measure,  colour = measure), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_two_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0), 
              aes(y = relative_measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))



scatterplot_sdl_EWR_climates_baseline
print("Fig 5. Climate change on EWRs relative to historical climate")
scatterplot_sdl_target_climates_baseline
print("Fig 5. Climate change on target groups relative to historical climate")
# scatterplot_sdl_hydro_climates_baseline
# print("Fig 5. Climate change on water allocation relative to historical climate")
# scatterplot_sdl_two_climates_baseline
# print("Fig 5. Climate change on two benefits relative to historical climate")
scatterplot_sdl_two_climates_baseline

ggsave_multi(plot = scatterplot_sdl_EWR_climates_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climates_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_target_climates_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climates_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_hydro_climates_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_WaterAllocation_climates_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_two_climates_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_two_climates_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)


```

## 6) ewater adaptation (licvol)

```{r}
#| label: Figure 6 - ewater adaptation 
#| echo: false
#| warning: false
#| message: false

scatterplot_sdl_EWR_climates_licvol <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic" & 
                             Mark == "Mk4a"), 
             aes(y = ewr_achieved, x = ewr_code, shape = Data, fill = factor(licvolfactor)), colour = "black", size = 3, position = position_dodge(width = 0.75)) + 
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_licvolfactor)+
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  theme(legend.box = "horizontal")+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#fill = factor(licvolfactor)), colour = "black"
#alpha = licvolfactor), colour = "black",fill = "black"

#TARGET
scatterplot_sdl_target_climates_licvol <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = target, colour = target, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_target_baseline, 
                           Mark == "Mk4a" & 
                           Data == "Historic"), 
             aes(y = ewr_achieved, x = target, shape = Data, fill = factor(licvolfactor)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_Target)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#hydro
scatterplot_sdl_hydro_climates_licvol <- sdl_hydro_baseline |>
  filter(Data == "Stochastic" & 
           licvolfactor == 1.0 & 
           Mark == "Mk4a")|> 
  ggplot()+
  #geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_hydro_baseline, 
                           Data == "Historic" & 
                             Mark == "Mk4a"), 
             aes(y = measure_achieved, x = measure, shape = Data, fill = factor(licvolfactor)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_hydro)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  theme(legend.box = "horizontal")+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#two
scatterplot_sdl_two_climates_licvol <- ggplot(data = filter(sdl_two_baseline, 
                                                              Data == "Stochastic" & 
                                                                licvolfactor == 1.0 & 
                                                                Mark == "Mk4a")) + 
  #geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_two_baseline, 
                           Data == "Historic" & 
                             Mark == "Mk4a"), 
             aes(y = measure_achieved, x = measure, shape = Data, fill = factor(licvolfactor)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_hydro)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

scatterplot_sdl_EWR_climates_licvol
print("Fig 6. Climate change and ewater adaptation on EWRs")
scatterplot_sdl_target_climates_licvol
print("Fig 6. Climate change and ewater adaptation on target groups")
scatterplot_sdl_hydro_climates_licvol
# print("Fig 6. Climate change and ewater adaptation on water allocation")
# scatterplot_sdl_two_climates_licvol
print("Fig 6. Climate change and ewater adaptation on two benefits")


ggsave_multi(plot = scatterplot_sdl_EWR_climates_licvol, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climates_licvol",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_target_climates_licvol, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climates_licvol",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

# ggsave_multi(plot = scatterplot_sdl_hydro_climates_licvol, filename = file.path(comp_results, paste0("scatterplot_sdl_WaterAllocation_climates_licvol",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_two_climates_licvol, filename = file.path(comp_results, paste0("scatterplot_sdl_two_climates_licvol",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

```

## 6) RELATIVE ewater adaptation

```{r}
#| label: Figure 6 - RELATIVE ewater adaptation 
#| echo: false
#| warning: false
#| message: false

#EWR
scatterplot_sdl_EWR_climates_licvol_baseline <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data),
  #            height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" ), 
              aes(y = relative_ewr_achieved, x = ewr_code, shape = Data, fill = factor(licvolfactor)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  theme(legend.box = "horizontal")+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#target
scatterplot_sdl_target_climates_licvol_baseline <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_ewr_achieved, x = target, colour = target, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = target,  colour = target), fill = NA, scale = "width") +
  geom_point(data = filter(sdl_target_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a"), 
              aes(y = relative_ewr_achieved, x = target, shape = Data, fill = factor(licvolfactor)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#hydro
scatterplot_sdl_hydro_climates_licvol_baseline <- sdl_hydro_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_measure_achieved, x = measure,  colour = measure), fill = NA, scale = "width") +
  geom_point(data = filter(sdl_hydro_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a"), 
              aes(y = relative_measure_achieved, x = measure, shape = Data, fill = factor(licvolfactor)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#two
scatterplot_sdl_two_climates_licvol_baseline <- sdl_two_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_measure_achieved, x = measure,  colour = measure), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_two_baseline, 
           Data == "Historic" & 
           Mark == "Mk4a" ), 
              aes(y = relative_measure_achieved, x = measure, shape = Data, fill = factor(licvolfactor)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_licvolfactor)+      scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

scatterplot_sdl_EWR_climates_licvol_baseline
print("Fig 6. Climate change and ewater adaptation on EWRs relative to historical climate")
scatterplot_sdl_target_climates_licvol_baseline
print("Fig 6. Climate change and ewater adaptation on target groups relative to historical climate")
# scatterplot_sdl_hydro_climates_licvol_baseline
# print("Fig 6. Climate change and ewater adaptation on water allocation relative to historical climate")
scatterplot_sdl_two_climates_licvol_baseline
print("Fig 6. Climate change and ewater adaptation on two benefits relative to historical climate")

ggsave_multi(plot = scatterplot_sdl_EWR_climates_licvol_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climates_licvol_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_target_climates_licvol_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climates_licvol_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)
# 
# ggsave_multi(plot = scatterplot_sdl_hydro_climates_licvol_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_WaterAllocation_climates_licvol_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_two_climates_licvol_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_two_climates_licvol_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)
```

## 7) eWater management (Mks)

```{r}
#| label: Figure 7 - eWater management
#| echo: false
#| warning: false
#| message: false

sdl_ewr_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR', 'MACQ_CC_EFR_mkiv', 'MACQ_CC_EFR_mkv', 'MACQ_CC_EFR_mkva'),
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'all',
                                    aggname = 'sdl_ewr_baseline',
                                    max_handling = "remove")

sdl_target_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR', 'MACQ_CC_EFR_mkiv', 'MACQ_CC_EFR_mkv', 'MACQ_CC_EFR_mkva'),
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'all',
                                    aggname = 'sdl_target_baseline',
                                    max_handling = "remove")

scatterplot_sdl_EWR_climates_mks <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic"  & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = ewr_code, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  theme(legend.box = "horizontal")+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#TARGET
scatterplot_sdl_target_climates_mks <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = target, colour = target, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_target_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = target, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_Target)+
  scale_fill_manual(values = pal_mark)+      
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#hydro
scatterplot_sdl_hydro_climates_mks <- sdl_hydro_baseline |>
  filter(Data == "Stochastic" & 
           licvolfactor == 1.0 & 
           Mark == "Mk4a")|> 
  ggplot()+
  #geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_hydro_baseline, 
                           Data == "Historic" &  
                             licvolfactor == 1.0 ), 
             aes(y = measure_achieved, x = measure, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_hydro)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

# #Economic
#scatterplot_sdl_Economic_climates_mks <- ggplot(data = filter(sdl_Economic_baseline, 
#                                                               Data == "Stochastic" & 
#                                                                 licvolfactor == 1.0 & 
#                                                                 Mark == "Mk4a")) + 
#   #geom_jitter(aes(y = measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
#   geom_violin(aes(y = measure_achieved, x = measure, colour = measure), fill = NA, scale = "width") + #ask galen about this
#   geom_point(data = filter(sdl_Economic_baseline, 
#                            Data == "Historic" & 
#                              licvolfactor == 1.0), 
#              aes(y = measure_achieved, x = measure, shape = Data), colour = "black", fill = "black", size = 3, position = position_dodge(width = 0.75)) +
#   theme_werp_toolkit()+
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
#   scale_colour_manual(values = pal_hydro)+
#   scale_fill_manual(values = pal_mark)+   
# scale_shape_manual(values = shapes_data)+
#   facet_wrap(~ names_CSIRO_climate_scenario)


scatterplot_sdl_EWR_climates_mks
print("Fig 7. Climate change and ewater management on EWRs")
scatterplot_sdl_target_climates_mks
print("Fig 7. Climate change and ewater management on target groups")
scatterplot_sdl_hydro_climates_mks
print("Fig 7. Climate change and ewater management on water allocation")
# scatterplot_sdl_Economic_climates_mks
# print("Fig 7. Climate change and ewater management on economic benefits")

ggsave_multi(plot = scatterplot_sdl_EWR_climates_mks, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_target_climates_mks, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_hydro_climates_mks, filename = file.path(comp_results, paste0("scatterplot_sdl_WaterAllocation_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

# ggsave_multi(plot = scatterplot_sdl_Economic_climates_mks, filename = file.path(comp_results, paste0("scatterplot_sdl_Economic_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

```

## 7) RELATIVE eWater management

```{r}
#| label: Figure 7 - RELATIVE eWater management
#| echo: false
#| warning: false
#| message: false

#EWR
scatterplot_sdl_EWR_climates_mks_baseline <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
           Data == "Historic" &
           licvolfactor == 1.0), 
              aes(y = relative_ewr_achieved, x = ewr_code, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_EWR)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  theme(legend.box = "horizontal")+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#target
scatterplot_sdl_target_climates_mks_baseline <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_ewr_achieved, x = target, colour = target, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = target,  colour = target), fill = NA, scale = "width") +
  geom_point(data = filter(sdl_target_baseline, 
           Data == "Historic" & 
           licvolfactor == 1.0), 
              aes(y = relative_ewr_achieved, x = target, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#hydro
scatterplot_sdl_hydro_climates_mks_baseline <- sdl_hydro_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_measure_achieved, x = measure,  colour = measure), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_hydro_baseline, 
           Data == "Historic" & 
           licvolfactor == 1.0), 
              aes(y = relative_measure_achieved, x = measure, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#Economic
# scatterplot_sdl_Economic_climates_mks_baseline <- sdl_Economic_baseline |>
#   filter(Data == "Stochastic" & 
#            Mark == "Mk4a" & 
#            licvolfactor == 1.0)|>
#   ggplot() +
#   #geom_jitter(aes(y = relative_measure_achieved, x = measure, colour = measure, shape = Data), height = 0) + 
#   geom_violin( aes(y = relative_measure_achieved, x = measure,  colour = measure), fill = NA, scale = "width") + 
#   geom_point(data = filter(sdl_Economic_baseline, 
#            Data == "Historic" & 
#            licvolfactor == 1.0), 
#               aes(y = relative_measure_achieved, x = measure, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
#   theme_werp_toolkit()+
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
#   scale_colour_manual(values = pal_theme)+
#   scale_fill_manual(values = pal_mark)+   
#scale_shape_manual(values = shapes_data)+
#   facet_wrap(~ names_CSIRO_climate_scenario)

scatterplot_sdl_EWR_climates_mks_baseline
print("Fig 7. Climate change and ewater management on EWRs relative to historical climate")
scatterplot_sdl_target_climates_mks_baseline
print("Fig 7. Climate change and ewater management on target groups relative to historical climate")
scatterplot_sdl_hydro_climates_mks_baseline
print("Fig 7. Climate change and ewater management on water allocation relative to historical climate")
# scatterplot_sdl_Economic_climates_mks_baseline
# print("Fig 7. Climate change and ewater management on economic benefits relative to historical climate")

ggsave_multi(plot = scatterplot_sdl_EWR_climates_mks_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climates_mks_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_target_climates_mks_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climates_mks_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_hydro_climates_mks_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_WaterAllocation_climates_mks_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

# ggsave_multi(plot = scatterplot_sdl_Economic_climates_mks_baseline, filename = file.path(comp_results, paste0("scatterplot_sdl_Economic_climates_mks_baseline",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

```

## Paneled figures

## Figure 4 - Climate variability

```{r}
#| label: Figure 4 - Climate variability panels
#| echo: false
#| warning: false
#| message: false

#Climate variability
scatterplot_sdl_EWR_climate_variability_2 <- scatterplot_sdl_EWR_climate_variability +
scatterplot_sdl_EWR_climate_variability_baseline +
  plot_layout(nrow = 2, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())

scatterplot_sdl_target_climate_variability_2 <- scatterplot_sdl_target_climate_variability +
scatterplot_sdl_target_climate_variability_baseline +
  plot_layout(nrow = 2, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())

# scatterplot_sdl_hydro_climate_variability_2 <- scatterplot_sdl_hydro_climate_variability +
# scatterplot_sdl_hydro_climate_variability_baseline +
#   plot_layout(nrow = 2, guides = "collect", axes = "collect") &
#   guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
#   theme(axis.title.x = element_blank())

# scatterplot_sdl_Economic_climate_variability_2 <- scatterplot_sdl_Economic_climate_variability +
# scatterplot_sdl_Economic_climate_variability_baseline +
#   plot_layout(nrow = 2, guides = "collect", axes = "collect") &
#   guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
#   theme(axis.title.x = element_blank())

scatterplot_sdl_two_climate_variability_2 <- scatterplot_sdl_two_climate_variability +
scatterplot_sdl_two_climate_variability_baseline +
  plot_layout(nrow = 2, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())

ggsave_multi(plot = scatterplot_sdl_EWR_climate_variability_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_EWR_climate_variability",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_target_climate_variability_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_target_climate_variability",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

# ggsave_multi(plot = scatterplot_sdl_hydro_climate_variability_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_WaterAllocation_climate_variability",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)
# 
# ggsave_multi(plot = scatterplot_sdl_Economic_climate_variability_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_Economic_climate_variability",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_two_climate_variability_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_two_climate_variability",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)


scatterplot_sdl_EWR_climate_variability_2
scatterplot_sdl_target_climate_variability_2
# scatterplot_sdl_hydro_climate_variability_2
# scatterplot_sdl_Economic_climate_variability_2
scatterplot_sdl_two_climate_variability_2

```

##Figure 5 - Climates

```{r}
#| label: Figure 5 - Climates panels
#| echo: false
#| warning: false
#| message: false

#Climates
scatterplot_sdl_EWR_climates_2 <- scatterplot_sdl_EWR_climates +
scatterplot_sdl_EWR_climates_baseline +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())&
  facet_wrap(~ names_CSIRO_climate_scenario, ncol = 1)

scatterplot_sdl_target_climates_2 <- scatterplot_sdl_target_climates +
scatterplot_sdl_target_climates_baseline +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())&
  facet_wrap(~ names_CSIRO_climate_scenario, ncol = 1)

scatterplot_sdl_hydro_climates_2 <- scatterplot_sdl_hydro_climates +
scatterplot_sdl_hydro_climates_baseline +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())&
  facet_wrap(~ names_CSIRO_climate_scenario, ncol = 1)

# scatterplot_sdl_Economic_climates_2 <- scatterplot_sdl_Economic_climates +
# scatterplot_sdl_Economic_climates_baseline +
#   plot_layout(nrow = 1, guides = "collect", axes = "collect") &
#   guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
#   theme(axis.title.x = element_blank())&
#   facet_wrap(~ names_CSIRO_climate_scenario, ncol = 1)

ggsave_multi(plot = scatterplot_sdl_EWR_climates_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_EWR_climates",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

ggsave_multi(plot = scatterplot_sdl_target_climates_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_target_climates",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

ggsave_multi(plot = scatterplot_sdl_hydro_climates_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_WaterAllocation_climates",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

# ggsave_multi(plot = scatterplot_sdl_Economic_climates_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_Economic_climates",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

scatterplot_sdl_EWR_climates_2
scatterplot_sdl_target_climates_2
scatterplot_sdl_hydro_climates_2
# scatterplot_sdl_Economic_climates_2
```

##Figure 6 - ewater adaptation (licvol)

```{r}
#| label: Figure 6 - ewater adaptation panels
#| echo: false
#| warning: false
#| message: false

#licvol
scatterplot_sdl_EWR_climates_licvol_2 <- scatterplot_sdl_EWR_climates_licvol +
scatterplot_sdl_EWR_climates_licvol_baseline +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())&
  facet_wrap(~ names_CSIRO_climate_scenario, ncol = 1)

scatterplot_sdl_target_climates_licvol_2 <- scatterplot_sdl_target_climates_licvol +
scatterplot_sdl_target_climates_licvol_baseline +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())&
  facet_wrap(~ names_CSIRO_climate_scenario, ncol = 1)

scatterplot_sdl_hydro_climates_licvol_2 <- scatterplot_sdl_hydro_climates_licvol +
scatterplot_sdl_hydro_climates_licvol_baseline +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())&
  facet_wrap(~ names_CSIRO_climate_scenario, ncol = 1)

scatterplot_sdl_two_climates_licvol_2 <- scatterplot_sdl_two_climates_licvol +
scatterplot_sdl_two_climates_licvol_baseline +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())&
  facet_wrap(~ names_CSIRO_climate_scenario, ncol = 1)

ggsave_multi(plot = scatterplot_sdl_EWR_climates_licvol_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_EWR_climates_licvol",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

ggsave_multi(plot = scatterplot_sdl_target_climates_licvol_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_target_climates_licvol",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

ggsave_multi(plot = scatterplot_sdl_hydro_climates_licvol_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_WaterAllocation_climates_licvol",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

ggsave_multi(plot = scatterplot_sdl_two_climates_licvol_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_two_climates_licvol",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

scatterplot_sdl_EWR_climates_licvol_2

```

## Figure 7 - eWater management (Mks)

```{r}
#| label: Figure 7 - eWater management panels
#| echo: false
#| warning: false
#| message: false

#mks
scatterplot_sdl_EWR_climates_mks_2 <- scatterplot_sdl_EWR_climates_mks +
scatterplot_sdl_EWR_climates_mks_baseline +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())&
  facet_wrap(~ names_CSIRO_climate_scenario, ncol = 1)

scatterplot_sdl_target_climates_mks_2 <- scatterplot_sdl_target_climates_mks +
scatterplot_sdl_target_climates_mks_baseline +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())&
  facet_wrap(~ names_CSIRO_climate_scenario, ncol = 1)

scatterplot_sdl_hydro_climates_mks_2 <- scatterplot_sdl_hydro_climates_mks +
scatterplot_sdl_hydro_climates_mks_baseline +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = guide_legend(""), fill = guide_legend(""))&
  theme(axis.title.x = element_blank())&
  facet_wrap(~ names_CSIRO_climate_scenario, ncol = 1)

ggsave_multi(plot = scatterplot_sdl_EWR_climates_mks_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_EWR_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

ggsave_multi(plot = scatterplot_sdl_target_climates_mks_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_target_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

ggsave_multi(plot = scatterplot_sdl_hydro_climates_mks_2, filename = file.path(comp_results, paste0("PANELscatterplot_sdl_WaterAllocation_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 12)

```

## 8) Targeted EWR management

I very well may be duplicating work above, but will be easier to think through if I just build this I think. The targeted approach does do something; the green, blue, and red do not fall on teh purple points @fig-experiment and @fig-experiment-targets.

```{r}
#| label: targeted-data-in 
#| echo: false
#| warning: false
#| message: false

sdl_ewr_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR_mkiv',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_3',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_5',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_7'),
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'all',
                                    aggname = 'sdl_ewr_baseline',
                                    max_handling = "remove")

sdl_target_baseline <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR_mkiv',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_3',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_5',
                                             'MACQ_CC_EFR_mkv_exp11_eventcoef0_7'),
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'all',
                                    aggname = 'sdl_target_baseline',
                                    max_handling = "remove")


EWR_select <- c("VF", "BF2", "SF1", "SF2", "SF3", "LF2", "OB-WS4")

scatterplot_sdl_EWR_climates_mks_exp <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 &
           ewr_code %in% EWR_select)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
                           Data == "Historic"  & 
                             licvolfactor == 1.0 &
           ewr_code %in% EWR_select), 
             aes(y = ewr_achieved, x = ewr_code, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  theme(legend.box = "horizontal")+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#TARGET
scatterplot_sdl_target_climates_mks_exp <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() + 
  #geom_jitter(aes(y = ewr_achieved, x = target, colour = target, shape = Data), height = 0) + 
  geom_violin(aes(y = ewr_achieved, x = target, colour = target), fill = NA, scale = "width") + #ask galen about this
  geom_point(data = filter(sdl_target_baseline, 
                           Data == "Historic" & 
                             licvolfactor == 1.0), 
             aes(y = ewr_achieved, x = target, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_mark)+      
  scale_shape_manual(values = shapes_data)+
  coord_cartesian(ylim = c(0,1))+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#ggsave_multi(plot = scatterplot_sdl_EWR_climates_mks_exp, filename = file.path(comp_results, paste0("scatterplot_sdl_EWR_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

#ggsave_multi(plot = scatterplot_sdl_target_climates_mks_exp, filename = file.path(comp_results, paste0("scatterplot_sdl_target_climates_mks",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

```
## 8) RELATIVE Targeted EWR management

```{r}
#EWR
scatterplot_sdl_EWR_climates_mks_baseline_exp <- sdl_ewr_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0 &
           ewr_code %in% EWR_select)|>
  ggplot() +
  #geom_jitter(aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = ewr_code, colour = ewr_code), fill = NA, scale = "width") + 
  geom_point(data = filter(sdl_ewr_baseline, 
           Data == "Historic" &
           licvolfactor == 1.0 &
           ewr_code %in% EWR_select), 
              aes(y = relative_ewr_achieved, x = ewr_code, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  theme(legend.box = "horizontal")+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

#target
scatterplot_sdl_target_climates_mks_baseline_exp <- sdl_target_baseline |>
  filter(Data == "Stochastic" & 
           Mark == "Mk4a" & 
           licvolfactor == 1.0)|>
  ggplot() +
  #geom_jitter(aes(y = relative_ewr_achieved, x = target, colour = target, shape = Data), height = 0) + 
  geom_violin( aes(y = relative_ewr_achieved, x = target,  colour = target), fill = NA, scale = "width") +
  geom_point(data = filter(sdl_target_baseline, 
           Data == "Historic" & 
           licvolfactor == 1.0), 
              aes(y = relative_ewr_achieved, x = target, shape = Data, fill = factor(Mark)), colour = "black", size = 3, position = position_dodge(width = 0.75)) +
  theme_werp_toolkit()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  scale_colour_manual(values = pal_theme2)+
  scale_fill_manual(values = pal_mark)+   
  scale_shape_manual(values = shapes_data)+
  facet_wrap(~ names_CSIRO_climate_scenario)+
  guides(shape = "none", colour = "none", fill = guide_legend(override.aes=list(shape = 21)))

ggsave_multi(plot = scatterplot_sdl_EWR_climates_mks_baseline_exp, filename = file.path(comp_results, paste0("EXP_","scatterplot_sdl_EWR_climates_mks_baseline_exp",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

ggsave_multi(plot = scatterplot_sdl_target_climates_mks_baseline_exp, filename = file.path(comp_results, paste0("EXP_","scatterplot_sdl_target_climates_mks_baseline_exp",Sys.Date())), device = c('png', 'svg'),  width = 8, height = 5)

```

```{r}
#| label: Fig 8. Targeted EWRs - EWRs
#| echo: false
#| warning: false
#| message: false
#| fig-cap:  Fig 8. Targeted EWRs - EWRs
#| 
#EWR
scatterplot_sdl_EWR_climates_mks_exp2 <- scatterplot_sdl_EWR_climates_mks_exp +
scatterplot_sdl_EWR_climates_mks_baseline_exp +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = "none", fill = guide_legend(title = "", override.aes=list(shape = 21)))&
  theme(axis.title.x = element_blank()) &
  facet_wrap(~ names_CSIRO_climate_scenario, nrow = 6)

scatterplot_sdl_EWR_climates_mks_exp2

```

```{r}
#| label: Fig 8. Targeted EWRs - targets
#| echo: false
#| warning: false
#| message: false
#| fig-cap:  Fig 8. Targeted EWRs - targets
#target
scatterplot_sdl_target_climates_mks_exp2 <- scatterplot_sdl_target_climates_mks_exp +
scatterplot_sdl_target_climates_mks_baseline_exp +
  plot_layout(nrow = 1, guides = "collect", axes = "collect") &
  guides(shape = "none", colour = "none", fill = guide_legend(title = "", override.aes=list(shape = 21)))&
  theme(axis.title.x = element_blank())&
  facet_wrap(~ names_CSIRO_climate_scenario, nrow = 6)

scatterplot_sdl_target_climates_mks_exp2
```

## Galens plots:
```{r}
#| label: fig-experiment
#| fig-cap: Does targeting flows towards EWRs work? Purple is the original Mk4a runs (with distribution), other coloured points are the 'experiments'. So if the red, green, or blue points are off the purple point, they differ from the original and targeting is doing something.
exp_11_plot <- ggplot(dplyr::filter(sdl_ewr_baseline, Data == 'Historic'),
             mapping = aes(x = ewr_code, y = ewr_achieved, 
                           color = Mark, shape = Data)) +
    geom_violin(data = dplyr::filter(sdl_ewr_baseline, Data == 'Stochastic'),
              scale = 'width') +
  geom_point() +
  facet_grid(names_CSIRO_climate_scenario ~ licvolfactor) +
  theme_werp_toolkit(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

exp_11_plot

ggsave_multi(plot = exp_11_plot, 
             filename = file.path(comp_results, "exp_11_plot"),
             device = c("png", "svg"),
       width = 24, height = 16, units = 'cm')
```

```{r}
#| label: fig-experiment-targets
#| fig-cap: Does targeting flows towards EWRs work? Purple is the original Mk4a runs (with distribution), other coloured points are the 'experiments'. So if the red, green, or blue points are off the purple point, they differ from the original and targeting is doing something.
exp_11_plot_target <- ggplot(dplyr::filter(sdl_target_baseline, Data == 'Historic'),
             mapping = aes(x = target, y = ewr_achieved, 
                           color = Mark, shape = Data)) +
    geom_violin(data = dplyr::filter(sdl_target_baseline, 
                                     Data == 'Stochastic'),
              scale = 'width') +
  geom_point() +
  facet_grid(names_CSIRO_climate_scenario ~ licvolfactor) +
  theme_werp_toolkit(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

exp_11_plot_target

ggsave_multi(plot = exp_11_plot_target, 
             filename = file.path(comp_results, "exp_11_plot_target"),
             device = c("png", "svg"),
       width = 24, height = 16, units = 'cm')
```

## another look at things

I was expecting this plot, but didn't see it and I'm curious about it. I made 4; ewrs and targets with the effect of licvolfactor @fig-licvolewr-diffs-variance and @fig-licvoltarget-diffs-variance, and Mark @fig-markewr-diffs-variance and @fig-marktarget-diffs-variance.

```{r}
#| label: read-in-stoch-summaries
#| include: false
variance_climmark <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR',
                                             'MACQ_CC_EFR_mkiv',
                                             'MACQ_CC_EFR_mkv',
                                             'MACQ_CC_EFR_mkva'),
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'all',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

variance_licclim <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_ewr_vulnerability',
                                    max_handling = "remove")

variance_climmark_target <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = c('MACQ_CC_EFR',
                                             'MACQ_CC_EFR_mkiv',
                                             'MACQ_CC_EFR_mkv',
                                             'MACQ_CC_EFR_mkva'),
                                    licvol = c('licvolfactor_1_0'),
                                    climate = 'all',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

variance_licclim_target <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR_mkiv',
                                    licvol = 'all',
                                    climate = 'all',
                                    aggname = 'sdl_target_vulnerability',
                                    max_handling = "remove")

```

```{r}
#| label: fig-markewr-diffs-variance
#| fig-cap: How much does mark matter, with points as means and error bars as 1 sd over the stochastic runs. This is only for licvolfactor = 1.

mark_ewr_variance <- ggplot(filter(variance_climmark, Data == 'Stochastic'), 
       aes(x = ewr_code, y = ewr_achieved,
           color = Mark,
           ymin = ewr_achieved-sqrt(variance_ewr_achieved),
           ymax = ewr_achieved + sqrt(variance_ewr_achieved))) +
  geom_point(position = position_dodge(width = 1)) +
  geom_linerange(position = position_dodge(width = 1)) +
  facet_wrap(~names_CSIRO_climate_scenario) +
  theme_werp_toolkit(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave_multi(plot = mark_ewr_variance, 
             filename = file.path(comp_results, "mark_ewr_variance"),
             device = c("png", "svg"),
       width = 24, height = 16, units = 'cm')

mark_ewr_variance
```

```{r}
#| label: fig-licvolewr-diffs-variance
#| fig-cap: How much does licvolfactor matter, with points as means and error bars as 1 sd over the stochastic runs. This is only for Mark 4a.

licvol_ewr_variance <- ggplot(filter(variance_licclim, Data == 'Stochastic'), 
       aes(x = ewr_code, y = ewr_achieved,
           color = as.character(licvolfactor),
           ymin = ewr_achieved-sqrt(variance_ewr_achieved),
           ymax = ewr_achieved + sqrt(variance_ewr_achieved))) +
  geom_point(position = position_dodge(width = 1)) +
  geom_linerange(position = position_dodge(width = 1)) +
  facet_wrap(~names_CSIRO_climate_scenario) +
  theme_werp_toolkit(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave_multi(plot = licvol_ewr_variance, 
             filename = file.path(comp_results, "licvol_ewr_variance"),
             device = c("png", "svg"),
       width = 24, height = 16, units = 'cm')

licvol_ewr_variance
```

```{r}
#| label: fig-marktarget-diffs-variance
#| fig-cap: How much does mark matter, with points as means and error bars as 1 sd over the stochastic runs. This is only for licvolfactor = 1.
mark_target_variance <- ggplot(filter(variance_climmark_target, 
                                      Data == 'Stochastic'), 
       aes(x = names_CSIRO_climate_scenario, y = ewr_achieved,
           color = Mark,
           ymin = ewr_achieved-sqrt(variance_ewr_achieved),
           ymax = ewr_achieved + sqrt(variance_ewr_achieved))) +
  geom_point(position = position_dodge(width = 1)) +
  geom_linerange(position = position_dodge(width = 1)) +
  facet_wrap(~target) +
  theme_werp_toolkit(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave_multi(plot = mark_target_variance, 
             filename = file.path(comp_results, "mark_target_variance"),
             device = c("png", "svg"),
       width = 24, height = 16, units = 'cm')

mark_target_variance
```

```{r}
#| label: fig-licvoltarget-diffs-variance
#| fig-cap: How much does licvolfactor matter, with points as means and error bars as 1 sd over the stochastic runs. This is only for Mark 4a.
licvol_target_variance <- ggplot(filter(variance_licclim_target, Data == 'Stochastic'), 
       aes(x = names_CSIRO_climate_scenario, y = ewr_achieved,
           color = as.character(licvolfactor),
           ymin = ewr_achieved-sqrt(variance_ewr_achieved),
           ymax = ewr_achieved + sqrt(variance_ewr_achieved))) +
  geom_point(position = position_dodge(width = 1)) +
  geom_linerange(position = position_dodge(width = 1)) +
  facet_wrap(~target) +
  theme_werp_toolkit(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave_multi(plot = licvol_target_variance, 
             filename = file.path(comp_results, "licvol_target_variance"),
             device = c("png", "svg"),
       width = 24, height = 16, units = 'cm')

licvol_target_variance
```

