---
title: "Testing CF"
format: html
editor: visual
---

## Librarys

```{r}
#| include: false

library(werptoolkitr)
library(dplyr)
library(sf)
library(ggplot2)
library(patchwork)
library(tidyr)
library(ggridges)
```

## Paths

```{r}
#| include: false

if (Sys.info()['user'] == 'galen') {
  qaelpath <- '~/../Deakin University/QAEL - WERP in house - WERP'
} else if (Sys.info()['user'] == 'Georgiad') {
  qaelpath <- '~/Deakin University/QAEL - WERP - WERP'
} else if (Sys.info()['user'] == 'georgiad') {
  qaelpath <- 'C:/Users/georgiad/Deakin University/QAEL - WERP - WERP'
} else if (Sys.info()['user'] == 'Admin') {
  qaelpath <- 'C:/Users/Admin/Deakin University/QAEL - WERP in house - WERP'
} else {
  rlang::abort("YOU'RE NOT GALEN. PUT IN YOUR PATH TO QAEL-WERP")
}

# python can't use the tildes, so have to expand
qaelpath <- path.expand(qaelpath)

#
# hydrographs by data type
#TEMPORARILIY USING THIS DATA:
hydro_dir_stochastic = file.path(qaelpath, 'Toolkit/macq-data-no_climate_change')


ewr_results <- file.path(hydro_dir_stochastic, 'module_output', 'EWR')


```

palettes etc
```{r}
pal_EWR <- stats::setNames(c("#555555FF", '#7B3014FF', "#9E3D22FF", '#C35322FF', '#E77129FF', '#F59843FF',
                                            '#FCAD52FF', '#FFC07CFF', '#FFEDDAFF', '#D6E8F3FF', '#A3CCE5FF', '#7DAED1FF',
                                            '#6094BFFF', '#4677A5FF', '#2B5C8AFF'), 
                                          c("CF", "VF", "BF1", "BF2", "SF1", "SF2",
                                            "SF3", "LF1", "LF2", "OB-WL", "OB-WM", "OB-WS1",
                                            "OB-WS2", "OB-WS3", "OB-WS4"))
class(pal_EWR) <- 'colors'

shapes_data2 <- c(24,21)
names(shapes_data2) <- c("Stochastic", "Historic")

```

## Manual aggregation (Stochastic data)

```{r}
# DATA
# flow chart?
# need intermediate steps?
# baseline_compare {werptoolkitr]

#------
#QAEL - WERP in house - WERP/Toolkit/macq-data-no_climate_change/aggregator_output/EWR_timeseries.csv"
EWR_timing_timeseries <- read.csv(file.path(hydro_dir_stochastic, 'aggregator_output', 'EWR_timeseries.csv')) |>
    #switch CFs:
  dplyr::mutate(event_years = ifelse(grepl("CF", ewr_code), 1-event_years, event_years))

EWR_timing_timeseries$ewr_code <- factor(EWR_timing_timeseries$ewr_code, levels = c("CF", "VF", "BF1", "BF2", "SF1", "SF2", "SF3", "LF1", "LF2", "OB-WL", "OB-WM", "OB-WS1", "OB-WS2", "OB-WS3", "OB-WS4")) 


objective_mapping <- read.csv(file.path(qaelpath, 'Toolkit','CausalNetworks', 'EWR_to_Target_mapping.csv'))

objective_mapping$ewr_code <- factor(objective_mapping$ewr_code, levels = c("CF", "VF", "BF1", "BF2", "SF1", "SF2", "SF3", "LF1", "LF2", "OB-WL", "OB-WM", "OB-WS1", "OB-WS2", "OB-WS3", "OB-WS4")) 

```

```{r}
# Join scenario info
#-------------------
#Add temporarily the scenario info for NOW ONLY 
EWR_timing_timeseries <- EWR_timing_timeseries |>
  dplyr::mutate(Rainfall = as.numeric(1.0),
                Evapotranspiration = as.numeric(1.0),
                licvolfactor = as.numeric(1.0),
                Mk = as.character("Mk4"),
                Data = "Stochastic")

```

```{r}
# Calculate Max inter-event durations and ewr_achieved over the timeseries
#------------------------------------
gauge_EWR_timing_spells <- EWR_timing_timeseries |>
  group_by(scenario, ewr_code, ewr_code_timing, gauge, planning_unit_name)|>
  dplyr::mutate(event_group = cumsum(abs(c(0, diff(event_years)))),
                ewr_achieved = mean(ewr_achieved, na.rm = TRUE))|>
  group_by(scenario, Rainfall, Evapotranspiration, licvolfactor, Mk, Data,  ewr_code, ewr_code_timing, gauge, planning_unit_name, event_group)|>
  dplyr::mutate(event_group_n = n())|>
  dplyr::filter(event_years == 0)|>
  ungroup()|>
  group_by(scenario, Rainfall, Evapotranspiration, licvolfactor, Mk, Data,  ewr_code, ewr_code_timing, gauge, planning_unit_name)|>
  reframe(ewr_achieved = unique(ewr_achieved),  #this is right - saves making 2 separate dfs for ewr_achieved and interevent
          Maximum_interevent_duration = max(event_group_n))

gets <- EWR_timing_timeseries |> 
  group_by(scenario, Rainfall, Evapotranspiration, licvolfactor, Mk, Data,  ewr_code, ewr_code_timing, gauge, planning_unit_name) |> 
  summarise(maxInter = maxInterevent(event_years),
            ewr_achieved = ArithmeticMean(ewr_achieved)) |> 
  ungroup()
```

Aggregate to ewr_code
```{r}
gauge_EWR_spells <- gauge_EWR_timing_spells |>
  group_by(scenario, Rainfall, Evapotranspiration, licvolfactor, Mk, Data,  ewr_code, gauge, planning_unit_name)|>
  reframe(n_EWR_versions = n(),
          ewr_achieved = mean(ewr_achieved),
          mean_Maximum_interevent_duration = mean(Maximum_interevent_duration),
          Maximum_interevent_duration = max(Maximum_interevent_duration))

gets_code <- gets |> 
  group_by(scenario, Rainfall, Evapotranspiration, licvolfactor, Mk, Data,  ewr_code, gauge, planning_unit_name)|>
  reframe(ewr_achieved = ArithmeticMean(ewr_achieved),
          mean_Maximum_interevent_duration = ArithmeticMean(maxInter),
          Maximum_interevent_duration = Max(maxInter))
```

Checker
```{r}
gets_code |> 
  filter(scenario == 0 & Rainfall == 1 & Evapotranspiration == 1 & licvolfactor == 1 & Mk == 'Mk4' & Data == 'Stochastic' & ewr_code == 'CF') |> 
  select(ewr_code, gauge, planning_unit_name,  ewr_achieved, mean_Maximum_interevent_duration, Maximum_interevent_duration) |> 
  arrange(gauge, ewr_code) |>
  filter(mean_Maximum_interevent_duration > 0) |> 
  print(n = 25)

gauge_EWR_spells |> 
  filter(scenario == 0 & Rainfall == 1 & Evapotranspiration == 1 & licvolfactor == 1 & Mk == 'Mk4' & Data == 'Stochastic' & ewr_code == 'CF') |> 
  select(ewr_code, gauge, planning_unit_name, ewr_achieved, mean_Maximum_interevent_duration, Maximum_interevent_duration) |> 
  arrange(gauge, ewr_code) |>
  filter(mean_Maximum_interevent_duration > 0) |> 
  print(n = 25)
```

To planning units
```{r}
planning_unit_EWR_spells <- gauge_EWR_spells |>
  group_by(scenario, Rainfall, Evapotranspiration, licvolfactor, Mk, Data,  ewr_code, planning_unit_name)|>
  reframe(n_EWR_versions = Sum(n_EWR_versions),
          n_gauges = NumberOfValues(ewr_achieved),
          EWR_Variance = Variance(ewr_achieved), # Variance = between gauges
          ewr_achieved = mean(ewr_achieved),
          mean_Maximum_interevent_duration = mean(mean_Maximum_interevent_duration),
          Maximum_interevent_duration = max(Maximum_interevent_duration))

gets_pu <- gets_code |> 
  group_by(scenario, Rainfall, Evapotranspiration, licvolfactor, Mk, Data,  ewr_code, planning_unit_name)|>
  reframe(ewr_achieved = ArithmeticMean(ewr_achieved),
          mean_Maximum_interevent_duration = ArithmeticMean(mean_Maximum_interevent_duration),
          Maximum_interevent_duration = Max(Maximum_interevent_duration))
```

SDL units
```{r}
sdl_EWR_spells <- planning_unit_EWR_spells |>
  group_by(scenario, Rainfall, Evapotranspiration, licvolfactor, Mk, Data,  ewr_code)|>
  reframe(n_EWR_versions = Sum(n_EWR_versions),
          n_gauges = Sum(n_gauges),
          n_planning_units = NumberOfValues(ewr_achieved),
          EWR_Variance = Sum(EWR_Variance),
          ewr_achieved = mean(ewr_achieved),
          mean_Maximum_interevent_duration = mean(mean_Maximum_interevent_duration),
          Maximum_interevent_duration = max(Maximum_interevent_duration))

gets_sdl <- gets_pu  |>
  group_by(scenario, Rainfall, Evapotranspiration, licvolfactor, Mk, Data,  ewr_code)|>
  reframe(ewr_achieved = ArithmeticMean(ewr_achieved),
          mean_Maximum_interevent_duration = ArithmeticMean(mean_Maximum_interevent_duration),
          Maximum_interevent_duration = Max(Maximum_interevent_duration))
```

The plot

## NULL DATA

```{r}

null_data <- data.frame(
  ewr_achieved = seq(from = 0, to = 1, by = 0.01),
  ewr_code = "CF",
  env_group = "NF",
  Data = "Null model")

null_data <- null_data |>
  mutate(n_years_achieved = 130*ewr_achieved,
         n_years_not_achieved = 130*(1-ewr_achieved),
         mean_Maximum_interevent_duration = n_years_not_achieved/n_years_achieved)|>
  mutate(mean_Maximum_interevent_duration = ifelse(mean_Maximum_interevent_duration == Inf, 130, mean_Maximum_interevent_duration))
```

```{r}
plot_sdl_EWR_spells <- sdl_EWR_spells |>
  ggplot(aes(y = mean_Maximum_interevent_duration, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_point() +
  geom_line(data = null_data, aes(y = mean_Maximum_interevent_duration, x = ewr_achieved), colour = "black")+
  geom_line(data = null_data, aes(y = n_years_not_achieved, x = ewr_achieved), colour = "black")+
  #geom_hex()#+
  #facet_wrap(~ewr_code)+
  theme_werp_toolkit()+
  # labs(y = "Mean Maximum_interevent_duration",
  #      x = "Mean ewr_achieved")+
  scale_colour_manual(values = pal_EWR) +
  scale_shape_manual(values = shapes_data2)
plot_sdl_EWR_spells

plot_gets <- gets_sdl |>
  ggplot(aes(y = mean_Maximum_interevent_duration, x = ewr_achieved, colour = ewr_code, shape = Data)) + 
  geom_point() +
  geom_line(data = null_data, aes(y = mean_Maximum_interevent_duration, x = ewr_achieved), colour = "black")+
  geom_line(data = null_data, aes(y = n_years_not_achieved, x = ewr_achieved), colour = "black")+
  #geom_hex()#+
  #facet_wrap(~ewr_code)+
  theme_werp_toolkit()+
  # labs(y = "Mean Maximum_interevent_duration",
  #      x = "Mean ewr_achieved")+
  scale_colour_manual(values = pal_EWR) +
  scale_shape_manual(values = shapes_data2)

plot_sdl_EWR_spells + plot_gets
```


## Toolkit version

```{r}
sdl_clip <- sdl_units |> 
  dplyr::filter(SWSDLName == 'Macquarie–Castlereagh')
```

We need the better-matched code timings
```{r}
objective_mapping <- readr::read_csv(file.path(qaelpath, 'Toolkit', 'macquarie', 'EWR_to_Target_mapping.csv')) |> 
  dplyr::select(planning_unit_name, gauge, ewr_code, ewr_code_timing, env_group = target) |> 
  dplyr::mutate(ewr_code_timing = ifelse(is.na(ewr_code_timing), '', ewr_code_timing)) |> 
  dplyr::mutate(ewr_code_timing = paste0(ewr_code, '_', ewr_code_timing)|>
                  gsub('_$', '', x = _)) |> 
  dplyr::mutate(target = dplyr::case_when(      
    env_group == "NF" ~ "Native fish",
    env_group == "NV" ~ "Native vegetation" ,
    env_group == "OS" ~ "Other species",   
    env_group == "EF" ~ "Priority ecosystem function", 
    env_group == "WB" ~ "Waterbird",
    is.na(env_group) ~ NA
  )
  )

# a few functions work better with a list of dfs than a bare df.
objective_list <- list(objective_mapping)
```

```{r}
agg_sEs <- list(all_time = 'all_time',
                ewr_code = c("ewr_code_timing", "ewr_code"),
                planning_units = planning_units, 
                sdl_units = sdl_clip)

fun_sEs <- list(c('ArithmeticMean', 'maxInterevent'),
                c('ArithmeticMean', 'Max'),
                c('ArithmeticMean', 'Max'),
                c('ArithmeticMean', 'Max'))

# NEED TO JUST HIT THE FILES USED FOR EWR_TIMING_TIMESERIES HERE
```

```{r}
# The EWR_timing_timeseries comes from a csv in the aggregator part of this.
tkspells <- read_and_agg(
    datpath = file.path(hydro_dir_stochastic, 'module_output', 'EWR'),
    type = "achievement",
    geopath = bom_basin_gauges,
    causalpath = objective_list,
    groupers = "scenario",
    aggCols = c('ewr_achieved', 'event_years'),
    aggsequence = agg_sEs, # generalise to furr over all agg paths
    funsequence = fun_sEs, # generalise to furr of all agg paths
    keepAllPolys = FALSE,
    auto_ewr_PU = TRUE,
    saveintermediate = TRUE,
    returnList = TRUE)
```

```{r}
tksdl <- tkspells$sdl_units

retained_sEs <- c('sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_all_time_ArithmeticMean_ewr_achieved',
                  'sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_all_time_maxInterevent_event_years',
                  'sdl_units_Max_planning_units_Max_ewr_code_Max_all_time_maxInterevent_event_years')

tksdl <- tksdl |> 
  select(scenario, ewr_code, all_of(retained_sEs))

tksdl <- tksdl |>
      dplyr::rename_with(.fn = \(x) c('ewr_achieved', 'mean_Maximum_interevent_duration', 'max_max_interevent'), .cols = all_of(retained_sEs))

```

```{r}
plot_tk <- tksdl |>
  ggplot(aes(y = mean_Maximum_interevent_duration, x = ewr_achieved, colour = ewr_code)) + 
  geom_point() +
  geom_line(data = null_data, aes(y = mean_Maximum_interevent_duration, x = ewr_achieved), colour = "black")+
  geom_line(data = null_data, aes(y = n_years_not_achieved, x = ewr_achieved), colour = "black")+
  #geom_hex()#+
  #facet_wrap(~ewr_code)+
  theme_werp_toolkit()+
  # labs(y = "Mean Maximum_interevent_duration",
  #      x = "Mean ewr_achieved")+
  scale_colour_manual(values = pal_EWR) +
  scale_shape_manual(values = shapes_data2)

plot_tk
```




A couple simple checks
```{r}
cfin <- tkspells$agg_input |> 
  filter(ewr_code == 'CF' & scenario == '0') |> 
  select(year, event_years, ewr_achieved, ewr_code, ewr_code_timing, scenario, gauge, planning_unit_name) |> 
  arrange(gauge, year)

cfgin <- EWR_timing_timeseries |> 
  filter(ewr_code == 'CF' & scenario == '0') |> 
  tibble() |> 
  select(year, event_years, ewr_achieved, ewr_code, ewr_code_timing, scenario, gauge, planning_unit_name) |> 
  arrange(gauge, year)
```

```{r}
mean(cfin$ewr_achieved, na.rm = TRUE)
mean(cfgin$ewr_achieved, na.rm = TRUE)
mean(cfin$event_years, na.rm = TRUE)
mean(cfgin$event_years, na.rm = TRUE)
```
Those mean ewr_achieved hide something- they're actually flipped and /10. 
```{r}
cfgin |> print(n = 25)
cfin |> print(n = 25)
```

But how are those flipped?
```{r}
 annualdf <- get_any_ewr_output(dir = ewr_results, type = "yearly")

```

That doesn't actually flip them. So how are they flipped in the csv
```{r}
rawin <- annualdf |> 
  filter(ewr_code == 'CF' & scenario == '0') |> 
  tibble() |> 
  select(year, event_years, ewr_code, ewr_code_timing, scenario, gauge, planning_unit_name) |> 
  arrange(gauge, year)
```

what about NON-CF? are those flipped?
```{r}
rawbf <- annualdf |> 
  filter(ewr_code == 'BF1' & scenario == '0') |> 
  tibble() |> 
  select(year, event_years, ewr_code, ewr_code_timing, scenario, gauge, planning_unit_name) |> 
  arrange(gauge, year)

cfbf <- tkspells$agg_input |> 
  filter(ewr_code == 'BF1' & scenario == '0') |> 
  select(year, event_years, ewr_achieved, ewr_code, ewr_code_timing, scenario, gauge, planning_unit_name) |> 
  arrange(gauge, year)

cfgbf <- EWR_timing_timeseries |> 
  filter(ewr_code == 'BF1' & scenario == '0') |> 
  tibble() |> 
  select(year, event_years, ewr_achieved, ewr_code, ewr_code_timing, scenario, gauge, planning_unit_name) |> 
  arrange(gauge, year)
```

