---
title: "Example data in"
format: html
editor: visual
---

```{r}
library(werptoolkitr)
library(sf)
library(future.batchtools)
library(furrr)
```

This is the read-in and directory-crawling functions

```{r}
source('R/read_in_aggs.R')
source('R/paths.R')

# This is just all the list-making that's done below
# source('R/agg_variables.R')
```


## Names of the various aggregations

Not actually sure we need these as variables, but here they are.

```{r}
name_sEt <- 'sdl_ewr_timeseries'
name_sTt <- 'sdl_target_timeseries'
name_sEs <- 'sdl_ewr_spells'
name_sTs <- 'sdl_target_spells'
name_sEv <- 'sdl_ewr_vulnerability'
name_sTv <- 'sdl_target_vulnerability'
```

## Variables to retain and rename

```{r}
# sdl_ewr_timeseries
retained_sEt <- c('sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_ewr_achieved')

rename_sEt <- 'ewr_achieved'

# sdl_target_timeseries
retained_sTt <- c('sdl_units_ArithmeticMean_planning_units_ArithmeticMean_target_ArithmeticMean_ewr_code_ArithmeticMean_ewr_achieved')

rename_sTt <- 'ewr_achieved'

# sdl_ewr_spells
retained_sEs <- c('sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_all_time_ArithmeticMean_ewr_achieved',
                  'sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_all_time_maxInterevent_event_years',
                  'sdl_units_Max_planning_units_Max_ewr_code_Max_all_time_maxInterevent_event_years')
rename_sEs <- c('ewr_achieved',
                  'mean_max_interevent',
                  'max_interevent')

# sdl_target_spells
retained_sTs <- c('sdl_units_ArithmeticMean_planning_units_ArithmeticMean_target_ArithmeticMean_ewr_code_ArithmeticMean_all_time_ArithmeticMean_ewr_achieved',
                  'sdl_units_ArithmeticMean_planning_units_ArithmeticMean_target_ArithmeticMean_ewr_code_ArithmeticMean_all_time_maxInterevent_event_years',
                  'sdl_units_Max_planning_units_Max_target_Max_ewr_code_Max_all_time_maxInterevent_event_years')
rename_sTs <- c('ewr_achieved',
                  'mean_max_interevent',
                  'max_interevent')

```

And the vulnerabilities

```{r}
# sdl_ewr_vulnerability
retained_vE <- c('replicates_ArithmeticMean_sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_all_time_ArithmeticMean_ewr_achieved',
                'replicates_ArithmeticMean_sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_all_time_maxInterevent_event_years',
                'replicates_Max_sdl_units_Max_planning_units_Max_ewr_code_Max_all_time_maxInterevent_event_years',
                'replicates_Variance_sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_all_time_ArithmeticMean_ewr_achieved',
                'replicates_Variance_sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_all_time_maxInterevent_event_years',
                'replicates_Variance_sdl_units_Max_planning_units_Max_ewr_code_Max_all_time_maxInterevent_event_years')
rename_vE <- c('ewr_achieved',
               'mean_max_interevent',
               'max_interevent',
               'variance_ewr_achieved',
               'variance_mean_max_interevent',
               'variance_max_interevent')

# sdl_target_vulnerability
retained_vT <- c('replicates_ArithmeticMean_sdl_units_ArithmeticMean_planning_units_ArithmeticMean_target_ArithmeticMean_ewr_code_ArithmeticMean_all_time_ArithmeticMean_ewr_achieved',
                'replicates_ArithmeticMean_sdl_units_ArithmeticMean_planning_units_ArithmeticMean_target_ArithmeticMean_ewr_code_ArithmeticMean_all_time_maxInterevent_event_years',
                'replicates_Max_sdl_units_Max_planning_units_Max_target_Max_ewr_code_Max_all_time_maxInterevent_event_years',
                'replicates_Variance_sdl_units_ArithmeticMean_planning_units_ArithmeticMean_target_ArithmeticMean_ewr_code_ArithmeticMean_all_time_ArithmeticMean_ewr_achieved',
                'replicates_Variance_sdl_units_ArithmeticMean_planning_units_ArithmeticMean_target_ArithmeticMean_ewr_code_ArithmeticMean_all_time_maxInterevent_event_years',
                'replicates_Variance_sdl_units_Max_planning_units_Max_target_Max_ewr_code_Max_all_time_maxInterevent_event_years')

rename_vT <- c('ewr_achieved',
               'mean_max_interevent',
               'max_interevent',
               'variance_ewr_achieved',
               'variance_mean_max_interevent',
               'variance_max_interevent')
```

*This is probably the most useful*: A list with the aggregation/dataframe name as name, retained cols and last_agg as the values.

```{r}
aggregation_info <- list(sdl_ewr_timeseries = list(lastagg = 'sdl_units',
                                                   retained = retained_sEt,
                                                   renames = rename_sEt),
                         sdl_target_timeseries = list(lastagg = 'sdl_units',
                                                      retained = retained_sTt,
                                                      renames = rename_sTt),
                         sdl_ewr_spells = list(lastagg = 'sdl_units', 
                                               retained = retained_sEs,
                                               renames = rename_sEs),
                         sdl_target_spells = list(lastagg = 'sdl_units',
                                                  retained = retained_sTs,
                                                  renames = rename_sTs),
                         sdl_ewr_vulnerability = list(lastagg = 'replicates',
                                                      retained = retained_vE,
                                                      renames = rename_vE),
                         sdl_target_vulnerability = list(lastagg = 'replicates',
                                                         retained = retained_vT,
                                                         renames = rename_vT))
```

# Read-in

That list lets us simplify some of the ways we call things, though we can send in the name, lastagg and retention cols separately, as shown below.

We can read those in with read_in_aggs.

For a single dataframe, we can just use for example the sdl_ewr_timeseries:

```{r}
sdl_ewr_time_example <- read_in_aggs(project_dir = project_dir,
                          data_type = 'stochastic',
                          info_list = aggregation_info,
                          aggname = 'sdl_ewr_timeseries',
                            mark = 'MACQ_CC_EFR',
                            licvol = 'licvolfactor_1_0',
                            climate = 'r1_0_e1_0')
```

All of those up to `lastagg` can be vectors that let you bring in more than one and glue them together (though it's probably a terrible idea to glue together different 'aggname's).

So, if we wanted to bring in the vulnerability for both historical and stochastic for a given licvol, mark, and climate, we could use

```{r}
sdl_vuln_hs_example <- read_in_aggs(project_dir = project_dir,
                                    data_type = c('stochastic', 'historical'),
                                    info_list = aggregation_info,
                                    mark = 'MACQ_CC_EFR',
                                    licvol = 'licvolfactor_1_0',
                                    climate = 'r1_0_e1_0',
                                    aggname = 'sdl_target_vulnerability')
```

which has both historic and stochastic

```{r}
unique(sdl_vuln_hs_example$Data)
```

Similarly, maybe you want to pull in all the climates for a mark for the spells. Can use a character vector or 'all' is a special thing that goes and searches.

```{r}
sdl_spell_clims_example <- read_in_aggs(project_dir = project_dir,
                                        data_type = 'historical',
                                        info_list = aggregation_info,
                                        mark = 'MACQ_CC_EFR',
                                        licvol = 'licvolfactor_1_0',
                                        climate = 'all',
                                        aggname = 'sdl_target_spells')
```

```{r}
table(sdl_spell_clims_example$Rainfall, sdl_spell_clims_example$Evapotranspiration)
```

We can also just feed in paths manually as `data_path` if we construct them manually. You still need lastagg and retain_cols. Can use the info_list if that makes it easier though.

```{r}

random_target_spells <- list(
  "stochastic/MACQ_CC_EFR_mkiv/licvolfactor_1_0/r0_8_e1_07/sdl_target_spells",
  "stochastic/MACQ_CC_EFR_mkva/licvolfactor_1_0/r0_8_e1_0/sdl_target_spells",
  "stochastic/MACQ_CC_EFR_mkv/licvolfactor_1_0/r1_2_e1_0/sdl_target_spells"
  )

sdl_random_target_spells <- read_in_aggs(project_dir = project_dir,
                          data_path = random_target_spells,
                                    info_list = aggregation_info,
                          aggname = 'sdl_target_spells', # Not needed if the path above has it, but is needed if we don't want to pass in lastagg and retain_cols
                            # lastagg = 'sdl_units',
                            # retain_cols = retained_sTs
                          )
```

Check

```{r}
sdl_random_target_spells$Mk |> unique()
```

## TODO

What I haven't tested much is combinations, ie historical and stochastic, with all climates, but only one mark. They should typically work, but just not well-tested so make sure you got what you wanted..

## same as above, just not with the list

and not passing in the renames
```{r}
sdl_ewr_time_example <- read_in_aggs(project_dir = project_dir,
                          data_type = 'stochastic',
                            mark = 'MACQ_CC_EFR',
                            licvol = 'licvolfactor_1_0',
                            climate = 'r1_0_e1_0',
                            aggname = 'sdl_ewr_timeseries',
                            lastagg = 'sdl_units',
                            retain_cols = retained_sEt)
```

All of those up to `lastagg` can be vectors that let you bring in more than one and glue them together (though it's probably a terrible idea to glue together different 'aggname's).

So, if we wanted to bring in the vulnerability for both historical and stochastic for a given licvol, mark, and climate, we could use

```{r}
sdl_vuln_hs_example <- read_in_aggs(project_dir = project_dir,
                          data_type = c('stochastic', 'historical'),
                            mark = 'MACQ_CC_EFR',
                            licvol = 'licvolfactor_1_0',
                            climate = 'r1_0_e1_0',
                            aggname = 'sdl_target_vulnerability',
                            lastagg = 'replicates',
                            retain_cols = retained_vT)
```

which has both historic and stochastic

```{r}
unique(sdl_vuln_hs_example$Data)
```

Similarly, maybe you want to pull in all the climates for a mark for the spells. Can use a character vector or 'all' is a special thing that goes and searches.

```{r}
sdl_spell_clims_example <- read_in_aggs(project_dir = project_dir,
                          data_type = 'historical',
                            mark = 'MACQ_CC_EFR',
                            licvol = 'licvolfactor_1_0',
                            climate = 'all',
                            aggname = 'sdl_target_spells',
                            lastagg = 'sdl_units',
                            retain_cols = retained_sTs)
```

```{r}
table(sdl_spell_clims_example$Rainfall, sdl_spell_clims_example$Evapotranspiration)
```

We can also just feed in paths manually as `data_path` if we construct them manually. You still need lastagg and retain_cols

```{r}

random_target_spells <- list(
  "stochastic/MACQ_CC_EFR_mkiv/licvolfactor_1_0/r0_8_e1_07/sdl_target_spells",
  "stochastic/MACQ_CC_EFR_mkva/licvolfactor_1_0/r0_8_e1_0/sdl_target_spells",
  "stochastic/MACQ_CC_EFR_mkv/licvolfactor_1_0/r1_2_e1_0/sdl_target_spells"
  )

sdl_random_target_spells <- read_in_aggs(project_dir = project_dir,
                          data_path = random_target_spells,
                            lastagg = 'sdl_units',
                            retain_cols = retained_sTs)
```

Check

```{r}
sdl_random_target_spells$Mk |> unique()
```
