---
title: "Organise data"
format: html
editor: visual
---

## Data

Data from Ash on his blob. https://sho108storage.blob.core.windows.net/werp-deliverables/

Galen can access via CSIRO Azure account with Azure Storage Explorer. In process of sorting out programmatic access, for now it's just copied down.

This file is just going to extract the zips. The toolkit actually *can* read them straight out of the zip now, but unzipping seems better for clarity.

They're on the QAEL werp drive so we don't all have to have them locally. Very annoyingly, the WERP dir has different names for all of us. So it would be really nice to actually access a blob.

## Paths

```{r}
#| include: false

if (Sys.info()['user'] == 'galen') {
  qaelpath <- '~/../Deakin University/QAEL - WERP in house - WERP'
} else if (Sys.info()['user'] == 'Georgiad') {
  qaelpath <- '~/Deakin University/QAEL - WERP - WERP'
} else if (Sys.info()['user'] == 'georgiad') {
  qaelpath <- 'C:/Users/georgiad/Deakin University/QAEL - WERP - WERP'
} else if (Sys.info()['user'] == 'Admin') {
  qaelpath <- 'C:/Users/Admin/Deakin University/QAEL - WERP in house - WERP'
} else {
  rlang::abort("YOU'RE NOT GALEN. PUT IN YOUR PATH TO QAEL-WERP")
}

# python can't use the tildes, so have to expand
qaelpath <- path.expand(qaelpath)

# Outer directory for project data
project_dir = file.path(qaelpath, 'Toolkit', 'macq-data')

# hydrographs by data type
hydro_dir_historical = file.path(qaelpath, 'Toolkit/AshData/historical')
hydro_dir_stochastic = file.path(qaelpath, 'Toolkit/AshData/stochastic')

# Hydrographs (expected to exist already; created here with Ash_data_sorting.qmd)
#hydro_dir_Mk5a = file.path(qaelpath, 'Toolkit/AshData/historical/MACQ_CC_EFR_mkva')
hydro_dir_Mk5 = file.path(qaelpath, 'Toolkit/AshData/historical/MACQ_CC_EFR_mkv')
hydro_dir_Mk4a = file.path(qaelpath, 'Toolkit/AshData/historical/MACQ_CC_EFR_mkiv')
hydro_dir_Mk4 = file.path(qaelpath, 'Toolkit/AshData/historical/MACQ_CC_EFR')

# Generated data
#Mk5a_dir = file.path(project_dir, 'historic', 'Mk5a')
Mk5_dir = file.path(project_dir, 'historic', 'Mk5')
Mk4a_dir = file.path(project_dir, 'historic', 'Mk4a')
Mk4_dir = file.path(project_dir, 'historic', 'Mk4')

#OR

Models <- c('Mk5', 'Mk4', 'Mk4a') #'Mk5a', 

# module_output
ewr_results <- c('module_output', 'EWR') 

# outputs of aggregator. There may be multiple modules
agg_results <- c('aggregator_output','sdl_EWRs')
aggregations <-  c('sdl_EWRs', 'sdl_objective', 'sdl_objective_simple','sdl_target' , 'sdl_theme')

comp_results <- file.path(project_dir, 'comparer_output') 


#DATA PATHS - by data type
  hydro_paths <- list.files(hydro_dir_historical,  pattern="*Straight Node*", full.names=TRUE, recursive = TRUE)
  balance_paths <- list.files(hydro_dir_historical,  pattern="*h2o_table.nc", full.names=TRUE, recursive = TRUE)
  total_licvol_paths <- list.files(hydro_dir_historical,  pattern="*total_licvol.csv", full.names=TRUE, recursive = TRUE)
  
# #DATA PATHS - by Mk
#   hydro_paths <- list.files(hydro_dir_Mk5,  pattern="*Straight Node*", full.names=TRUE, recursive = TRUE)
#   balance_paths <- list.files(hydro_dir_Mk5,  pattern="*h2o_table.nc", full.names=TRUE, recursive = TRUE)
#   total_licvol_paths <- list.files(hydro_dir_Mk5,  pattern="*total_licvol.csv", full.names=TRUE, recursive = TRUE)
    
  
```

# total_licvo

```{r}
read_plus <- function(flnm) {
    readr::read_csv(flnm) |>
    dplyr::mutate(filename = flnm)
}

Merged_total_licvo_init <- do.call(rbind,
          lapply(total_licvol_paths[1], read_plus))

#total_licvo data
for (i in 2:length(total_licvol_paths)) {
  Merged_total_licvo_temp <- do.call(rbind,
          lapply(total_licvol_paths[i], read_plus))
  
Merged_total_licvo_init <- rbind(Merged_total_licvo_init, Merged_total_licvo_temp)
  
}

# get the right scenario name and summarise to mean
Merged_total_licvo <- Merged_total_licvo_init |>
  tidyr::separate(filename, sep = "historical/", remove = FALSE, into = c(NA,"scenario"))|>  
  dplyr::mutate(scenario = gsub(x = scenario, pattern = "MACQ_CC_EFR_mkva/", replacement = "MACQ_CC_EFR_Mk5a/"))|>
  dplyr::mutate(scenario = gsub(x = scenario, pattern = "MACQ_CC_EFR_mkv/", replacement = "MACQ_CC_EFR_Mk5/"))|>
  dplyr::mutate(scenario = gsub(x = scenario, pattern = "MACQ_CC_EFR_mkiv/", replacement = "MACQ_CC_EFR_Mk4a/"))|>
  dplyr::mutate(scenario = gsub(x = scenario, pattern = "MACQ_CC_EFR/", replacement = "MACQ_CC_EFR_Mk4/"))|>  
  tidyr::separate(scenario, sep = "MACQ_CC_EFR_", remove = FALSE, into = c(NA,"scenario"))|>  
  tidyr::separate(scenario, sep = "/0/total_licvol.csv", remove = FALSE, into = c("scenario"))|>
  dplyr::mutate(scenario = stringr::str_replace_all(scenario, "/", "_"))|>
  dplyr::mutate(node_type = paste("node_type", node_type, sep = "_")) |>
  tidyr::pivot_wider(names_from = node_type, values_from = licvol)

```

## BALANCE

```{r}
read_plus_nc <- function(flnm) {
    metR::ReadNetCDF(flnm)|>
    dplyr::mutate(filename = flnm)
}

Merged_balance_init <- do.call(rbind,
          lapply(balance_paths[1], read_plus_nc))

#balance data
for (i in 2:length(balance_paths)) {
  Merged_balance_temp <- do.call(rbind,
          lapply(balance_paths[i], read_plus_nc))
  
Merged_balance_init <- rbind(Merged_balance_init, Merged_balance_temp)
  
}

# get the right scenario name and summarise to mean
Merged_balance <- Merged_balance_init |>
  tidyr::separate(filename, sep = "historical/", remove = FALSE, into = c(NA,"scenario"))|>  
  dplyr::mutate(scenario = gsub(x = scenario, pattern = "MACQ_CC_EFR_mkva/", replacement = "MACQ_CC_EFR_Mk5a/"))|>
  dplyr::mutate(scenario = gsub(x = scenario, pattern = "MACQ_CC_EFR_mkv/", replacement = "MACQ_CC_EFR_Mk5/"))|>
  dplyr::mutate(scenario = gsub(x = scenario, pattern = "MACQ_CC_EFR_mkiv/", replacement = "MACQ_CC_EFR_Mk4a/"))|>
  dplyr::mutate(scenario = gsub(x = scenario, pattern = "MACQ_CC_EFR/", replacement = "MACQ_CC_EFR_Mk4/"))|>  
  tidyr::separate(scenario, sep = "MACQ_CC_EFR_", remove = FALSE, into = c(NA,"scenario"))|>  
  tidyr::separate(scenario, sep = "/0/h2o_table.nc", remove = FALSE, into = c("scenario"))|>
  dplyr::mutate(scenario = stringr::str_replace_all(scenario, "/", "_"))

#do we ever what to use the timeseries of the balance data?
write.csv(Merged_balance, file = file.path(hydro_dir_historical, "Merged_balance_all_Mks.csv"))

Merged_balance <- Merged_balance |>
  dplyr::group_by(scenario)|>
  dplyr::summarise_at(dplyr::vars(Tributary:`End sys`), mean, na.rm = TRUE)
```

```{r}
scenario_meta2 <- dplyr::tibble(scenario = unique(Merged_balance$scenario)) 

scenario_meta <- scenario_meta2 |>
  #Mk
  tidyr::separate(scenario, sep = "_licvolfactor_", remove = FALSE, into = c("Mk", "licvolfactor")) |>
  #licvolfactor
  tidyr::separate(licvolfactor, sep = "_r", remove = FALSE, into = c("licvolfactor", "r_e")) |>
  dplyr::mutate(licvolfactor = gsub(x = licvolfactor, pattern = "_", replacement = "."))|>
  #rainfall and Evapotranspiration
  tidyr::separate(r_e, sep = "_e", remove = TRUE, into = c("Rainfall", "Evapotranspiration"))|>
  dplyr::mutate(Rainfall = gsub(x = Rainfall, pattern = "_", replacement = "."))|>
  dplyr::mutate(Evapotranspiration = gsub(x = Evapotranspiration, pattern = "_", replacement = "."))
  
scenario_meta <- dplyr::left_join(scenario_meta, Merged_balance, by = dplyr::join_by(scenario))
scenario_meta <- dplyr::left_join(scenario_meta, Merged_total_licvo, by = dplyr::join_by(scenario))
scenario_meta_list <- as.list(scenario_meta)


# I don't know the format we'll be using, but this works to create yaml metadata
yaml::write_yaml(scenario_meta_list, 
                 file = file.path(hydro_dir_historical, 'scenario_metadata.yml'))
# and this does the same with JSON
jsonlite::write_json(scenario_meta_list, 
                     path = file.path(hydro_dir_historical, 'scenario_metadata.json'))
```
