---
title: "Organise data"
format: html
editor: visual
---

## Data

Data from Ash on his blob. https://sho108storage.blob.core.windows.net/werp-deliverables/

Galen can access via CSIRO Azure account with Azure Storage Explorer. In process of sorting out programmatic access, for now it's just copied down.

This file is just going to extract the zips. The toolkit actually *can* read them straight out of the zip now, but unzipping seems better for clarity.

They're on the QAEL werp drive so we don't all have to have them locally. Very annoyingly, the WERP dir has different names for all of us. So it would be really nice to actually access a blob.

```{r}
if (Sys.info()['user'] == 'galen') {
  qaelpath <- '~/../Deakin University/QAEL - WERP in house - WERP'
} else if (Sys.info()['user'] == 'Georgiad') {
  qaelpath <- '~/Deakin University/QAEL - WERP - WERP'
} else {
  rlang::abort("YOU'RE NOT GALEN. PUT IN YOUR PATH TO QAEL-WERP")
}

ashpath <- file.path(qaelpath, 'Toolkit', 'AshData')


# Outer directory for project data
project_dir = file.path(qaelpath, 'Toolkit', 'eslt-data-2')

# Hydrographs (expected to exist already; created here with Ash_data_sorting.qmd)
hydro_dir = file.path(project_dir, 'hydrographs')

# Generated data
# EWR outputs (will be created here in controller, read from here in aggregator)
ewr_results <- file.path(project_dir, 'module_output', 'EWR')

# outputs of aggregator. There may be multiple modules
agg_results <- file.path(project_dir, 'aggregator_output')
```

Get the paths to the data we want, so we don't unzip the whole thing

```{r}
path_to_eslt_zip <- file.path(ashpath, 'dec23_results_2.zip')

all_paths <- unzip(path_to_eslt_zip, list = TRUE)$Name
    
hydro_paths <- all_paths[grepl('Straight Node \\(Gauge\\)\\.nc', 
                                     all_paths)]
csv_paths <- all_paths[grepl('*.csv', 
                                     all_paths)]
```

Create the output folder and unzip into it. I'm keeping Ash's name, though something more informative would be better.

```{r}
# unzip_to <- file.path(ashpath, 'dec23_results')
# if (!dir.exists(unzip_to)) {
#   dir.create(unzip_to, recursive = TRUE)}

unzip(path_to_eslt_zip, files = hydro_paths, exdir = file.path(qaelpath, 'Toolkit', 'eslt-data-2', 'hydrographs'))

unzip(path_to_eslt_zip, files = csv_paths, exdir = file.path(qaelpath, 'Toolkit', 'eslt-data-2', 'hydrographs'))
```

## ESLT data 2

## Extract variables

```{r}
read_plus <- function(flnm) {
    readr::read_csv(flnm) |>
    dplyr::mutate(filename = flnm)
}

#paths
Files_balance <- list.files(path = list.dirs(path = hydro_dir), pattern = "balance.csv", full.names=TRUE)
Files_total_licvol <- list.files(path = list.dirs(path = hydro_dir), pattern = "total_licvol.csv", full.names=TRUE)

#balance data
Merged_balance_init <- do.call(rbind,
          lapply(Files_balance, read_plus))

# get the right scenario name and summarise to mean
Merged_balance <- Merged_balance_init |>
  tidyr::separate(filename, sep = "hydrographs/", remove = FALSE, into = c(NA,"scenario"))|>
  tidyr::separate(scenario, sep = "balance.csv", remove = FALSE, into = c("scenario"))|>
  dplyr::mutate(scenario = stringr::str_replace_all(scenario, "/", "_"))|>
  dplyr::mutate(scenario = paste(scenario,"Straight Node (Gauge)", sep = ""))|>
  dplyr::group_by(scenario)|>
  dplyr::summarise_at(dplyr::vars(Tributary:`End sys`), mean, na.rm = TRUE)

#total_licvol data
Merged_total_licvol_init <- do.call(rbind,
          lapply(Files_total_licvol, read_plus))

Merged_total_licvol <- Merged_total_licvol_init |>
  tidyr::separate(filename, sep = "hydrographs/", remove = FALSE, into = c(NA,"scenario"))|>
  tidyr::separate(scenario, sep = "total_licvol.csv", remove = FALSE, into = c("scenario"))|>
  dplyr::mutate(scenario = stringr::str_replace_all(scenario, "/", "_"))|>
  dplyr::mutate(scenario = paste(scenario,"Straight Node (Gauge)", sep = ""))|>
  dplyr::mutate(node_type = paste("node_type", node_type, sep = "_")) |>
  tidyr::pivot_wider(names_from = node_type, values_from = licvol)


```

## Metadata

```{r}
scenario_meta2 <- dplyr::tibble(scenario = unique(Merged_balance$scenario)) 

scenario_meta <- scenario_meta2 |>
  tidyr::separate(scenario, sep = "_licvolfactor_", remove = FALSE, into = c("scale_evap", "licvolfactor")) |>
  #licvolfactor
  tidyr::separate(licvolfactor, sep = "_Straight", remove = FALSE, into = c("licvolfactor"))|>
  tidyr::separate(licvolfactor, sep = "_", remove = FALSE, into = c("lic","vol","factor"))|>
  dplyr::mutate(factor = ifelse(is.na(factor), 0, factor))|>
  dplyr::mutate(licvolfactor = as.numeric(paste(lic, ".",vol, factor, sep = "")))|>
  dplyr::select(-lic,-vol, -factor)|>
  # #scale_evap #when there was no rain
  # tidyr::separate(scale_evap, sep = "historical", remove = FALSE, into = c(NA,"scale_evap"))|>
  # tidyr::separate(scale_evap, sep = "_scale_evap_", remove = FALSE, into = c(NA, "scale_evap"))|>
  # tidyr::separate(scale_evap, sep = "_", remove = FALSE, into = c("scale","evap"))|>
  # dplyr::mutate(scale = ifelse(is.na(scale), 0, scale))|>
  # dplyr::mutate(evap = ifelse(is.na(evap), 0, evap))|>
  # dplyr::mutate(scale_evap = as.numeric(paste(scale, ".",evap, sep = "")))|>
  # dplyr::select(-scale,-evap)
  #scale_evap
  tidyr::separate(scale_evap, sep = "historical_scale_rain_", remove = FALSE, into = c(NA,"rain_evap"))|>
  tidyr::separate(rain_evap, sep = "_evap_", remove = TRUE, into = c("scale_rain", "scale_evap"))|>
  dplyr::mutate(scale_rain = as.numeric(stringr::str_replace_all(scale_rain, "_", ".")))|>
  dplyr::mutate(scale_evap = as.numeric(stringr::str_replace_all(scale_evap, "_", ".")))

scenario_meta <- dplyr::left_join(scenario_meta, Merged_balance, by = dplyr::join_by(scenario))
scenario_meta <- dplyr::left_join(scenario_meta, Merged_total_licvol, by = dplyr::join_by(scenario))
scenario_meta_list <- as.list(scenario_meta)


# I don't know the format we'll be using, but this works to create yaml metadata
yaml::write_yaml(scenario_meta_list, 
                 file = file.path(hydro_dir, 'scenario_metadata.yml'))
# and this does the same with JSON
jsonlite::write_json(scenario_meta_list, 
                     path = file.path(hydro_dir, 'scenario_metadata.json'))
```
