---
title: "2_aggregation_testing"
format: html
editor: visual
---

## testing aggregations to hopefully match what Georgia needs

*note* in general, it looks like Georgia wasn't actually using aggregate_historic.qmd, but we will need to modify the following into a scenario-parser at some point (likely post-aggregation)

```{r}
#| eval: false
# get the right scenario name and summarise to mean
Merged_EWR <- Merged_EWR_init |>
  tidyr::separate(filename, sep = "historic/", remove = FALSE, into = c(NA,"rem"))|>  
  tidyr::separate(rem, sep = "/module_output/EWR/licvolfactor_", remove = TRUE, into = c("Mk","rem"))|>  
  tidyr::separate(rem, sep = "_r", remove = TRUE, into = c("licvolfactor","rem"))|>  
  tidyr::separate(rem, sep = "_e", remove = TRUE, into = c("Rainfall","rem"))|>  
  tidyr::separate(rem, sep = "_0/yearly.csv", remove = TRUE, into = c("Evapotranspiration",NA))|>
  dplyr::mutate(licvolfactor = gsub(x = licvolfactor, pattern = "_", replacement = "."))|>
  dplyr::mutate(Rainfall = gsub(x = Rainfall, pattern = "_", replacement = "."))|>
  dplyr::mutate(Evapotranspiration = gsub(x = Evapotranspiration, pattern = "_", replacement = "."))|>
  dplyr::select(-filename)|>
  dplyr::mutate(gauge = as.character(gauge))
```

```{r}
# library(HydroBOT)
library(sf)
# for testing, use the dev
devtools::load_all('../WERP_toolkit')
```

## Paths

```{r}
#| include: false

if (Sys.info()['user'] == 'galen') {
  qaelpath <- '~/../Deakin University/QAEL - WERP in house - WERP'
} else if (Sys.info()['user'] == 'Georgiad') {
  qaelpath <- '~/Deakin University/QAEL - WERP - WERP'
} else if (Sys.info()['user'] == 'georgiad') {
  qaelpath <- 'C:/Users/georgiad/Deakin University/QAEL - WERP - WERP'
} else if (Sys.info()['user'] == 'Admin') {
  qaelpath <- 'C:/Users/Admin/Deakin University/QAEL - WERP in house - WERP'
} else {
  rlang::abort("YOU'RE NOT GALEN. PUT IN YOUR PATH TO QAEL-WERP")
}

# python can't use the tildes, so have to expand
qaelpath <- path.expand(qaelpath)
```

## there's some creation of a new causal network

I guess I'll do that or I'm going to get completely lost

```{r}
# Make this small and make sense. Will need more cleanup to use for real
objective_mapping <- readr::read_csv(file.path(qaelpath, 'Toolkit','CausalNetworks', 'EWR_to_Target_mapping.csv')) |> 
  dplyr::select(planning_unit_name, gauge, ewr_code, ewr_code_timing, env_group = target) |> 
  dplyr::mutate(ewr_code_timing = ifelse(is.na(ewr_code_timing), '', ewr_code_timing)) |> 
  dplyr::mutate(ewr_code_timing = paste0(ewr_code, '_', ewr_code_timing)|>
                  gsub('_$', '', x = _)) |> 
  dplyr::mutate(target = dplyr::case_when(      
    env_group == "NF" ~ "Native fish",
    env_group == "NV" ~ "Native vegetation" ,
    env_group == "OS" ~ "Other species",   
    env_group == "EF" ~ "Priority ecosystem function", 
    env_group == "WB" ~ "Waterbird",
    is.na(env_group) ~ NA
  )
  )
```

Clip sdls to the Macquarie, or it will return a bunch of other units due to overlaps of the pplanning units

```{r}
sdl_clip <- sdl_units |> 
  dplyr::filter(SWSDLName == 'Macquarie–Castlereagh')
```

*TESTING DIRS TO TRY TO MATCH GEORGIA*

```{r}
project_dir <- file.path(qaelpath, 'Toolkit', 'macq-data-no_climate_change')
ewr_results <- file.path(project_dir, 'module_output', 'EWR')
```

Because this is testing a bunch of new code, I'm going to very explicitly step through things and then build a final aggsequence to send off for processing.

Try to duplicate just the timing spells step. Georgia's doing two things there- getting a time-mean of ewr_achieved and getting a max interevent duration. She ends up with a single df with both, but it feels dangerous. Is it? Maybe not- they're both time-aggregations, so should each collapse to one row per group.

*this test data only has the stochastic runs as scenarios*

```{r}
data <- prep_ewr_agg(ewrpath = ewr_results, type = 'achievement', geopath = bom_basin_gauges)
```

Now, step 1 is a full-time mean of the ewr_achieved, and a full-time interevent max. Can I do them at the same time? Do they yield the same thing?

```{r}
meanach <- multi_aggregate(data, 
                           causal_edges = list(objective_mapping), 
                           groupers = c('scenario', 'ewr_code_timing', 'gauge', 'planning_unit_name'), 
                           aggCols = 'ewr_achieved',
                           aggsequence = list(all_time = 'all_time'),
                           funsequence = list('ArithmeticMean'))
```

```{r}
maxinter <- multi_aggregate(data, 
                           causal_edges = list(objective_mapping), 
                           groupers = c('scenario', 'ewr_code_timing', 'gauge', 'planning_unit_name'), 
                           aggCols = 'event_years',
                           aggsequence = list(all_time = 'all_time'),
                           funsequence = list('get_max_interevent'))
```

Those are the same length. Does it make sense to keep them together? It will spawn extra cols that we don't really want. Does work though.

```{r}
# gauge_EWR_timing_spells?
timeagged <- multi_aggregate(data, 
                           causal_edges = list(objective_mapping), 
                           groupers = c('scenario', 'ewr_code_timing', 'gauge', 'planning_unit_name'), 
                           aggCols = c('ewr_achieved', 'event_years'),
                           aggsequence = list(all_time = 'all_time'),
                           funsequence = list(c('ArithmeticMean', 'get_max_interevent')))
```

# The rest of the sequence

I cannot figure out what the sequences are. They're all jumbled up and I can't tell the point of each one.

So, there's timeseries and then there's the time-aggregates, as above (`data` and `timeagged`)

## JUST THE Time-AGGED FOR NOW

I do not understand the 'target' vs not-'target' versions.

### Following the not-target versions

First, to ewr_code from code_timing

```{r}

# gauge_EWR_spells
ewr_aggregated <- multi_aggregate(timeagged, 
                           causal_edges = list(objective_mapping), 
                           groupers = c('scenario', 'gauge', 'planning_unit_name'), 
                           aggCols = c('ewr_achieved', 'event_years'),
                           aggsequence = list(ewr_code = c("ewr_code_timing", "ewr_code")),
                           funsequence = list(c('NumberOfValues', 'ArithmeticMean', 'Sum')))
```

Then, to planning_unit from gauge

Really should update all the functiosn to return NA if all na

```{r}
maxna <- function(x, na.rm = TRUE) {
  ifelse(all(is.na(x)), NA, max(x, na.rm = TRUE))
}
```

Then to planning units

```{r}
# planning_unit_EWR_spells
pu_aggregated <- multi_aggregate(ewr_aggregated, 
                           causal_edges = list(objective_mapping), 
                           groupers = c('scenario', 'ewr_code'), 
                           aggCols = c('ewr_achieved', 'event_years'),
                           pseudo_spatial = 'planning_units',
                           aggsequence = list(planning_units = planning_units),
                           funsequence = list(c('NumberOfValues', 'ArithmeticMean', 'Sum', 'Variance', 'maxna')))
```

So, cudgegong is throwing an NA in everything

Then to sdl units

```{r}
# sdl_EWR_spells

sdl_aggregated <- multi_aggregate(pu_aggregated, 
                           causal_edges = list(objective_mapping), 
                           groupers = c('scenario', 'ewr_code'), 
                           aggCols = c('ewr_achieved', 'event_years'),
                           aggsequence = list(sdl_units = sdl_clip),
                           funsequence = list(c('NumberOfValues', 'ArithmeticMean', 'Sum', 'maxna')))

```

Now, can we set all that up together into one call?

Yes, this works.

```{r}
agg_sequence <- list(all_time = 'all_time',
                     ewr_code = c("ewr_code_timing", "ewr_code"),
                     planning_units = planning_units, 
                     sdl_units = sdl_clip )

fun_sequence <- list(c('ArithmeticMean', 'get_max_interevent'),
                     c('NumberOfValues', 'ArithmeticMean', 'Sum'),
                     c('NumberOfValues', 'ArithmeticMean', 'Sum', 'Variance', 'maxna'),
                     c('NumberOfValues', 'ArithmeticMean', 'Sum', 'maxna'))
```

```{r}
all_agg <- multi_aggregate(data, 
                           causal_edges = list(objective_mapping), 
                           groupers = c('scenario'), 
                           aggCols = c('ewr_achieved', 'event_years'),
                           aggsequence = agg_sequence,
                           funsequence = fun_sequence,
                           saveintermediate = TRUE, 
                           auto_ewr_PU = TRUE)
```

Now, there's the issue of what to do about the massively propagating functions. Do we do separate calls for each sequence? Do we post-hoc trim?

There are really only a couple options.

1.  Do it this way, post-hoc parse the names
    1.  Will be annoying, but maybe not terrible. Could rename at the same time with `select`
2.  Do it this way, set namehistory = FALSE, and post-hoc filter
    1.  Probably about the same as 1. Would then pivot_wider, probably.
3.  Run each path through separately
    1.  This seems horribly complex
4.  Change the toolkit to accept branching/closing pathways, not fully-factorial.
    1.  Would be best, but not by tomorrow

## Next steps

Whatever we do with that, if we assume we have some setup like above, can we test and check that it works with `read_and_agg` to loop over everything and save where it should?

Worst case, could returnList and save in the script, but using the machinery would be better.

How to parallel? One option is to pass in long datpaths? ie all the way in to the 76? What does that save as if we give it the default savepath or append the extra bits onto savepath or remove bits from savepath?

Will need to test all this with the full set of data, not the test case above.

What do I get if I just read_and_agg? 104 seconds. so 1.4 seconds per scenario. at 5548, that's 130 minutes. Local parallel should be enough, but might as well just use petrichor? Especially since we'll need 4-5 of these. the file size is 1.1 Gb

```{r}

# real mac data path
full_mac_dir <- file.path(qaelpath, 'Toolkit', 'macquarie')

# Let's just drill all the way in to one of them and see what I get
test_ewr_results <- file.path(full_mac_dir, 'module_output', 'EWR', 'hydrographs/stochastic/MACQ_CC_EFR/licvolfactor_1_0/r1_0_e1_0')

  system.time(spatagg_s_th_t <- read_and_agg(
    datpath = test_ewr_results,
    type = "achievement",
    geopath = bom_basin_gauges,
    causalpath = list(objective_mapping),
    groupers = "scenario",
    aggCols = c('ewr_achieved', 'event_years'),
    aggsequence = agg_sequence,
    funsequence = fun_sequence,
    keepAllPolys = FALSE,
    auto_ewr_PU = TRUE,
    saveintermediate = TRUE,
    returnList = FALSE,
    savepath = file.path(full_mac_dir, 'aggregated')
  ))
```

Where does that save? directly to the folder specified, so if we want deeper folder structures, we'll need to give them to longer savepaths.

Can we do an ugly thing of looping over the input paths in a parallel loop? Would be better to embed, but for now that'd work.

Do we need to saveintermediate?

What does the rds look like? does the scenario retain the full original path we can parse to get metadata? No. And the EWR tool didn't retain it either. SO, we'll need to add that and be careful about it.

```{r}
testrds <- readRDS(file.path(full_mac_dir, 'aggregated', 'achievement_aggregated.rds'))
```

It might actually work better then for now to returnList = TRUE, not save in the function, do the column drops, edit the 'scenario' column (we'll have the full path up to the 76-index in the ewrpath), and then save to a new full path in aggregated. That would handle a lot of the weird complexity here.

Really, that'd just mean figuring out which columns are the paths we want, and that has to happen anyway.

Try to set that up.

It's basically the run_macq_stoch.r approach in /HPC

```{r}

ewr_dir <- file.path(full_mac_dir, 'module_output', 'EWR', 'hydrographs')

inner_dirs <- list.dirs(
  ewr_dir, recursive = TRUE
  )

inner_climdirs <- grepl('r[0-9]_[0-9]_e1_[0-9]{1,2}$', inner_dirs)
inner_parents <- inner_dirs[inner_climdirs]
# Those will be the hydro_dirs, each with 76 scenarios inside
# Then we want to make the outputs work, so put them in subdirs with the same structure
inner_subdirs <- gsub(ewr_dir, '', inner_parents)
inner_subdirs <- gsub('^/', '', inner_subdirs)
```

Set that up for one run

With some set of retained columns, chosen largely at random here to test

```{r}
retain_cols <- c(
  "sdl_units_Sum_planning_units_NumberOfValues_ewr_code_NumberOfValues_temporal_ArithmeticMean_ewr_achieved",
  "sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_temporal_ArithmeticMean_ewr_achieved",
  "sdl_units_ArithmeticMean_planning_units_NumberOfValues_ewr_code_NumberOfValues_temporal_get_max_interevent_ewr_achieved",
  "sdl_units_NumberOfValues_planning_units_ArithmeticMean_ewr_code_NumberOfValues_temporal_get_max_interevent_ewr_achieved"
)
```

Let's test with

```{r}
inner_parents[100]
```

If we want saveintermediate, will need to parse back that retain list at each step

```{r}
#| eval: false
# This was to develop the function below
for (i in 100:100) {

  testagg <- read_and_agg(
    datpath = inner_parents[i],
    type = "achievement",
    geopath = bom_basin_gauges,
    causalpath = list(objective_mapping),
    groupers = "scenario",
    aggCols = c('ewr_achieved', 'event_years'),
    aggsequence = agg_sequence,
    funsequence = fun_sequence,
    keepAllPolys = FALSE,
    auto_ewr_PU = TRUE,
    saveintermediate = FALSE,
    returnList = TRUE #,
   # savepath = file.path(full_macq_dir, 'aggregated', inner_subdirs[i])
  )
  
  # aggregated columns will always start with the last aggsequence name
  not_aggs <- which(!grepl(paste0('^',
                                  names(agg_sequence)[length(agg_sequence)], 
                                  '_'), x = names(testagg)))
  
  desired_aggs <- tidyselect::eval_select(retain_cols, testagg)
  
  testagg <- testagg |> 
    dplyr::select(tidyselect::all_of(c(not_aggs, desired_aggs)))
  
  # If we keep MAX, will need to be careful on read-in of multiple agg files not to duplicate it.

  # Make scenarios unique
  # I *hate* using path separators / in this, but if I use _ like I want, it'll get confused with Ash's use to sub them with . in things like 1_07.

  # I should parse here too into the cols to actually ID them
  fix_ <- function(x) {
    x <- gsub('[A-Za-z]*', '', x)
    x <- gsub('^_', '', x) 
    x <- gsub('_', '.', x)
    x <- as.numeric(x)
  }
  
  testagg <- testagg |> 
    dplyr::mutate(scenario = paste0(inner_subdirs[i], '/', scenario)) |> 
    tidyr::separate_wider_delim(scenario, '/', 
                                names = c('Data', 'Mk', 'licvolfactor',
                                          'rem', 'stoch_replicate'),
                                cols_remove = FALSE) |> 
     tidyr::separate_wider_delim(rem, "_e", 
                     names = c("Rainfall","Evapotranspiration")) |> 
    dplyr::mutate(across(c(licvolfactor, Rainfall, Evapotranspiration), fix_)) |> 
    # not sure about this; it's Cudgegong NAs
    dplyr::filter(!is.na(polyID))
  
  
  savepath <- file.path(full_mac_dir, 
                           'aggregated',
                           inner_subdirs[i])
  if (!dir.exists(savepath)) {
    dir.create(savepath, recursive = TRUE)
  }
  saveRDS(tc, 
          file = file.path(savepath,
                           paste0(aggname, '.rds')))
  
  
}
```

```{r}
aggregate_dirs <- function(subdir, 
                           ewr_dir, 
                           project_dir, 
                           aggsequence,
                           funsequence, 
                           aggCols, 
                           retain_cols,
                           aggname) {
  
 oneagg <- read_and_agg(
    datpath = file.path(ewr_dir, subdir),
    type = "achievement",
    geopath = bom_basin_gauges,
    causalpath = list(objective_mapping),
    groupers = "scenario",
    aggCols = aggCols,
    aggsequence = aggsequence,
    funsequence = funsequence,
    keepAllPolys = FALSE,
    auto_ewr_PU = TRUE,
    saveintermediate = FALSE,
    returnList = TRUE #,
   # savepath = file.path(full_macq_dir, 'aggregated', inner_subdirs[i])
  )
  
  # aggregated columns will always start with the last aggsequence name
  not_aggs <- which(!grepl(paste0('^',
                                  names(aggsequence)[length(aggsequence)], 
                                  '_'), x = names(oneagg)))
  
  desired_aggs <- tidyselect::eval_select(retain_cols, oneagg)
  
  oneagg <- oneagg |> 
    dplyr::select(tidyselect::all_of(c(not_aggs, desired_aggs)))
  
  # If we keep MAX, will need to be careful on read-in of multiple agg files not to duplicate it.

  # Make scenarios unique
  # I *hate* using path separators / in this, but if I use _ like I want, it'll get confused with Ash's use to sub them with . in things like 1_07.

  # I should parse here too into the cols to actually ID them
  fix_ <- function(x) {
    x <- gsub('[A-Za-z]*', '', x)
    x <- gsub('^_', '', x) 
    x <- gsub('_', '.', x)
    x <- as.numeric(x)
  }
  
  oneagg <- oneagg |> 
    dplyr::mutate(scenario = paste0(subdir, '/', scenario)) |> 
    tidyr::separate_wider_delim(scenario, '/', 
                                names = c('Data', 'Mk', 'licvolfactor',
                                          'rem', 'stoch_replicate'),
                                cols_remove = FALSE) |> 
     tidyr::separate_wider_delim(rem, "_e", 
                     names = c("Rainfall","Evapotranspiration")) |> 
    dplyr::mutate(across(c(licvolfactor, Rainfall, Evapotranspiration), fix_)) |> 
    # not sure about this; it's Cudgegong NAs
    dplyr::filter(!is.na(polyID)) |> 
    dplyr::select(scenario, tidyselect::everything(), geometry)
  
  
  savepath <- file.path(project_dir, 
                           'aggregated',
                           subdir)
  
  if (!dir.exists(savepath)) {
    dir.create(savepath, recursive = TRUE)
  }
  saveRDS(tc, 
          file = file.path(savepath,
                           paste0(aggname, '.rds')))
  
}
```

Test that

```{r}
system.time(
  aggregate_dirs(subdir = inner_subdirs[100], 
                 ewr_dir = ewr_dir, 
                 project_dir = full_mac_dir, 
                 aggsequence = agg_sequence,
                 funsequence = fun_sequence,
                 aggCols = c('ewr_achieved', 'event_years'), 
                 retain_cols = retain_cols,
                 aggname = 'TEST'
  )
)
```

That works. So, now we want to set up the actual runs. There are four key runs, and the trick is going to be setting up their sequencing.

The 'timeseries' runs are simpler.

The one Georgia called sdl_EWR_timeseries should be as follows according to the spreadsheet. However, her code also produced n_ewr_versions and n_gauges and n_planning_units and EWR_Variance. If we need those, I'll have to re-run.

```{r}
agg_sEt <- list(ewr_code = c("ewr_code_timing", "ewr_code"),
                     planning_units = planning_units, 
                     sdl_units = sdl_clip)

fun_sEt <- list(c('ArithmeticMean'),
                     c('ArithmeticMean'),
                     c('ArithmeticMean'))

retained_sEt <- c('sdl_units_ArithmeticMean_planning_units_ArithmeticMean_ewr_code_ArithmeticMean_ewr_achieved')

name_sEt <- 'sdl_ewr_timeseries'
```

We will furrr over the parents, but to test one,

```{r}
system.time(
  aggregate_dirs(subdir = inner_subdirs[100], 
                 ewr_dir = ewr_dir, 
                 project_dir = full_mac_dir, 
                 aggsequence = agg_sEt,
                 funsequence = fun_sEt,
                 aggCols = c('ewr_achieved'), 
                 retain_cols = retained_sEt,
                 aggname = name_sEt
  )
)

test_sdl_ewr_ts <- readRDS(file.path(full_mac_dir, 'aggregated', inner_subdirs[100], paste0(name_sEt, '.rds')))
```
